### 2022-10-10 README.qmd
Add a README.

---
title: "DCVtestkit Output Examples"
format: 
  gfm:
    author: Jeremy Selva
    date: "Last compiled on `r format(Sys.time(), '%d %B, %Y')`"
---

## Quarto

Quarto enables you to weave together content and executable code into a finished document. To learn more about Quarto see <https://quarto.org>.

## Running Code

When you click the **Render** button a document will be generated that includes both content and the output of embedded code. You can embed code like this:

```{r}
1 + 1
```

You can add options to executable code like this

```{r}
#| echo: false
2 * 2
```

The `echo: false` option disables the printing of code (only output is displayed).

### 2022-10-10 README.qmd
Add additional text.

@@
 title: "DCVtestkit Output Examples"
-format: 
-  gfm:
-    author: Jeremy Selva
-    date: "Last compiled on `r format(Sys.time(), '%d %B, %Y')`"
+format: gfm
 ---
 
-## Quarto
+# Introduction
 
-Quarto enables you to weave together content and executable code into a finished document. To learn more about Quarto see <https://quarto.org>.
+Here is where I store some output example of the R package [`DCVtestkit`](https://github.com/SLINGhub/DCVtestkit)
 
-## Running Code
+## Excel Output Example
 
-When you click the **Render** button a document will be generated that includes both content and the output of embedded code. You can embed code like this:
+[`dilution_summary.xlsx`] is the output in Excel.
 
-```{r}
-1 + 1
-```
+## Pdf Output Example
 
-You can add options to executable code like this
+[`dilution_plot.xlsx`] is the output in pdf.
 
-```{r}
-#| echo: false
-2 * 2
-```
+## Trellis Output Example
 
-The `echo: false` option disables the printing of code (only output is displayed).
+https://dcvtestkit-interactive-example.netlify.app is the output as an interactive trellis plot from the `Dilution_Plot_Folder` when the `index.html` file is clicked.
+
+## Quarto Output Example
+
+https://dcvtestkit-quarto-example.netlify.app is the output of a html file generated using [Quarto](https://quarto.org/)

### 2022-10-10 README.qmd
Try to fix the link to the excel and pdf files.

@@
 
-[`dilution_summary.xlsx`] is the output in Excel.
+[`dilution_summary.xlsx`](https://raw.githubusercontent.com/JauntyJJS/DCVtestkit_Output/main/dilution_summary.xlsx) is the output in Excel.
 
@@
 
-[`dilution_plot.xlsx`] is the output in pdf.
+[`dilution_plot.pdf`](https://raw.githubusercontent.com/JauntyJJS/DCVtestkit_Output/main/dilution_plot.pdf) is the output in pdf.
 

### 2022-10-12 Quarto_Simulation/index.qmd
Save simulation code.

---
title: "Simulation"
author: "Jeremy Selva"
format: html
---

# R Libaries used
```{r R packages}
#| message: false

library(dplyr)
library(tidyr)
library(stringr)
library(tibble)
library(purrr)
library(ggplot2)
library(epifitter)
library(DCVtestkit)

set.seed(123)
```

```{r Saturation Many Data}

simulate_saturation <- function(id) {

  mono_model <- sim_monomolecular(
  N = 200,     # total time units 
  y0 = 0.01,   # initial inoculum
  dt = 30,     #  interval between assessments in time units
  r = 0.0175,  #  apparent infection rate
  alpha = 0.15,# level of noise
  n = 1        # number of replicates
  )

  saturation_simulation <- tibble::tibble(
    x = mono_model$time,
    y = mono_model$random_y * sample(1:1000000, 1),
    `Sample Name` = as.character(mono_model$time))

  return(saturation_simulation)

}

saturation_simulated_database <-
  tibble::tibble(
    ID = paste("Saturation", 
               stringr::str_pad(1:200, width = 3, pad = "0")),
    `Dilution Batch Name` = "Saturation"

  ) |> 
  dplyr::mutate(
    dilution_data = purrr::map(
      .x = .data$ID,
      .f = simulate_saturation
      )
    ) |> 
  tidyr::unnest("dilution_data")

```

```{r}
# exp_model <- sim_exponential(
#     N = 200,    # total time units 
#     y0 = 1,  # initial inoculum
#     dt = 30,    #  interval between assessments in time units
#     r = 0.02,  #  apparent infection rate
#     #alpha = 0.01,# level of noise
#     alpha = 0.2, # level of noise
#     n = 1       # number of replicates
#     )
# 
# exp_plot = exp_model %>%
#   ggplot(aes(time, y)) +
#   geom_jitter(aes(time, random_y), size = 3, width = .1) +
#   geom_line(size = 1) +
#   labs(
#     title = "Exponential",
#     y = "Disease intensity",
#     x = "Time"
#   )
# exp_plot
```

```{r LOD Many Data}

simulate_lod <- function(id) {

  exp_model <- sim_exponential(
    N = 200,    # total time units 
    y0 = 1,  # initial inoculum
    dt = 30,    #  interval between assessments in time units
    r = 0.02,  #  apparent infection rate
    #alpha = 0.1, # level of noise
    alpha = 0.15, # level of noise
    n = 1       # number of replicates
    )

  lod_simulation <- tibble::tibble(
    x = exp_model$time,
    y = exp_model$random_y * sample(1:1000000, 1),
    `Sample Name` = as.character(exp_model$time))

  return(lod_simulation)

}

lod_simulated_database <-
  tibble::tibble(
    ID = paste("Limit Of Detection", 
               stringr::str_pad(1:200, width = 3, pad = "0")),
    `Dilution Batch Name` = "Limit Of Detection"

  ) |> 
  dplyr::mutate(
    dilution_data = purrr::map(
      .x = .data$ID,
      .f = simulate_lod
      )
    ) |> 
  tidyr::unnest("dilution_data")

```

```{r Linear Many Data}

simulate_lod <- function(id) {

  exp_model <- sim_exponential(
    N = 200,    # total time units 
    y0 = 1,  # initial inoculum
    dt = 30,    #  interval between assessments in time units
    r = 0.02,  #  apparent infection rate
    #alpha = 0.1, # level of noise
    alpha = 0.15, # level of noise
    n = 1       # number of replicates
    )

  lod_simulation <- tibble::tibble(
    x = exp_model$time,
    y = exp_model$random_y * sample(1:1000000, 1),
    `Sample Name` = as.character(exp_model$time))

  return(lod_simulation)

}

lod_simulated_database <-
  tibble::tibble(
    ID = paste("Limit Of Detection", 
               stringr::str_pad(1:200, width = 3, pad = "0")),
    `Dilution Batch Name` = "Limit Of Detection"

  ) |> 
  dplyr::mutate(
    dilution_data = purrr::map(
      .x = .data$ID,
      .f = simulate_lod
      )
    ) |> 
  tidyr::unnest("dilution_data")

```

```{r}

# Create dilution statistical summary
saturation_dilution_summary <- summarise_dilution_table(
  saturation_simulated_database,
  grouping_variable = c("ID"),
  conc_var = "x",
  signal_var = "y")
```

```{r}

lod_dilution_summary <- summarise_dilution_table(
  lod_simulated_database,
  grouping_variable = c("ID"),
  conc_var = "x",
  signal_var = "y")

```

```{r}
saturation_ggplot_table <- add_ggplot_panel(
  dilution_table = saturation_simulated_database,
  dilution_summary = saturation_dilution_summary,
  grouping_variable = c("ID"),
  dil_batch_var = "Dilution Batch Name",
  conc_var = "x",
  signal_var = "y",
  conc_var_units = ""
  )

saturation_ggplot_list <- saturation_ggplot_table$panel

view_ggplot_pdf(saturation_ggplot_list,
                filename = "dilution_plot_saturated.pdf",
                ncol_per_page = 2,
                nrow_per_page = 2)

```

```{r}
lod_ggplot_table <- add_ggplot_panel(
  dilution_table = lod_simulated_database,
  dilution_summary = lod_dilution_summary,
  grouping_variable = c("ID"),
  dil_batch_var = "Dilution Batch Name",
  conc_var = "x",
  signal_var = "y",
  conc_var_units = ""
  )

lod_ggplot_list <- lod_ggplot_table$panel

view_ggplot_pdf(lod_ggplot_list,
                filename = "dilution_plot_lod.pdf",
                ncol_per_page = 2,
                nrow_per_page = 2)

```

```{r}
# Create a trellis table
saturation_trellis_table <- add_plotly_panel(
  dilution_table = saturation_simulated_database,
  dilution_summary = saturation_dilution_summary,
  grouping_variable = c("ID"),
  sample_name_var = "Sample Name",
  dil_batch_var = "Dilution Batch Name",
  dil_batch_col = c(
    "#377eb8"),
  conc_var = "x",
  conc_var_units = "",
  conc_var_interval = 50,
  signal_var = "y",
  have_plot_title = FALSE
) |> 
  convert_to_cog(
    grouping_variable = "ID",
    panel_variable = "panel",
    col_name_vec = "col_name_vec",
    desc_vec = "desc_vec",
    type_vec = "type_vec"
  )

view_trellis_html(
  trellis_table = saturation_trellis_table,
  grouping_variable = c("ID"),
  trellis_report_name = "Dilution_Plot_Saturated",
  trellis_report_folder = "Dilution_Saturated_Folder",
  panel_variable = "panel"
)
```

```{r}
# Create a trellis table
lod_trellis_table <- add_plotly_panel(
  dilution_table = lod_simulated_database,
  dilution_summary = lod_dilution_summary,
  grouping_variable = c("ID"),
  sample_name_var = "Sample Name",
  dil_batch_var = "Dilution Batch Name",
  dil_batch_col = c(
    "#377eb8"),
  conc_var = "x",
  conc_var_units = "",
  conc_var_interval = 50,
  signal_var = "y",
  have_plot_title = FALSE
) |> 
  convert_to_cog(
    grouping_variable = "ID",
    panel_variable = "panel",
    col_name_vec = "col_name_vec",
    desc_vec = "desc_vec",
    type_vec = "type_vec"
  )

view_trellis_html(
  trellis_table = lod_trellis_table,
  grouping_variable = c("ID"),
  trellis_report_name = "Dilution_Plot_LOD",
  trellis_report_folder = "Dilution_LOD_Folder",
  panel_variable = "panel"
)
```

### 2022-10-12 Quarto_Simulation/index.qmd
Update simulation code.

@@
 library(epifitter)
+library(deSolve)
 library(DCVtestkit)
@@
 
+# Simulation Functions
+
+Here are the functions to simulate the different types of curves.
+
+::: {.panel-tabset}
+
+## Saturated Curve
+
 ```{r Saturation Many Data}
@@
 
-  mono_model <- sim_monomolecular(
+  mono_model <- epifitter::sim_monomolecular(
   N = 200,     # total time units 
@@
 
+```
+
+## Limit of Detection Curve
+
+```{r LOD Many Data}
+
+simulate_lod <- function(id) {
+
+  exp_model <- epifitter::sim_exponential(
+    N = 200,    # total time units 
+    y0 = 1,  # initial inoculum
+    dt = 30,    #  interval between assessments in time units
+    r = 0.02,  #  apparent infection rate
+    alpha = 0.15, # level of noise
+    n = 1       # number of replicates
+    )
+
+  lod_simulation <- tibble::tibble(
+    x = exp_model$time,
+    y = exp_model$random_y * sample(1:1000000, 1),
+    `Sample Name` = as.character(exp_model$time))
+
+  return(lod_simulation)
+
+}
+
+```
+
+## Linear Curve
+
+```{r Linear Many Data}
+
+#diffeq model as function
+model.constant = function(times, y, parms) {
+  ## times = current times
+  ## y = current state vector: in this case the 0th derivative, c(x)
+  ## parms = vector of model parameters.
+  with(as.list(c(y,parms)),{
+  derivs = c( 
+    dx = a
+    )
+  ## Return
+  list(derivs)
+})
+}
+
+sim_linear <- function(
+    N,    # total time units
+    y0,  # initial inoculum
+    dt,    #  interval between assessments in time units
+    r,  #  apparent infection rate
+    alpha, # level of noise
+    n       # number of replicates
+) {
+
+  time <- seq(0, N, by = dt)
+  random_y <- numeric(length(time))
+  y <- numeric(length(time))
+  y[1] <- y0
+
+  for (k in 1:(length(time) - 1)) {
+    r[k + 1] <- r[k]
+    InitCond <- c(y[k])
+    steps <- seq(time[k], time[k + 1], by = dt)
+    parms <- c(a = r[k])
+    ode_logi <- deSolve::ode(InitCond, steps, model.constant, parms)
+    y[k + 1] <- ode_logi[length(ode_logi[, 2]), 2]
+  }
+
+  data_uni <- matrix(0, ncol = 4, nrow = length(y))
+  data_all <- matrix(0, ncol = 4, nrow = 0)
+
+  for (j in 1:n) {
+    for (i in 1:length(time)) {
+      random_y[i] <- stats::rnorm(1, y[i], sd = alpha * y[i])
+      }
+    data_uni[, 1] <- rep(j, length(y))
+    data_uni[, 2] <- time
+    data_uni[, 3] <- y
+    data_uni[, 4] <- random_y
+    data_all <- rbind(data_all, data_uni)
+    colnames(data_all) <-
+      c("replicates", "time", "y", "random_y")
+  }
+
+  data_all = data.frame(data_all)
+  return(data_all)
+
+}
+
+simulate_linear <- function(id) {
+
+  linear_model <- sim_linear(
+    N = 200,    # total time units 
+    y0 = 1,  # initial inoculum
+    dt = 30,    #  interval between assessments in time units
+    r = 0.02,  #  apparent infection rate
+    alpha = 0.1, # level of noise
+    n = 1       # number of replicates
+  )
+
+  linear_simulation <- tibble::tibble(
+    x = linear_model$time,
+    y = linear_model$random_y * sample(1:1000000, 1),
+    `Sample Name` = as.character(linear_model$time))
+
+  return(linear_simulation)
+
+}
+
+```
+
+:::
+
+# Create Simulation Curve Data
+
+::: {.panel-tabset}
+
+## Saturated Curve
+
+```{r Create Simulated Data Saturated}
+
 saturation_simulated_database <-
@@
   tidyr::unnest("dilution_data")
-
 ```
 
-```{r}
-# exp_model <- sim_exponential(
-#     N = 200,    # total time units 
-#     y0 = 1,  # initial inoculum
-#     dt = 30,    #  interval between assessments in time units
-#     r = 0.02,  #  apparent infection rate
-#     #alpha = 0.01,# level of noise
-#     alpha = 0.2, # level of noise
-#     n = 1       # number of replicates
-#     )
-# 
-# exp_plot = exp_model %>%
-#   ggplot(aes(time, y)) +
-#   geom_jitter(aes(time, random_y), size = 3, width = .1) +
-#   geom_line(size = 1) +
-#   labs(
-#     title = "Exponential",
-#     y = "Disease intensity",
-#     x = "Time"
-#   )
-# exp_plot
-```
+## Limit of Detection Curve
 
-```{r LOD Many Data}
-
-simulate_lod <- function(id) {
-
-  exp_model <- sim_exponential(
-    N = 200,    # total time units 
-    y0 = 1,  # initial inoculum
-    dt = 30,    #  interval between assessments in time units
-    r = 0.02,  #  apparent infection rate
-    #alpha = 0.1, # level of noise
-    alpha = 0.15, # level of noise
-    n = 1       # number of replicates
-    )
-
-  lod_simulation <- tibble::tibble(
-    x = exp_model$time,
-    y = exp_model$random_y * sample(1:1000000, 1),
-    `Sample Name` = as.character(exp_model$time))
-
-  return(lod_simulation)
-
-}
+```{r Create Simulated Data LOD}
 
@@
   tidyr::unnest("dilution_data")
-
 ```
 
-```{r Linear Many Data}
+## Linear Curve
 
-simulate_lod <- function(id) {
+```{r Create Simulated Data Linear}
 
-  exp_model <- sim_exponential(
-    N = 200,    # total time units 
-    y0 = 1,  # initial inoculum
-    dt = 30,    #  interval between assessments in time units
-    r = 0.02,  #  apparent infection rate
-    #alpha = 0.1, # level of noise
-    alpha = 0.15, # level of noise
-    n = 1       # number of replicates
-    )
-
-  lod_simulation <- tibble::tibble(
-    x = exp_model$time,
-    y = exp_model$random_y * sample(1:1000000, 1),
-    `Sample Name` = as.character(exp_model$time))
-
-  return(lod_simulation)
-
-}
-
-lod_simulated_database <-
+linear_simulated_database <-
   tibble::tibble(
-    ID = paste("Limit Of Detection", 
+    ID = paste("Linear", 
                stringr::str_pad(1:200, width = 3, pad = "0")),
-    `Dilution Batch Name` = "Limit Of Detection"
+    `Dilution Batch Name` = "Linear"
 
@@
       .x = .data$ID,
-      .f = simulate_lod
+      .f = simulate_linear
       )
@@
   tidyr::unnest("dilution_data")
-
 ```
 
-```{r}
+:::
 
-# Create dilution statistical summary
-saturation_dilution_summary <- summarise_dilution_table(
-  saturation_simulated_database,
+# Create Statistical Summary
+
+::: {.panel-tabset}
+
+## Saturated Curve
+
+```{r dilution statistical summary saturated}
+saturation_dilution_summary <- DCVtestkit::summarise_dilution_table(
+  dilution_table = saturation_simulated_database,
   grouping_variable = c("ID"),
@@
 
-```{r}
+## Limit of Detection Curve
 
-lod_dilution_summary <- summarise_dilution_table(
-  lod_simulated_database,
+```{r dilution statistical summary lod}
+lod_dilution_summary <- DCVtestkit::summarise_dilution_table(
+  dilution_table = lod_simulated_database,
   grouping_variable = c("ID"),
@@
 
-```{r}
-saturation_ggplot_table <- add_ggplot_panel(
+## Linear Curve
+
+```{r dilution statistical summary linear}
+linear_dilution_summary <- DCVtestkit::summarise_dilution_table(
+  dilution_table = linear_simulated_database,
+  grouping_variable = c("ID"),
+  conc_var = "x",
+  signal_var = "y")
+
+```
+
+:::
+
+# Report plots as pdf files
+
+::: {.panel-tabset}
+
+## Saturated Curve
+
+```{r plots as pdf saturated}
+saturation_ggplot_table <- DCVtestkit::add_ggplot_panel(
   dilution_table = saturation_simulated_database,
@@
 
-view_ggplot_pdf(saturation_ggplot_list,
+DCVtestkit::view_ggplot_pdf(
+  ggplot_list = saturation_ggplot_list,
   filename = "dilution_plot_saturated.pdf",
@@
 
-```{r}
-lod_ggplot_table <- add_ggplot_panel(
+## Limit of Detection Curve
+
+```{r plots as pdf lod}
+lod_ggplot_table <- DCVtestkit::add_ggplot_panel(
   dilution_table = lod_simulated_database,
@@
 
-view_ggplot_pdf(lod_ggplot_list,
+DCVtestkit::view_ggplot_pdf(
+  ggplot_list = lod_ggplot_list,
   filename = "dilution_plot_lod.pdf",
@@
 
-```{r}
-# Create a trellis table
-saturation_trellis_table <- add_plotly_panel(
+## Linear Curve
+
+```{r plots as pdf linear}
+linear_ggplot_table <- DCVtestkit::add_ggplot_panel(
+  dilution_table = linear_simulated_database,
+  dilution_summary = linear_dilution_summary,
+  grouping_variable = c("ID"),
+  dil_batch_var = "Dilution Batch Name",
+  conc_var = "x",
+  signal_var = "y",
+  conc_var_units = ""
+  )
+
+linear_ggplot_list <- linear_ggplot_table$panel
+
+DCVtestkit::view_ggplot_pdf(
+  ggplot_list = linear_ggplot_list,
+  filename = "dilution_plot_linear.pdf",
+  ncol_per_page = 2,
+  nrow_per_page = 2)
+
+```
+
+:::
+
+# Report plots as trellis
+
+## Saturated Curve
+
+```{r plots as trellis saturated}
+saturation_trellis_table <- DCVtestkit::add_plotly_panel(
   dilution_table = saturation_simulated_database,
@@
 ) |> 
-  convert_to_cog(
+  DCVtestkit::convert_to_cog(
     grouping_variable = "ID",
@@
 
-view_trellis_html(
+DCVtestkit::view_trellis_html(
   trellis_table = saturation_trellis_table,
@@
 
-```{r}
-# Create a trellis table
-lod_trellis_table <- add_plotly_panel(
+## Limit of Detection Curve
+
+```{r plots as trellis lod}
+lod_trellis_table <- DCVtestkit::add_plotly_panel(
   dilution_table = lod_simulated_database,
@@
 
-view_trellis_html(
+DCVtestkit::view_trellis_html(
   trellis_table = lod_trellis_table,
@@
 ```
+
+## Linear Curve
+
+```{r plots as trellis linear}
+linear_trellis_table <- DCVtestkit::add_plotly_panel(
+  dilution_table = linear_simulated_database,
+  dilution_summary = linear_dilution_summary,
+  grouping_variable = c("ID"),
+  sample_name_var = "Sample Name",
+  dil_batch_var = "Dilution Batch Name",
+  dil_batch_col = c(
+    "#377eb8"),
+  conc_var = "x",
+  conc_var_units = "",
+  conc_var_interval = 50,
+  signal_var = "y",
+  have_plot_title = FALSE
+) |> 
+  DCVtestkit::convert_to_cog(
+    grouping_variable = "ID",
+    panel_variable = "panel",
+    col_name_vec = "col_name_vec",
+    desc_vec = "desc_vec",
+    type_vec = "type_vec"
+  )
+
+DCVtestkit::view_trellis_html(
+  trellis_table = linear_trellis_table,
+  grouping_variable = c("ID"),
+  trellis_report_name = "Dilution_Plot_Linear",
+  trellis_report_folder = "Dilution_Linear_Folder",
+  panel_variable = "panel"
+)
+```

### 2022-10-13 Manuscript/manuscript.qmd
Add manuscript

---
title: "*DCVtestkit*: an R package for analysis of quality control dilution curves"
bibliography: bibliography.bib
csl: bioinfo.csl
format: docx
---

## Manuscript Type

Application Note

# Abstract

## Summary

In a metabolomics and lipidomics workflow, a linear response in quality control dilution curves is used to assess the quality of molecules measured for further analysis. Current software tools only allow the analyst to repetitively plot, view and analyse the dilution curve one at a time which is a tedious and time-consuming process. In addition, summary statistics of dilution curves are limited to the Pearson Correlation Coefficient $R$ and/or Coefficient Of Determination $R^2$, which are insufficient to fully understand the shape of the dilution curves. `DCVtestkit` aims to provide additional summary statistics of dilution curves from various literatures which are not implemented in the current software tools. It also helps to reduce the analyst's workload by analysing many dilution curves automatically, reporting the statistical results in Excel and recording the dilution plots in a pdf file. In addition, it can also create an interactive trellis displayed as a HTML folder for analyst to do exploratory analysis on these dilution curve results.

## Availability and implementation

`DCVtestkit` is available on GitHub <https://github.com/SLINGhub/DCVtestkit>. The documentation and tutorials can be accessed from <https://slinghub.github.io/DCVtestkit/>

## Supplementary information

Supplementary data are available at *Bioinformatics* online.

## Issue Section

Data and text mining

# Introduction

Dilution curves have been used in many areas of biomedical and pharmaceutical sciences. In the field of metabolomics and lipidomics, quality control dilution curves for each molecule are plotted, as proposed by @croixmarie2009 to check if the sample matrix is the same among all samples. Molecules that do not have a linear relationship are rejected in spite of its relevance to the study. A cut off Pearson Correlation Coefficient value of $0.8$ was used to balance the risk of accepting spurious signals and removing signals related to important molecules. As such, many laboratories use commercial software to plot these dilution curves and report their corresponding off Pearson Correlation Coefficient value. These includes general purpose programs such as Excel and GraphPad Prism. Nevertheless, these general-purpose tools have their limitations.

While the Pearson Correlation Coefficient $R$ and/or Coefficient Of Determination $R^2$ are popular indicators of how well the dilution points fits a linear line, @sonnergaard2006 assets that these are not effective standalone numeric parameter to linearity. Using a modified version of Anscombe's quartet, the paper showed that a high coefficient of determination does not reflect a curve relationship well. Both @croixmarie2009 and @sands2021 support this view by indicating that an obvious non-linear response at the high and/or low ends of the diluted quality control sample dilution curve can still yield a high correlation coefficient. This is in agreement with @sanchez2021 findings of several saturated calibration curves with a $R$ value greater than $0.995$.

Fortunately, researcher who have studied deeply on model validation and misspecification have provided alternative graphical and statistical methods to improve the reliability of linearity assessment. For example, @vanloco2002 shared the presence of alternative statistics such as the Lack-of-fit test and quality coefficient that can be used to make better judgement on the shape of the dilution curve. While the progress in finding better metrics and algorithms to evaluate the linearity of dilution curve is commendable, these findings are rarely implemented in many general-purpose software.

In addition, with the advancement of technology in molecular identification coupled with a high emphasis on high throughput analysis and automation, today's targeted meatbolomics/lipidomics analysis can go as high as five hundred molecules being measured. This number can increase further in an untargeted approach. Using general-purpose programs to plot dilution curves for every single molecule may be tedious. Moreover, the report generated by these programs are static dilution plots coupled with statistical summary table. Having the analyst to look at five hundred dilution curves individually is time consuming and inefficient in understanding the data.

To address the issues mentioned above, we have created an R package, `DCVtestkit`, to assist analysts, not only to plot these dilution curves for many molecules easily, but also provided additional statistical results, other than the Pearson Correlation Coefficient $R$ or coefficient of determination $R^2$, for these curves. These alternative statistical results may be helpful in describing the shape the dilution curve possess. The R package also provide several ways of reporting the dilution data, including one as an interactive html file. This allows the analyst to group, filter and sort the dilution plots, to only look at the relevant ones, like saturated dilution curves, and identify problematic molecules quickly.

# General Workflow

Here, we introduce the workflow in which R package, `DCVtestkit`, follows.

![DCVtestkit Workflow](images/README-Workflow.png)

Beginning with the Input Data phase, the workflow starts with two tables: a table (Transition Signal Data) containing transition signals (y-axis for dilution curve) for each sample and a table (Dilution Annotation) containing dilution curve related information for each sample, such as concentration (x-axis for dilution curve) and dilution batches. As, the two tables share the same sample list, it can be merged together into one table (Dilution Table) using the function `create_dilution_table`.

During the Calculation stage of the workflow, the summary statistics are calculated using the function `summarise_dilution_table` for each dilution curve corresponding to a dilution batch and transition. Optionally, analysts can use the function `evaluate_linearity` to group the dilution curves based on the summary statistics. These tabular results can be reported as an Excel sheet using the function `write_summary_excel`.

With the summary statistics results, the workflow can proceed to the Dilution Curve Plotting phase in which static and interactive dilution plots can be created using `add_ggplot_panel` and `add_plotly_panel` respectively. Static plots are output as a pdf file while the interactive plots are output as a HTML folder containing several folders and one `index.html` file. Analysts can view the interactive plots by double clicking on the `index.html` file.

# Statistical Summary for Dilution Curves

To address the paucity of parameters describing the goodness-of-fit of linear dilution curves, a few additional parameters are added in the R package `DCVtestkit`, on top of the popular Pearson Correlation Coefficient $R$ on a linear regression fit. Currently, the additional parameters are statistical results from Mandel's Fitting Test in @andrade2013 and the Percent Residual Accuracy in @logue2018. The software also fits a quadratic model on the dilution curve and calculates the concavity of the quadratic model to identify to verify if the dilution curve is predominantly non-linear at high or low concentrations.

Given an example linear curve, saturated curve and a curve with limit of detection (LOD) and their corresponding summary statistics, it can be observed that the corresponding Pearson Correlation Coefficient `r_corr` are really high $\ge0.9$ even for the curves that are non-linear. On the other hand, both the saturated and LOD curves give a much lower Mandel's Fitting Test p values `mandel_p_val` and Percent Residual Accuracy `pra_linear` values than the linear curve.

```{r Motivation, echo = FALSE}
linear_data <- data.frame(
  conc_var = c(10, 25, 40, 50, 60,
               75, 80, 100, 125, 150),
  signal_var = c(25463, 63387, 90624, 131274, 138069,
                 205353, 202407, 260205, 292257, 367924)
)

saturated_data <- data.frame(
  conc_var = c(10, 25, 40, 50, 60,
               75, 80, 100, 125, 150),
  signal_var = c(5192648, 16594991, 32507833, 46499896,
                 55388856, 62505210, 62778078, 72158161,
                 78044338, 86158414)
)

lod_data <- data.frame(
  conc_var = c(10, 25, 40, 50, 60,
               75, 80, 100, 125, 150),
  signal_var = c(500, 903, 1267, 2031, 2100,
                 3563, 4500, 5300, 8500, 10430)
)

tabular_display <- tibble::tibble(
  Concentration = c(10, 25, 40, 50, 60,
                    75, 80, 100, 125, 150), 
  `Linear\nsignal` = c(25463, 63387, 90624, 131274, 138069,
                    205353, 202407, 260205, 292257, 367924),
  `Saturated\nsignal` = c(5192648, 16594991, 32507833, 46499896,
                       55388856, 62505210, 62778078, 72158161,
                       78044338, 86158414),
  `Lod\nsignal` = c(500, 903, 1267, 2031, 2100,
                 3563, 4500, 5300, 8500, 10430)
)

concentration_table <- gridExtra::tableGrob(
  d = tabular_display, 
  rows = NULL,
  theme = gridExtra::ttheme_default(
    core=list(fg_params=list(hjust=1, x=0.9))
    )
  ) 
```

```{r create linear plot, echo = FALSE}
# Get dilution summary
statistical_summary <- DCVtestkit::summarise_dilution_data(
  linear_data, 
  "conc_var", 
  "signal_var")

table <- DCVtestkit::plot_summary_table(statistical_summary)

# Model the data
linear_model <- DCVtestkit::create_linear_model(linear_data, 
                                                "conc_var", "signal_var")
quad_model <- DCVtestkit::create_quad_model(linear_data, 
                                            "conc_var", "signal_var")

dilution <- seq(min(linear_data$conc_var, na.rm = TRUE),
                max(linear_data$conc_var, na.rm = TRUE),
                length.out = 15)

# Create the y values for the line
y_lin_predict <- stats::predict(linear_model,
                                tibble::tibble("conc_var" := dilution))
y_quad_predict <- stats::predict(quad_model,
                                 tibble::tibble("conc_var" := dilution))
reg_data <- data.frame(
  dilution = dilution,
  y_lin_predict = y_lin_predict,
  y_quad_predict = y_quad_predict
)

reg_col_vec <- c("Lin" = "black", "Quad" = "red")

linear_plot <- ggplot2::ggplot(linear_data) +
  ggplot2::aes(x = .data$conc_var,
               y = .data$signal_var
               ) +
    ggplot2::geom_point(size = 5, colour = "#746ab0") +
  ggplot2::geom_line(data = reg_data,
                           mapping = ggplot2::aes(x = dilution, y=y_lin_predict,
                                                  colour = "Lin")
        ) +
  ggplot2::geom_line(data = reg_data,
                     mapping = ggplot2::aes(x = dilution, y=y_quad_predict,
                                            colour = "Quad")
  ) +
  ggplot2::scale_colour_manual(values = c(reg_col_vec),
                               labels = names(c(reg_col_vec)),
                               guide = ggplot2::guide_legend(override.aes = list(
                                 linetype = c(rep("solid", length(reg_col_vec))),
                                 shape = c(rep(NA, length(reg_col_vec))),
                                 colour = c(reg_col_vec)
                               ))
    ) +
  ggplot2::theme(
    legend.title = ggplot2::element_blank(),
    legend.position = "top",
    axis.title.y = ggplot2::element_text(angle = 0,
                                         vjust = 1)
  ) +
  ggplot2::labs(title = "Linear",
                x = "Concentration",
                y = "Signal")

linear_plot <- patchwork::wrap_plots(linear_plot, table, ncol = 2, nrow = 1)
```

```{r create saturation plot, echo = FALSE}
# Get dilution summary
statistical_summary <- DCVtestkit::summarise_dilution_data(
  saturated_data, 
  "conc_var", 
  "signal_var")

table <- DCVtestkit::plot_summary_table(statistical_summary)

# Model the data
linear_model <- DCVtestkit::create_linear_model(saturated_data, 
                                                "conc_var", "signal_var")
quad_model <- DCVtestkit::create_quad_model(saturated_data, 
                                            "conc_var", "signal_var")

dilution <- seq(min(saturated_data$conc_var, na.rm = TRUE),
                max(saturated_data$conc_var, na.rm = TRUE),
                length.out = 15)

# Create the y values for the line
y_lin_predict <- stats::predict(linear_model,
                                tibble::tibble("conc_var" := dilution))
y_quad_predict <- stats::predict(quad_model,
                                 tibble::tibble("conc_var" := dilution))
reg_data <- data.frame(
  dilution = dilution,
  y_lin_predict = y_lin_predict,
  y_quad_predict = y_quad_predict
)

reg_col_vec <- c("Lin" = "black", "Quad" = "red")

saturation_plot <- ggplot2::ggplot(saturated_data) +
  ggplot2::aes(x = .data$conc_var,
               y = .data$signal_var
               ) +
    ggplot2::geom_point(size = 5, colour = "#377eb8") +
  ggplot2::geom_line(data = reg_data,
                           mapping = ggplot2::aes(x = dilution, y=y_lin_predict,
                                                  colour = "Lin")
        ) +
  ggplot2::geom_line(data = reg_data,
                     mapping = ggplot2::aes(x = dilution, y=y_quad_predict,
                                            colour = "Quad")
  ) +
  ggplot2::scale_colour_manual(values = c(reg_col_vec),
                               labels = names(c(reg_col_vec)),
                               guide = ggplot2::guide_legend(override.aes = list(
                                 linetype = c(rep("solid", length(reg_col_vec))),
                                 shape = c(rep(NA, length(reg_col_vec))),
                                 colour = c(reg_col_vec)
                               ))
    ) +
  ggplot2::theme(
    legend.title = ggplot2::element_blank(),
    legend.position = "top",
    axis.title.y = ggplot2::element_text(angle = 0,
                                         vjust = 1)
  ) +
  ggplot2::labs(title = "Saturation",
                x = "Concentration",
                y = "Signal")

saturation_plot <- patchwork::wrap_plots(saturation_plot, table, ncol = 2, nrow = 1)
```

```{r create lod plot, echo = FALSE}
# Get dilution summary
statistical_summary <- DCVtestkit::summarise_dilution_data(
  lod_data, 
  "conc_var", 
  "signal_var")

table <- DCVtestkit::plot_summary_table(statistical_summary)

# Model the data
linear_model <- DCVtestkit::create_linear_model(lod_data, 
                                                "conc_var", "signal_var")
quad_model <- DCVtestkit::create_quad_model(lod_data, 
                                            "conc_var", "signal_var")

dilution <- seq(min(lod_data$conc_var, na.rm = TRUE),
                max(lod_data$conc_var, na.rm = TRUE),
                length.out = 15)

# Create the y values for the line
y_lin_predict <- stats::predict(linear_model,
                                tibble::tibble("conc_var" := dilution))
y_quad_predict <- stats::predict(quad_model,
                                 tibble::tibble("conc_var" := dilution))
reg_data <- data.frame(
  dilution = dilution,
  y_lin_predict = y_lin_predict,
  y_quad_predict = y_quad_predict
)

reg_col_vec <- c("Lin" = "black", "Quad" = "red")

lod_plot <- ggplot2::ggplot(lod_data) +
  ggplot2::aes(x = .data$conc_var,
               y = .data$signal_var
               ) +
    ggplot2::geom_point(size = 5, colour = "#4daf4a") +
  ggplot2::geom_line(data = reg_data,
                           mapping = ggplot2::aes(x = dilution, y=y_lin_predict,
                                                  colour = "Lin")
        ) +
  ggplot2::geom_line(data = reg_data,
                     mapping = ggplot2::aes(x = dilution, y=y_quad_predict,
                                            colour = "Quad")
  ) +
  ggplot2::scale_colour_manual(values = c(reg_col_vec),
                               labels = names(c(reg_col_vec)),
                               guide = ggplot2::guide_legend(override.aes = list(
                                 linetype = c(rep("solid", length(reg_col_vec))),
                                 shape = c(rep(NA, length(reg_col_vec))),
                                 colour = c(reg_col_vec)
                               ))
    ) +
  ggplot2::theme(
    legend.title = ggplot2::element_blank(),
    legend.position = "top",
    axis.title.y = ggplot2::element_text(angle = 0,
                                         vjust = 1)
  ) +
  ggplot2::labs(title = "LOD",
                x = "Concentration",
                y = "Signal")

lod_plot <- patchwork::wrap_plots(lod_plot, table, ncol = 2, nrow = 1)
```

```{r ViewMotivationData1, echo = FALSE, fig.height=9, fig.width=13, fig.cap = "Plots and statistical results of three curves: Linear curve, Saturated curve and a curve with Limit Of Detection (LOD)"}
patchwork::wrap_plots(concentration_table, linear_plot, saturation_plot, lod_plot, ncol = 2, nrow = 2)
```

The Mandel's Fitting Test and Percent Residual Accuracy findings are also in agreement with the results from @vanloco2002 and @logue2018 respectively, highlighting that these two alternative parameters are more sensitive and advantageous than the Pearson Correlation Coefficient in their calibration curves and simulated experiments.

# Dilution Curve Grouping

`DCVtestkit` uses the function `evaluate_linearity` to group the dilution curves. At this moment, two workflows are proposed.

![Dilution Curve Grouping Workflow](images/README-LinearEvaluation.png)

While the threshold values given for Pearson Correlation Coefficient and Percent Residual Accuracy are based on @y.h.chan2003 and @logue2018 interpretation respectfully, it remains subjective and arbitrary. Moreover, it is also possible for the dilution curve to exhibit a sigmoidal relationship, or non-linear at both low and high concentrations, which the proposed workflow is unable to identify.

Nevertheless, while the proposed workflow is not infallible, `DCVtestkit` allows the analyst to change and optimise these threshold values to suit the congruency of the analyst's opinion about linearity and saturation of dilution curves. More information on how to perform such customisation can be found in the program documentation titled: ["Customise Linearity Evaluation Workflow"](https://slinghub.github.io/DCVtestkit/articles/lineval-customization.html) Furthermore, it is also possible to output these statistical summaries in Excel without the classification results.

# Results Distribution

Lastly, `DCVtestkit` is able export the statistical results of each dilution curve in Excel. Furthermore, it can report the list of dilution plots as static charts with statistical summary results on the side in a single pdf file.

As some may find a pdf file to be too complex for further interpretation, the R package also provides an interactive viewer as a HTML folder to look at dilution plots in a trellis display framework, as introduced in @becker1996. Clicking on the `index.html` file inside the folder will open the interactive viewer that allows the analysts to group, filter and sort these trellis charts in a meaningful way based using @hafen2013 definition of "cognostics" or computer guiding diagnostics. This provides the analysts to be able to do exploratory data analysis such as identifying groups of molecules with linearity issues or finding out the effects of changing the Pearson Correlation Coefficient to another value. Such tasks can be challenging and time consuming if only the Excel and pdf files full of static plots are provided.

![Viewing Several Interactive Dilution Curves](images/README-TrellisOutput.png)

An example of an interactive viewer created by `DCVtestkit` can be accessed from <https://dcvtestkit-interactive-example.netlify.app/>. Such interactive visualisation was also utilised by @hafen2019 in the exploration of proteomics, metabolomics, and lipidomics data in a multi-omics fashion. The HTML folder can be compressed as a zip file and distributed to others like a pdf or Excel file. This interactive viewer can also be displayed in as a report created from Quarto (https://quarto.org/), an open-source scientific and technical publishing system. The report can be viewed at <https://dcvtestkit-quarto-example.netlify.app/>

R script and result outputs can be found in the Supplementary Material or by accessing this GitHub page <https://github.com/JauntyJJS/DCVtestkit_Output>

# Conclusion

A linear response in quality control dilution curves is one of the many checks used in metabolomics and lipidomics to assess the suitability of the molecules measured for further analysis. Despite its importance in providing high quality data, the shortage of software tools to analyse many dilution curves effectively and efficiently prevents researchers from doing it. An R package called `DCVtestkit` is created to rectify this issue by allowing many dilution curves to be analysed quickly and reliably. This is done by the use of alternative statistics, other than the Pearson Correlation Coefficient, to better understand the linearity of the dilution curves as well as reporting of statistical results and dilution plots that can be distributed to others. It is also able to provide an interactive trellis plot for exploratory data analysis. The R package is available on GitHub <https://github.com/SLINGhub/DCVtestkit> while the documentation and tutorials can be accessed from <https://slinghub.github.io/DCVtestkit/>. As `DCVtestkit` is an opensource software, it is accessible to collaboration works which can help improve its usability and performance in the future.

# Acknowledgements

These should be included at the end of the text and not in footnotes. Please ensure you acknowledge all sources of funding, see funding section below.

Details of all funding sources for the work in question should be given in a separate section entitled 'Funding'. This should appear before the 'Acknowledgements' section.

# Funding

The following rules should be followed:

-   The sentence should begin: 'This work was supported by ...' -
-   The full official funding agency name should be given, i.e. 'National Institutes of Health', not 'NIH' (full RIN-approved list of UK funding agencies)
-   Grant numbers should be given in brackets as follows: '[grant number xxxx]'
-   Multiple grant numbers should be separated by a comma as follows: '[grant numbers xxxx, yyyy]'
-   Agencies should be separated by a semi-colon (plus 'and' before the last funding agency)
-   Where individuals need to be specified for certain sources of funding the following text should be added after the relevant agency or grant number 'to [author initials]'.

An example is given here: 'This work was supported by the National Institutes of Health [AA123456 to C.S., BB765432 to M.H.]; and the Alcohol & Education Research Council [hfygr667789].'

Oxford Journals will deposit all NIH-funded articles in PubMed Central. See Depositing articles in repositories -- information for authors for details. Authors must ensure that manuscripts are clearly indicated as NIH-funded using the guidelines above.

# References

### 2022-10-13 Manuscript/manuscript.qmd
Add a news files.

@@
 -   The full official funding agency name should be given, i.e. 'National Institutes of Health', not 'NIH' (full RIN-approved list of UK funding agencies)
--   Grant numbers should be given in brackets as follows: '[grant number xxxx]'
--   Multiple grant numbers should be separated by a comma as follows: '[grant numbers xxxx, yyyy]'
+-   Grant numbers should be given in brackets as follows: '\[grant number xxxx\]'
+-   Multiple grant numbers should be separated by a comma as follows: '\[grant numbers xxxx, yyyy\]'
 -   Agencies should be separated by a semi-colon (plus 'and' before the last funding agency)
--   Where individuals need to be specified for certain sources of funding the following text should be added after the relevant agency or grant number 'to [author initials]'.
+-   Where individuals need to be specified for certain sources of funding the following text should be added after the relevant agency or grant number 'to \[author initials\]'.
 
-An example is given here: 'This work was supported by the National Institutes of Health [AA123456 to C.S., BB765432 to M.H.]; and the Alcohol & Education Research Council [hfygr667789].'
+An example is given here: 'This work was supported by the National Institutes of Health \[AA123456 to C.S., BB765432 to M.H.\]; and the Alcohol & Education Research Council \[hfygr667789\].'
 

### 2022-10-13 Manuscript/manuscript.qmd
Update the Summary to Federico's correction.

@@
 
-In a metabolomics and lipidomics workflow, a linear response in quality control dilution curves is used to assess the quality of molecules measured for further analysis.
-Current software tools only allow the analyst to repetitively plot, view and analyse the dilution curve one at a time which is a tedious and time-consuming process.
+In metabolomic and lipidomic workflows, a linear response in dilution series generated from pooled quality control (QC) samples is used to assess the quality of the measurement of molecules measured before further analysis.
+Most of the currently used software only allow the analyst to repetitively plot, view and analyse the dilution curves one at a time, a tedious and time-consuming process.
 In addition, summary statistics of dilution curves are limited to the Pearson Correlation Coefficient $R$ and/or Coefficient Of Determination $R^2$, which are insufficient to fully understand the shape of the dilution curves.
-`DCVtestkit` aims to provide additional summary statistics of dilution curves from various literatures which are not implemented in the current software tools.
-It also helps to reduce the analyst's workload by analysing many dilution curves automatically, reporting the statistical results in Excel and recording the dilution plots in a pdf file.
-In addition, it can also create an interactive trellis displayed as a HTML folder for analyst to do exploratory analysis on these dilution curve results.
+DCVtestkit aims to provide additional summary statistics for dilution curves, taken from previous publications but which are not implemented in the current software tools.
+It also helps to reduce the analyst’s workload by analysing many dilution curves automatically, reporting the statistical results in Excel and recording the dilution plots in a pdf file.
+In addition, it can also create an interactive trellis displayed as a HTML folder for more exploratory analyses.
 

### 2022-10-13 Manuscript/manuscript.qmd

@@
 Dilution curves have been used in many areas of biomedical and pharmaceutical sciences.
-In the field of metabolomics and lipidomics, quality control dilution curves for each molecule are plotted, as proposed by @croixmarie2009 to check if the sample matrix is the same among all samples.
-Molecules that do not have a linear relationship are rejected in spite of its relevance to the study.
-A cut off Pearson Correlation Coefficient value of $0.8$ was used to balance the risk of accepting spurious signals and removing signals related to important molecules.
-As such, many laboratories use commercial software to plot these dilution curves and report their corresponding off Pearson Correlation Coefficient value.
-These includes general purpose programs such as Excel and GraphPad Prism.
-Nevertheless, these general-purpose tools have their limitations.
+In the field of metabolomics and lipidomics, dilution curves for each molecule measured, usually in a quality control sample generated by pooling equal aliquots from each study sample, are plotted as proposed by @croixmarie2009 to check if the sample matrix is the same among all samples.
+Molecules that do not show a linear dilution curve can be rejected before further statistical analysis, in spite of their relevance to the study, as their quantitation in different sample groups might be compromised.
+A cut off Pearson Correlation Coefficient value of $0.8$ is commonly used to balance the risk of accepting or removing signals related to relevant molecules.
+As such, many laboratories use commercial software to plot these dilution curves and report their corresponding Pearson Correlation Coefficient value.
+These include either mass spectrometry vendors’ software or, more in general, programs such as Excel and GraphPad Prism.
+Nevertheless, these tools have limitations.
 
-While the Pearson Correlation Coefficient $R$ and/or Coefficient Of Determination $R^2$ are popular indicators of how well the dilution points fits a linear line, @sonnergaard2006 assets that these are not effective standalone numeric parameter to linearity.
-Using a modified version of Anscombe's quartet, the paper showed that a high coefficient of determination does not reflect a curve relationship well.
-Both @croixmarie2009 and @sands2021 support this view by indicating that an obvious non-linear response at the high and/or low ends of the diluted quality control sample dilution curve can still yield a high correlation coefficient.
-This is in agreement with @sanchez2021 findings of several saturated calibration curves with a $R$ value greater than $0.995$.
+While the Pearson Correlation Coefficient $R$ and/or Coefficient Of Determination $R^2$ are popular indicators of how well the dilution points fits a linear line, @sonnergaard2006 estimated that these are not effective standalone numeric parameter to estimate linearity.
+Using a modified version of Anscombe’s quartet, the paper showed that a high coefficient of determination does not reflect well a curve relationship.
+Both @croixmarie2009 and @sands2021 support this view, by indicating that an obvious non-linear response at the high and/or low ends of the quality control sample-based dilution curve can still yield a high correlation coefficient.
+This is in agreement with @sanchez2021 findings of several saturated calibration curves with $R$ values greater than $0.995$.
 
-Fortunately, researcher who have studied deeply on model validation and misspecification have provided alternative graphical and statistical methods to improve the reliability of linearity assessment.
-For example, @vanloco2002 shared the presence of alternative statistics such as the Lack-of-fit test and quality coefficient that can be used to make better judgement on the shape of the dilution curve.
-While the progress in finding better metrics and algorithms to evaluate the linearity of dilution curve is commendable, these findings are rarely implemented in many general-purpose software.
+Fortunately, researchers who have studied deeply model validation and misspecification have provided alternative graphical and statistical methods to improve the reliability of linearity assessments.
+For example, @vanloco2002 highlighted the presence of alternative statistics, such as the Lack-of-fit test and quality coefficient, that can be used to make better judgement on the shape of the dilution curve.
+While the progress in finding better metrics and algorithms to evaluate the linearity of dilution curves is commendable, these findings are rarely implemented in more general-purpose software.
 
-In addition, with the advancement of technology in molecular identification coupled with a high emphasis on high throughput analysis and automation, today's targeted meatbolomics/lipidomics analysis can go as high as five hundred molecules being measured.
-This number can increase further in an untargeted approach.
-Using general-purpose programs to plot dilution curves for every single molecule may be tedious.
-Moreover, the report generated by these programs are static dilution plots coupled with statistical summary table.
-Having the analyst to look at five hundred dilution curves individually is time consuming and inefficient in understanding the data.
+In addition, with the advancement of the technology used for molecular identification coupled with a high emphasis on high throughput analysis and automation, today’s targeted metabolomics/lipidomics can include more than eight hundred analytes measured by a single method.
+This number can also increase further in an untargeted approach.
+In these cases, using general-purpose programs to plot dilution curves for every single molecule may be tedious.
+Moreover, the reports generated by these programs are static dilution plots coupled with a statistical summary table.
+Having the analyst to look at five hundred dilution curves individually is time consuming and inefficient for data evaluation.
 
-To address the issues mentioned above, we have created an R package, `DCVtestkit`, to assist analysts, not only to plot these dilution curves for many molecules easily, but also provided additional statistical results, other than the Pearson Correlation Coefficient $R$ or coefficient of determination $R^2$, for these curves.
-These alternative statistical results may be helpful in describing the shape the dilution curve possess.
-The R package also provide several ways of reporting the dilution data, including one as an interactive html file.
-This allows the analyst to group, filter and sort the dilution plots, to only look at the relevant ones, like saturated dilution curves, and identify problematic molecules quickly.
+To address the issues mentioned above, we have created an R package, DCVtestkit, to assist analysts, not only to plot these dilution curves for many molecules easily but also providing additional statistical results, other than the Pearson Correlation Coefficient $R$ or coefficient of determination $R^2$, for these curves.
+These alternative statistical results may be helpful in better describing the shape of the dilution curve.
+The R package also provides several ways of reporting the dilution data, including an interactive html file.
+This allows the analyst to group, filter and sort the dilution plots, to only look at the relevant ones, such as the saturated dilution curves, and identify problematic molecules quickly.
 
@@
 
-Here, we introduce the workflow in which R package, `DCVtestkit`, follows.
+Here, we introduce the workflow in which R package, DCVtestkit.
 

### 2022-10-13 Manuscript/manuscript.qmd
Update manuscript with the changes recommended by reviewer.

@@
 
-`DCVtestkit` is available on GitHub <https://github.com/SLINGhub/DCVtestkit>. The documentation and tutorials can be accessed from <https://slinghub.github.io/DCVtestkit/>
+*DCVtestkit* is available on GitHub <https://github.com/SLINGhub/DCVtestkit>. The documentation and tutorials can be accessed from <https://slinghub.github.io/DCVtestkit/>
 
@@
 
-To address the issues mentioned above, we have created an R package, DCVtestkit, to assist analysts, not only to plot these dilution curves for many molecules easily but also providing additional statistical results, other than the Pearson Correlation Coefficient $R$ or coefficient of determination $R^2$, for these curves.
+To address the issues mentioned above, we have created an R package, *DCVtestkit*, to assist analysts, not only to plot these dilution curves for many molecules easily but also providing additional statistical results, other than the Pearson Correlation Coefficient $R$ or coefficient of determination $R^2$, for these curves.
 These alternative statistical results may be helpful in better describing the shape of the dilution curve.
@@
 
-Here, we introduce the workflow in which R package, DCVtestkit.
+Here, we introduce the workflow used by our R package, *DCVtestkit* in @fig-DCVtestkit-Workflow.
 
-![DCVtestkit Workflow](images/README-Workflow.png)
+::: {#fig-DCVtestkit-Workflow layout-ncol=1}
+
+![](images/README-Workflow.png)
+
+*DCVtestkit* Workflow
+:::
 
@@
 
-To address the paucity of parameters describing the goodness-of-fit of linear dilution curves, a few additional parameters are added in the R package `DCVtestkit`, on top of the popular Pearson Correlation Coefficient $R$ on a linear regression fit.
-Currently, the additional parameters are statistical results from Mandel's Fitting Test in @andrade2013 and the Percent Residual Accuracy in @logue2018.
-The software also fits a quadratic model on the dilution curve and calculates the concavity of the quadratic model to identify to verify if the dilution curve is predominantly non-linear at high or low concentrations.
+@fig-curves gives a plot of three manually curated curves together with their corresponding summary statistics.
+The characteristic of three curves are as follows: One is a linear curve.
+Another is having a plateau at higher concentrations, also known as a saturated curve.
+The last example is a curve with a plateau at lower concentrations or experiencing a limit of detection (denoted as LOD curves in this paper).
+It can be observed that the corresponding Pearson Correlation Coefficient values, denoted as `r_corr`, are $\ge0.9$ ($0.99$, $0.95$ and $0.98$ respectively) even for the curves that are non-linear.
+These results are in agreement with @vanloco2002 as well as @logue2018 arguments that the Pearson Correlation Coefficient is a poor descriptor of non-linear calibration curves.
 
-Given an example linear curve, saturated curve and a curve with limit of detection (LOD) and their corresponding summary statistics, it can be observed that the corresponding Pearson Correlation Coefficient `r_corr` are really high $\ge0.9$ even for the curves that are non-linear.
-On the other hand, both the saturated and LOD curves give a much lower Mandel's Fitting Test p values `mandel_p_val` and Percent Residual Accuracy `pra_linear` values than the linear curve.
+To improve the description of the goodness-of-fit for linear dilution curves, a few additional parameters, on top of the popular Pearson Correlation Coefficient $R$, are added in the R package *DCVtestkit*.
+The first additional parameters are statistical results from Mandel’s Fitting Test (as reported in @andrade2013) in which a low $p$ value gives sufficient evidence that a quadratic model is a better fit than a linear model, indicating the curve may not be linear.
+Another parameter calculated is the Percent Residual Accuracy (as reported in @logue2018) which ranges from $-\infty$ to $100$.
+If the curve is linear, the value should be close to $100$.
+Finally, the software also fits a quadratic model on the dilution curve and calculates the concavity, trying to verify if the dilution curve is predominantly non-linear at high (concavity $<0$) or low (concavity $>0$) concentrations.
+
+Returning to @fig-curves, both the saturated and LOD curves give a much lower Mandel’s Fitting Test $p$ values, denoted as `mandel_p_val`, ($1.66 * 10^{-4}$ and $2.56 * 10^{-3}$ respectively vs $0.38$).
+Correspondingly, ranging from $-\infty$ to $100$, the Percent Residual Accuracy values, denoted as `pra_linear`, are much lower in the saturated and LOD curves compared to the linear curve ($62.30$ and $74.69$ respectively vs $94.32$).
 
 ```{r Motivation, echo = FALSE}
+#| echo: false
+
 linear_data <- data.frame(
@@
                     75, 80, 100, 125, 150), 
-  `Linear\nsignal` = c(25463, 63387, 90624, 131274, 138069,
+  `Linear signal` = c(25463, 63387, 90624, 131274, 138069,
                     205353, 202407, 260205, 292257, 367924),
-  `Saturated\nsignal` = c(5192648, 16594991, 32507833, 46499896,
+  `Saturated signal` = c(5192648, 16594991, 32507833, 46499896,
                        55388856, 62505210, 62778078, 72158161,
                        78044338, 86158414),
-  `Lod\nsignal` = c(500, 903, 1267, 2031, 2100,
+  `LOD signal` = c(500, 903, 1267, 2031, 2100,
                  3563, 4500, 5300, 8500, 10430)
@@
 
-```{r create linear plot, echo = FALSE}
+```{r create linear plot}
+#| echo: false
+
 # Get dilution summary
@@
 
-```{r create saturation plot, echo = FALSE}
+```{r create saturation plot}
+#| echo: false
+
 # Get dilution summary
@@
 
-```{r create lod plot, echo = FALSE}
+```{r create lod plot}
+#| echo: false
+
 # Get dilution summary
@@
 
-```{r ViewMotivationData1, echo = FALSE, fig.height=9, fig.width=13, fig.cap = "Plots and statistical results of three curves: Linear curve, Saturated curve and a curve with Limit Of Detection (LOD)"}
-patchwork::wrap_plots(concentration_table, linear_plot, saturation_plot, lod_plot, ncol = 2, nrow = 2)
+```{r ViewMotivationData1}
+#| echo: false
+#| label: fig-curves
+#| fig-height: 9
+#| fig-width: 13
+#| fig-cap: "Plots and statistical results of three curves: Linear curve, Saturated curve and a curve with Limit Of Detection (LOD)"
+
+patchwork::wrap_plots(
+  concentration_table, 
+  linear_plot, 
+  saturation_plot, 
+  lod_plot, 
+  ncol = 2, 
+  nrow = 2
+)
 ```
-
-The Mandel's Fitting Test and Percent Residual Accuracy findings are also in agreement with the results from @vanloco2002 and @logue2018 respectively, highlighting that these two alternative parameters are more sensitive and advantageous than the Pearson Correlation Coefficient in their calibration curves and simulated experiments.
 
@@
 
-`DCVtestkit` uses the function `evaluate_linearity` to group the dilution curves. At this moment, two workflows are proposed.
+*DCVtestkit* uses the function `evaluate_linearity` to group the dilution curves. At this moment, two workflows are proposed.
 
-![Dilution Curve Grouping Workflow](images/README-LinearEvaluation.png)
+::: {#fig-Dilution-Grouping-Workflow layout-ncol=1}
 
-While the threshold values given for Pearson Correlation Coefficient and Percent Residual Accuracy are based on @y.h.chan2003 and @logue2018 interpretation respectfully, it remains subjective and arbitrary.
-Moreover, it is also possible for the dilution curve to exhibit a sigmoidal relationship, or non-linear at both low and high concentrations, which the proposed workflow is unable to identify.
+![](images/README-LinearEvaluation.png)
 
-Nevertheless, while the proposed workflow is not infallible, `DCVtestkit` allows the analyst to change and optimise these threshold values to suit the congruency of the analyst's opinion about linearity and saturation of dilution curves.
-More information on how to perform such customisation can be found in the program documentation titled: ["Customise Linearity Evaluation Workflow"](https://slinghub.github.io/DCVtestkit/articles/lineval-customization.html) Furthermore, it is also possible to output these statistical summaries in Excel without the classification results.
+Dilution Curve Grouping Workflows
+:::
+
+While the threshold values given for Pearson Correlation Coefficient and Percent Residual Accuracy are based on the interpretation given by @y.h.chan2003 and @logue2018, respectively, it remains subjective and arbitrary.
+Moreover, it is also possible for the dilution curve to exhibit a sigmoidal relationship, or non-linear, at both low and high concentrations, which the proposed workflow would be unable to identify.
+
+Nevertheless, while the proposed workflow is not a perfect solution, *DCVtestkit* allows the analyst to change and optimise the threshold values, to adjust the determinants of linearity and saturation of dilution curves according to the user’s needs.
+More information on how to perform such customisation can be found in the program documentation titled: ["Customise Linearity Evaluation Workflow"](https://slinghub.github.io/DCVtestkit/articles/lineval-customization.html).
+Furthermore, it is also possible to output these statistical summaries in Excel without the classification results.
 
@@
 
-Lastly, `DCVtestkit` is able export the statistical results of each dilution curve in Excel.
-Furthermore, it can report the list of dilution plots as static charts with statistical summary results on the side in a single pdf file.
+Lastly, *DCVtestkit* can export the statistical results of each dilution curve in Excel.
+Furthermore, it can report the list of dilution plots as static charts with the statistical summary results included in a single pdf file.
 
-As some may find a pdf file to be too complex for further interpretation, the R package also provides an interactive viewer as a HTML folder to look at dilution plots in a trellis display framework, as introduced in @becker1996.
-Clicking on the `index.html` file inside the folder will open the interactive viewer that allows the analysts to group, filter and sort these trellis charts in a meaningful way based using @hafen2013 definition of "cognostics" or computer guiding diagnostics.
-This provides the analysts to be able to do exploratory data analysis such as identifying groups of molecules with linearity issues or finding out the effects of changing the Pearson Correlation Coefficient to another value.
-Such tasks can be challenging and time consuming if only the Excel and pdf files full of static plots are provided.
+As some may find the final pdf file too complex for further interpretation, the R package also provides an interactive viewer, as a HTML folder, to look at dilution plots in a trellis display framework, as introduced in @becker1996.
+Clicking on the `index.html` file inside the folder will open the interactive viewer that allows the user to group, filter and sort these trellis charts in a meaningful way, based on @hafen2013's definition of "cognostics" or computer guiding diagnostics.
+This allows the user to do exploratory data analysis, such as identifying groups of molecules with linearity issues or finding out the effects of changing the Pearson Correlation Coefficient to another value.
+Such tasks can be challenging and time consuming if only the Excel and pdf files full of static plots were provided.
 
-![Viewing Several Interactive Dilution Curves](images/README-TrellisOutput.png)
+::: {#fig-Viewing-Interactive-Curves layout-ncol=1}
 
-An example of an interactive viewer created by `DCVtestkit` can be accessed from <https://dcvtestkit-interactive-example.netlify.app/>.
+![](images/README-TrellisOutput.png)
+
+Viewing Several Interactive Dilution Curves
+:::
+
+An example of an interactive viewer created by *DCVtestkit* can be accessed from <https://dcvtestkit-interactive-example.netlify.app/>.
+Such interactive visualisation was also utilised by @hafen2019 in the exploration of proteomics, metabolomics and lipidomics data in a multi-omics approach.
+The HTML folder can be compressed as a zip file and shared as a pdf or Excel file.
+This interactive viewer can also be displayed as a report created from Quarto (https://quarto.org/), an open-source scientific and technical publishing system.
+The report can be viewed at <https://dcvtestkit-quarto-example.netlify.app/>
+R script and result outputs can be found in the Supplementary Material or by accessing this GitHub page <https://github.com/JauntyJJS/DCVtestkit_Output>
+
+An example of an interactive viewer created by *DCVtestkit* can be accessed from <https://dcvtestkit-interactive-example.netlify.app/>.
 Such interactive visualisation was also utilised by @hafen2019 in the exploration of proteomics, metabolomics, and lipidomics data in a multi-omics fashion.
 The HTML folder can be compressed as a zip file and distributed to others like a pdf or Excel file.
-This interactive viewer can also be displayed in as a report created from Quarto (https://quarto.org/), an open-source scientific and technical publishing system.
-The report can be viewed at <https://dcvtestkit-quarto-example.netlify.app/>
-
-R script and result outputs can be found in the Supplementary Material or by accessing this GitHub page <https://github.com/JauntyJJS/DCVtestkit_Output>
+This interactive viewer can also be displayed in as a report created from Quarto (<https://quarto.org/>), an open-source scientific and technical publishing system.
+The report can be viewed at <https://dcvtestkit-quarto-example.netlify.app/>.
+R script and result outputs can be found in the Supplementary Material or by accessing this GitHub page <https://github.com/JauntyJJS/DCVtestkit_Output>.
 
@@
 
-A linear response in quality control dilution curves is one of the many checks used in metabolomics and lipidomics to assess the suitability of the molecules measured for further analysis.
-Despite its importance in providing high quality data, the shortage of software tools to analyse many dilution curves effectively and efficiently prevents researchers from doing it.
-An R package called `DCVtestkit` is created to rectify this issue by allowing many dilution curves to be analysed quickly and reliably.
-This is done by the use of alternative statistics, other than the Pearson Correlation Coefficient, to better understand the linearity of the dilution curves as well as reporting of statistical results and dilution plots that can be distributed to others.
+A linear response in quality control dilution curves is one of the requirements in metabolomics and lipidomics to assess the suitability of the molecules measured for further analysis.
+Despite its importance in testing data quality, the shortage of software tools to analyse dilution curves effectively and efficiently prevents researchers from fully analysing data.
+An R package called *DCVtestkit* is created to rectify this issue by allowing many dilution curves to be analysed quickly and reliably.
+This is done by the use of alternative statistics, other than the Pearson Correlation Coefficient, to better understand the linearity of the dilution curves, as well as reporting of statistical results and dilution plots that can be distributed to others.
 It is also able to provide an interactive trellis plot for exploratory data analysis.
 The R package is available on GitHub <https://github.com/SLINGhub/DCVtestkit> while the documentation and tutorials can be accessed from <https://slinghub.github.io/DCVtestkit/>.
-As `DCVtestkit` is an opensource software, it is accessible to collaboration works which can help improve its usability and performance in the future.
+As *DCVtestkit* is an opensource software, it is accessible to collaboration works which can help improve its usability and performance in the future.
 

### 2022-10-14 Manuscript/manuscript.qmd
Add results of simulation in a table.

@@
 ---
+
+```{r R packages}
+#| echo: false
+#| message: false
+
+library(dplyr)
+library(stringr)
+library(here)
+library(tibble)
+library(ggplot2)
+library(gridExtra)
+library(patchwork)
+library(labelled)
+library(gtsummary)
+library(flextable)
+library(DCVtestkit)
+```
 
@@
 
-*DCVtestkit* uses the function `evaluate_linearity` to group the dilution curves. At this moment, two workflows are proposed.
+*DCVtestkit* uses the function `evaluate_linearity` to group the dilution curves.
+At this moment, two workflows are proposed.
+Workflow $1$ uses both the Pearson Correlation Coefficient and Percent Residual Accuracy to determine if the dilution curve is linear (labelled as Good Linearity) or not (labelled as Poor Linearity).
+Workflow $2$ goes one step further by using the Mandel’s Fitting Test and the concavity of the fitted quadratic model to check if the non-linear dilution curve plateaus at low concentrations (labelling them as limit of detection) or high concentrations (labelling them as saturation).
+Non-linear dilution curves that do not follow these trends are then labelled as Poor Linearity.
 
@@
 :::
+
+```{r Load Simulated Data Results}
+#| echo: false
+saturation_dilution_summary <-
+  readRDS(file = here::here(
+    "Quarto_Simulation",
+    "saturation_dilution_summary.rds")
+)
+
+lod_dilution_summary <-
+  readRDS(file = here::here(
+    "Quarto_Simulation",
+    "lod_dilution_summary.rds")
+)
+
+linear_dilution_summary <-
+  readRDS(file = here::here(
+    "Quarto_Simulation",
+    "linear_dilution_summary.rds")
+)
+```
+
+```{r Combine Simulated Data Results}
+#| echo: false
+saturation_dilution_summary <- saturation_dilution_summary |> 
+  dplyr::mutate(curve_group = "Saturated")
+
+lod_dilution_summary <- lod_dilution_summary |> 
+  dplyr::mutate(curve_group = "Limit of Detection")
+
+linear_dilution_summary <- linear_dilution_summary |> 
+  dplyr::mutate(curve_group = "Linear")
+
+combined_dilution_summary <-
+  dplyr::bind_rows(
+    saturation_dilution_summary,
+    lod_dilution_summary,
+    linear_dilution_summary
+  ) 
+```
+
+```{r Data Wrangling for Simulation Results}
+#| echo: false
+combined_dilution_summary <- 
+  combined_dilution_summary |> 
+  dplyr::mutate(
+    curve_group = factor(.data$curve_group,
+                         levels = c("Linear",
+                                    "Saturated",
+                                    "Limit of Detection")),
+    wf2_group = stringr::str_replace(
+      string = .data$wf2_group,
+      pattern = "LOD",
+      replacement = "Limit of Detection"
+    ),
+    wf2_group = factor(.data$wf2_group,
+                         levels = c("Good Linearity",
+                                    "Saturation",
+                                    "Limit of Detection",
+                                    "Poor Linearity"))
+  ) |> 
+  labelled::set_variable_labels(
+    ID = "Unique Curve Identifier",
+    curve_group = "Simulated Curve Group",
+    wf1_group = "Workflow 1 Result",
+    wf2_group = "Workflow 2 Result",
+    r_corr = "Pearson Correlation Coefficient",
+    pra_linear = "Percent Residual Accuracy",
+    mandel_p_val = "Mandel's Test p Value",
+    concavity = "Concavity Of Fitted Quadratic Model",
+    r2_linear = "Coefficient Of Determination",
+    r2_adj_linear = "Adjusted Coefficient Of Determination",
+    mandel_stats = "Test statistics from Mandel's Test"
+  )
+
+```
+
+The workflow was tested on `r nrow(linear_dilution_summary)` simulated linear curves, `r nrow(lod_dilution_summary)` curves that plateau at low concentrations (labelled as LOD curves) and `r nrow(saturation_dilution_summary)` curves that plateau at high concentrations (labelled as Saturated curves)
+
+```{r}
+#| echo: false
+#| label: tbl-simulation-result
+#| tbl-cap-location: bottom
+#| tbl-cap: "Simulation Results"
+combined_dilution_summary |> 
+  dplyr::select(c("curve_group", "wf2_group", 
+                  "r_corr", "pra_linear")) |> 
+  gtsummary::tbl_summary(
+    by = "curve_group",
+    statistic = list(
+      wf2_group ~ "{n}/{N} ({p}%)"
+    ) 
+  ) |> 
+  modify_header(all_stat_cols() ~ "**{level}**\nN = {n}") |> 
+  gtsummary::modify_spanning_header(all_stat_cols() ~ "**Simulated Curve Types**") |>  
+  gtsummary::as_flex_table() |> 
+  flextable::set_table_properties(width = 1, layout = "autofit")
+
+```
 

### 2022-10-14 Quarto_Simulation/index.qmd
Add results of simulation in a table.

@@
 library(epifitter)
+library(reactable)
 library(deSolve)
@@
 
+```{r Save Simulated Data Saturated}
+saveRDS(saturation_simulated_database, 
+        file = "saturated_simulated_database.rds")
+```
+
 ## Limit of Detection Curve
@@
   tidyr::unnest("dilution_data")
+```
+
+```{r Save Simulated Data LOD}
+saveRDS(lod_simulated_database, 
+        file = "lod_simulated_database.rds")
 ```
@@
 
+```{r Save Simulated Data Linear}
+saveRDS(linear_simulated_database, 
+        file = "linear_simulated_database.rds")
+```
+
 :::
@@
 ```{r dilution statistical summary saturated}
-saturation_dilution_summary <- DCVtestkit::summarise_dilution_table(
+#| message: false
+saturation_dilution_summary <- 
+  DCVtestkit::summarise_dilution_table(
     dilution_table = saturation_simulated_database,
@@
     conc_var = "x",
-  signal_var = "y")
+    signal_var = "y") |> 
+  DCVtestkit::evaluate_linearity(
+    grouping_variable = c("ID")
+  )
+```
+
+```{r save dilution statistical summary saturated}
+saveRDS(saturation_dilution_summary, 
+        file = "saturation_dilution_summary.rds")
 ```
@@
 ```{r dilution statistical summary lod}
-lod_dilution_summary <- DCVtestkit::summarise_dilution_table(
+#| message: false
+lod_dilution_summary <- 
+  DCVtestkit::summarise_dilution_table(
     dilution_table = lod_simulated_database,
@@
     conc_var = "x",
-  signal_var = "y")
+    signal_var = "y") |> 
+  DCVtestkit::evaluate_linearity(
+    grouping_variable = c("ID")
+  )
 
+```
+
+```{r save dilution statistical summary lod}
+saveRDS(lod_dilution_summary, 
+        file = "lod_dilution_summary.rds")
 ```
@@
 ```{r dilution statistical summary linear}
-linear_dilution_summary <- DCVtestkit::summarise_dilution_table(
+#| message: false
+linear_dilution_summary <-
+  DCVtestkit::summarise_dilution_table(
     dilution_table = linear_simulated_database,
@@
     conc_var = "x",
-  signal_var = "y")
+    signal_var = "y") |> 
+  DCVtestkit::evaluate_linearity(
+    grouping_variable = c("ID")
+  )
 
+```
+
+```{r save dilution statistical summary linear}
+saveRDS(linear_dilution_summary, 
+        file = "linear_dilution_summary.rds")
 ```

### 2022-10-14 Manuscript/manuscript.qmd
Modify the digits of percentages.

@@
 
-The workflow was tested on `r nrow(linear_dilution_summary)` simulated linear curves, `r nrow(lod_dilution_summary)` curves that plateau at low concentrations (labelled as LOD curves) and `r nrow(saturation_dilution_summary)` curves that plateau at high concentrations (labelled as Saturated curves)
+Workflow $2$ was tested on `r nrow(linear_dilution_summary)` simulated linear curves, `r nrow(lod_dilution_summary)` curves that plateau at low concentrations (labelled as Limit of Detection curves) and `r nrow(saturation_dilution_summary)` curves that plateau at high concentrations (labelled as Saturated curves)
 
@@
       wf2_group ~ "{n}/{N} ({p}%)"
-    ) 
+    ),
+    digits = list(wf2_group ~ c(0, 0, 1),
+                  r_corr ~ c(2),
+                  pra_linear ~ c(0))
   ) |> 
   modify_header(all_stat_cols() ~ "**{level}**\nN = {n}") |> 
-  gtsummary::modify_spanning_header(all_stat_cols() ~ "**Simulated Curve Types**") |>  
+  gtsummary::modify_spanning_header(all_stat_cols() ~ "**Simulated Curve Type**") |>  
   gtsummary::as_flex_table() |> 

### 2022-10-14 Manuscript/manuscript.qmd
Added the simulation results.

--- 2022-10-13 Manuscript/manuscript.qmd
@@
 ---
+
+```{r R packages}
+#| echo: false
+#| message: false
+
+library(dplyr)
+library(stringr)
+library(here)
+library(tibble)
+library(ggplot2)
+library(gridExtra)
+library(patchwork)
+library(labelled)
+library(gtsummary)
+library(flextable)
+library(webshot2)
+library(DCVtestkit)
+```
 
@@
 
-While the threshold values given for Pearson Correlation Coefficient and Percent Residual Accuracy are based on the interpretation given by @y.h.chan2003 and @logue2018, respectively, it remains subjective and arbitrary.
+```{r Load Simulated Data Results}
+#| echo: false
+saturation_dilution_summary <-
+  readRDS(file = here::here(
+    "Quarto_Simulation",
+    "saturation_dilution_summary.rds")
+)
+
+lod_dilution_summary <-
+  readRDS(file = here::here(
+    "Quarto_Simulation",
+    "lod_dilution_summary.rds")
+)
+
+linear_dilution_summary <-
+  readRDS(file = here::here(
+    "Quarto_Simulation",
+    "linear_dilution_summary.rds")
+)
+```
+
+```{r Combine Simulated Data Results}
+#| echo: false
+saturation_dilution_summary <- saturation_dilution_summary |> 
+  dplyr::mutate(curve_group = "Saturated")
+
+lod_dilution_summary <- lod_dilution_summary |> 
+  dplyr::mutate(curve_group = "Limit of Detection")
+
+linear_dilution_summary <- linear_dilution_summary |> 
+  dplyr::mutate(curve_group = "Linear")
+
+combined_dilution_summary <-
+  dplyr::bind_rows(
+    saturation_dilution_summary,
+    lod_dilution_summary,
+    linear_dilution_summary
+  ) 
+```
+
+```{r Data Wrangling for Simulation Results}
+#| echo: false
+combined_dilution_summary <- 
+  combined_dilution_summary |> 
+  dplyr::mutate(
+    curve_group = factor(.data$curve_group,
+                         levels = c("Linear",
+                                    "Saturated",
+                                    "Limit of Detection")),
+    pearson_group = dplyr::case_when(
+      .data$r_corr >= 0.8 ~ "more than or\nequal to 0.8",
+      .data$r_corr < 0.8 ~ "less than 0.8",
+    ),
+    wf2_group = stringr::str_replace(
+      string = .data$wf2_group,
+      pattern = "LOD",
+      replacement = "Limit of Detection"
+    ),
+    wf2_group = factor(.data$wf2_group,
+                         levels = c("Good Linearity",
+                                    "Saturation",
+                                    "Limit of Detection",
+                                    "Poor Linearity"))
+  ) |> 
+  labelled::set_variable_labels(
+    ID = "Unique Curve Identifier",
+    curve_group = "Simulated Curve Group",
+    wf1_group = "Workflow 1 Grouping",
+    wf2_group = "Workflow 2 Grouping",
+    pearson_group = "Pearson Correlation\nCoefficient Grouping",
+    r_corr = "Pearson Correlation\nCoefficient",
+    pra_linear = "Percent Residual\nAccuracy",
+    mandel_p_val = "Mandel's Test p Value",
+    concavity = "Concavity Of Fitted Quadratic Model",
+    r2_linear = "Coefficient Of Determination",
+    r2_adj_linear = "Adjusted Coefficient Of Determination",
+    mandel_stats = "Test statistics from Mandel's Test"
+  )
+
+```
+
+Workflow $2$ was tested on `r nrow(linear_dilution_summary)` simulated linear curves (labelled as Linear), `r nrow(lod_dilution_summary)` curves that plateau at low concentrations (labelled as Limit of Detection) and `r nrow(saturation_dilution_summary)` curves that plateau at high concentrations (labelled as Saturated).
+A benchmark workflow using only Pearson Correlation Coefficient with a cut off value of $0.8$ is used to compare with Workflow $2$.
+
+```{r}
+#| echo: false
+#| output: false
+simulation_results <- combined_dilution_summary |> 
+  dplyr::select(c("curve_group", "wf2_group", 
+                  "pearson_group"
+                  # "r_corr", "pra_linear"
+                  )
+                ) |> 
+  dplyr::relocate(c("pearson_group")) |> 
+  gtsummary::tbl_summary(
+    by = "curve_group",
+    statistic = list(
+      pearson_group ~ "{n}/{N} ({p}%)",
+      wf2_group ~ "{n}/{N} ({p}%)"
+    ),
+    digits = list(
+      wf2_group ~ c(0, 0, 1),
+      pearson_group ~ c(0, 0, 1)
+      #r_corr ~ c(2),
+      #pra_linear ~ c(0)
+      )
+  ) |> 
+  modify_header(
+    all_stat_cols() ~ "**{level}**\nN = {n}"
+    ) |> 
+  gtsummary::modify_spanning_header(
+    all_stat_cols() ~ "**Simulated Curve Type**"
+    )
+
+simulation_results |> 
+  gtsummary::as_flex_table() |> 
+  flextable::set_table_properties(width = 1, layout = "autofit") |>
+  flextable::save_as_image(
+    path = here::here("Manuscript",
+                      "images",
+                      "simulation_results.png"), 
+    webshot = "webshot2")
+```
+
+::: {#fig-Simulation-Result layout-ncol=1}
+
+![](images/simulation_results.png)
+
+Simulation Results
+:::
+
+@fig-Simulation-Result showed that Workflow $2$ is able to identify the saturated and limit of detection curves better than the benchmark workflow.
+On the other hand, while Workflow $2$ is able to identify less linear curves than the benchmark workflow, the results are comparable score of `r inline_text(simulation_results, variable = wf2_group, level = "Good Linearity", column = "Linear")`
+
+While the proposed workflows' threshold values of Pearson Correlation Coefficient and Percent Residual Accuracy are based on the interpretation given by @y.h.chan2003 and @logue2018, respectively, these cut off values remain subjective and arbitrary.
 Moreover, it is also possible for the dilution curve to exhibit a sigmoidal relationship, or non-linear, at both low and high concentrations, which the proposed workflow would be unable to identify.

### 2022-10-15 Quarto_Simulation/index.qmd
Fixed some file naming issues.
Make the html document nicer.

@@
 author: "Jeremy Selva"
-format: html
+format:
+  html:
+    theme: 
+      light: cerulean 
+      dark: cyborg
+    toc: true
+    toc-depth: 3
+    toc-location: left
+    number-sections: false
+    code-fold: show
+    code-overflow: scroll
+    code-copy: true
+    code-tools: true
+    code-link: true
+    self-contained: false
+    smooth-scroll: true
+execute: 
+  cache: true
 ---
@@
 saveRDS(saturation_simulated_database, 
-        file = "saturated_simulated_database.rds")
+        file = "saturation_simulated_database.rds")
 ```

### 2022-10-15 Quarto_Simulation/index.qmd
Add pdf

@@
 
+We simulate $200$ curves (saturated, limit of detection and linear) using $7$ points from $0$ to $200$ on the x-axis. A unique id is added for each simulated data.
+
 ::: {.panel-tabset}
@@
 
-saturation_simulated_database <-
+nested_saturation_simulated_database <-
   tibble::tibble(
@@
       )
-    ) |> 
-  tidyr::unnest("dilution_data")
-```
-
-```{r Save Simulated Data Saturated}
-saveRDS(saturation_simulated_database, 
-        file = "saturation_simulated_database.rds")
+  )
 ```
@@
 
-lod_simulated_database <-
+nested_lod_simulated_database <-
   tibble::tibble(
@@
       )
-    ) |> 
-  tidyr::unnest("dilution_data")
-```
-
-```{r Save Simulated Data LOD}
-saveRDS(lod_simulated_database, 
-        file = "lod_simulated_database.rds")
+  )
 ```
@@
 
-linear_simulated_database <-
+nested_linear_simulated_database <-
   tibble::tibble(
@@
       )
-    ) |> 
+  )
+```
+
+:::
+
+# Unnest Simulated Data
+
+While nested dilution (having a column of data frames) is easier to view with a human eye, it can be hard to be read and processed by a computer.
+We need flattened the data frames back into columns.
+To do this, we use [`tidyr::unnest`](https://tidyr.tidyverse.org/reference/nest.html)
+
+## Saturated Curve
+
+```{r Nest Simulated Data Saturated}
+saturation_simulated_database <-
+  nested_saturation_simulated_database |> 
   tidyr::unnest("dilution_data")
 ```
+
+## Limit of Detection Curve
+
+```{r Nest Simulated Data LOD}
+lod_simulated_database <-
+  nested_lod_simulated_database |> 
+  tidyr::unnest("dilution_data")
+```
+
+## Linear Curve
+
+```{r Nest Simulated Data Linear}
+linear_simulated_database <-
+  nested_linear_simulated_database |> 
+  tidyr::unnest("dilution_data")
+```
+
+# Save Simulated Data
+
+We can now save the data as a csv and rds files.
+
+## Saturated Curve
+
+```{r Save Simulated Data Saturated}
+saveRDS(saturation_simulated_database, 
+        file = "saturation_simulated_database.rds")
+
+write.csv(x = saturation_simulated_database,
+          file = "saturation_simulated_database.csv", 
+          row.names = FALSE)
+```
+
+## Limit of Detection Curve
+
+```{r Save Simulated Data LOD}
+saveRDS(lod_simulated_database, 
+        file = "lod_simulated_database.rds")
+
+write.csv(x = saturation_simulated_database,
+          file = "lod_simulated_database.csv", 
+          row.names = FALSE)
+```
+
+## Linear Curve
 
@@
         file = "linear_simulated_database.rds")
+
+write.csv(x = linear_simulated_database,
+          file = "linear_simulated_database.csv", 
+          row.names = FALSE)
 ```
 
-:::
+# Calculate Statistical Summary
 
-# Create Statistical Summary
+We now calculate the statistical summary for each dilution curve. In addition, we export statistical summary as a csv and rds files.
 
@@
         file = "saturation_dilution_summary.rds")
+
+write.csv(x = saturation_dilution_summary,
+          file = "saturation_dilution_summary.csv", 
+          row.names = FALSE)
 ```
@@
         file = "lod_dilution_summary.rds")
+
+write.csv(x = lod_dilution_summary,
+          file = "lod_dilution_summary.csv", 
+          row.names = FALSE)
 ```
@@
         file = "linear_dilution_summary.rds")
+
+write.csv(x = linear_dilution_summary,
+          file = "linear_dilution_summary.csv", 
+          row.names = FALSE)
 ```
@@
 
-# Report plots as pdf files
+# View Simulation Curve Data and Statistical Summary
+
+We use [`reactable::reactable`](https://glin.github.io/reactable/reference/reactable.html) to print the simulated data and statistical summary.
+
+## Saturated Curve
+
+```{r Print Simulated Data Saturated}
+#| layout-ncol: 1
+
+nested_saturation_simulated_database |> 
+  reactable::reactable(
+    defaultColDef = reactable::colDef(minWidth = 200),
+    defaultPageSize = 5,
+    columns = list(
+      ID = reactable::colDef(
+        # Freeze first column
+        sticky = "left",
+        style = list(borderRight = "1px solid #eee"),
+        headerStyle = list(borderRight = "1px solid #eee"),
+        minWidth = 200),
+      dilution_data = reactable::colDef(
+        details = function(index) {
+          filtered_data <- nested_saturation_simulated_database[["dilution_data"]][index][[1]]
+          htmltools::div(style = "padding: 1rem",
+                         reactable::reactable(
+                           data = filtered_data,
+                           defaultPageSize = 10,
+                           defaultColDef = reactable::colDef(minWidth = 200),
+                           columns = list(Sample_Name = reactable::colDef(minWidth = 200)),
+                           outlined = TRUE,
+                           highlight = TRUE)
+                       )
+      }
+    )
+  )
+)
+
+saturation_dilution_summary |> 
+  reactable::reactable(
+    defaultColDef = reactable::colDef(minWidth = 200),
+    defaultPageSize = 5,
+    columns = list(
+      ID = reactable::colDef(
+      # Freeze first column
+      sticky = "left",
+      style = list(borderRight = "1px solid #eee"),
+      headerStyle = list(borderRight = "1px solid #eee"),
+      minWidth = 200)
+    )
+)
+```
+
+## Limit of Detection Curve
+
+```{r Print Simulated Data LOD}
+#| layout-ncol: 1
+
+nested_lod_simulated_database |> 
+  reactable::reactable(
+    defaultColDef = reactable::colDef(minWidth = 200),
+    defaultPageSize = 5,
+    columns = list(
+      ID = reactable::colDef(
+        # Freeze first column
+        sticky = "left",
+        style = list(borderRight = "1px solid #eee"),
+        headerStyle = list(borderRight = "1px solid #eee"),
+        minWidth = 200),
+      dilution_data = reactable::colDef(
+        details = function(index) {
+          filtered_data <- nested_lod_simulated_database[["dilution_data"]][index][[1]]
+          htmltools::div(style = "padding: 1rem",
+                         reactable::reactable(
+                           data = filtered_data,
+                           defaultPageSize = 10,
+                           defaultColDef = reactable::colDef(minWidth = 200),
+                           columns = list(Sample_Name = reactable::colDef(minWidth = 200)),
+                           outlined = TRUE,
+                           highlight = TRUE)
+                       )
+      }
+    )
+  )
+
+)
+
+lod_dilution_summary |> 
+  reactable::reactable(
+    defaultColDef = reactable::colDef(minWidth = 200),
+    defaultPageSize = 5,
+    columns = list(
+      ID = reactable::colDef(
+      # Freeze first column
+      sticky = "left",
+      style = list(borderRight = "1px solid #eee"),
+      headerStyle = list(borderRight = "1px solid #eee"),
+      minWidth = 200)
+    )
+)
+```
+
+## Linear Curve
+
+```{r Print Simulated Data Linear}
+#| layout-ncol: 1
+
+nested_linear_simulated_database |>
+  reactable::reactable(
+    defaultColDef = reactable::colDef(minWidth = 200),
+    defaultPageSize = 5,
+    columns = list(
+      ID = reactable::colDef(
+        # Freeze first column
+        sticky = "left",
+        style = list(borderRight = "1px solid #eee"),
+        headerStyle = list(borderRight = "1px solid #eee"),
+        minWidth = 200),  
+      dilution_data = reactable::colDef(
+        details = function(index) {
+          filtered_data <- nested_linear_simulated_database[["dilution_data"]][index][[1]]
+          htmltools::div(style = "padding: 1rem",
+                         reactable::reactable(
+                           data = filtered_data,
+                           defaultPageSize = 10,
+                           defaultColDef = reactable::colDef(minWidth = 200),
+                           columns = list(Sample_Name = reactable::colDef(minWidth = 200)),
+                           outlined = TRUE,
+                           highlight = TRUE)
+                       )
+      }
+    )
+  )
+
+)
+
+linear_dilution_summary |> 
+  reactable::reactable(
+    defaultColDef = reactable::colDef(minWidth = 200),
+    defaultPageSize = 5,
+    columns = list(
+      ID = reactable::colDef(
+      # Freeze first column
+      sticky = "left",
+      style = list(borderRight = "1px solid #eee"),
+      headerStyle = list(borderRight = "1px solid #eee"),
+      minWidth = 200)
+    )
+)
+```
+
+# Report Plots As pdf Files
 

### 2022-10-15 Quarto_Simulation/index.qmd
Managed to fix the blocked trellis plot issue

@@
 execute: 
-  cache: true
+  cache: false
 ---
@@
 ```{r plots as trellis saturated}
+#| column: screen-inset-right
+
 saturation_trellis_table <- DCVtestkit::add_plotly_panel(
@@
 ```{r plots as trellis lod}
+#| column: screen-inset-right
+
 lod_trellis_table <- DCVtestkit::add_plotly_panel(
@@
 ```{r plots as trellis linear}
+#| column: screen-inset-right
+
 linear_trellis_table <- DCVtestkit::add_plotly_panel(

### 2022-10-15 Manuscript/manuscript.qmd
Add dilution classification table in the Simulation document.

@@
 
-Workflow $2$ was tested on `r nrow(linear_dilution_summary)` simulated linear curves (labelled as Linear), `r nrow(lod_dilution_summary)` curves that plateau at low concentrations (labelled as Limit of Detection) and `r nrow(saturation_dilution_summary)` curves that plateau at high concentrations (labelled as Saturated).
-A benchmark workflow using only Pearson Correlation Coefficient with a cut off value of $0.8$ is used to compare with Workflow $2$.
+Workflow $2$ was tested on simulated data sets of `r nrow(linear_dilution_summary)` linear curves (labelled as Linear), `r nrow(lod_dilution_summary)` curves that plateau at low concentrations (labelled as Limit of Detection) and `r nrow(saturation_dilution_summary)` curves that plateau at high concentrations (labelled as Saturated).
+A benchmark workflow using only Pearson Correlation Coefficient with a cut off value of $0.8$, a threshold used in @croixmarie2009, is created to compare with Workflow $2$.
 
@@
 @fig-Simulation-Result showed that Workflow $2$ is able to identify the saturated and limit of detection curves better than the benchmark workflow.
-On the other hand, while Workflow $2$ is able to identify less linear curves than the benchmark workflow, the results are comparable score of `r inline_text(simulation_results, variable = wf2_group, level = "Good Linearity", column = "Linear")`
+On the other hand, while Workflow $2$ is able to identify less linear curves than the benchmark workflow, it gives a comparable score of `r inline_text(simulation_results, variable = wf2_group, level = "Good Linearity", column = "Linear")`
 

### 2022-10-15 Quarto_Simulation/index.qmd
Add dilution classification table in the Simulation document.

@@
 
-# R Libaries used
+# R Packages used
+
 ```{r R packages}
@@
 library(DCVtestkit)
+library(labelled)
+library(gtsummary)
+library(sessioninfo)
+library(report)
 
 set.seed(123)
+```
+
+```{r See packages info}
+#| code-fold: true
+r_package_table <- sessioninfo::package_info()
+rownames(r_package_table) <- NULL
+
+r_package_table |>
+  dplyr::mutate(
+    version = ifelse(is.na(r_package_table$loadedversion), 
+                     r_package_table$ondiskversion, 
+                     r_package_table$loadedversion)
+  ) |> 
+  dplyr::filter(.data$attached == TRUE) |> 
+  dplyr::select(c("package", "version", 
+                  "date", "source"
+    )
+  ) |> 
+  reactable::reactable(
+    columns = list(
+      package = reactable::colDef(
+        # Freeze first column
+        sticky = "left",
+        style = list(borderRight = "1px solid #eee"),
+        headerStyle = list(borderRight = "1px solid #eee"))
+  )
+  )
+```
+
+# R Platform Information
+
+```{r See session info}
+#| code-fold: true
+r_platform_table <- sessioninfo::platform_info()
+
+r_platform_table <- data.frame(
+    setting = names(r_platform_table),
+    value = unlist(r_platform_table,
+                   use.names = FALSE),
+    stringsAsFactors = FALSE
+  )
+
+r_platform_table |>
+  reactable::reactable(
+    defaultPageSize = 5
+  )
 ```
@@
 
+# Report Workflow $2$ Results
+
+We combined the three summary results together
+
+```{r Combine Simulated Data Results}
+
+saturation_dilution_summary <- saturation_dilution_summary |> 
+  dplyr::mutate(curve_group = "Saturated")
+
+lod_dilution_summary <- lod_dilution_summary |> 
+  dplyr::mutate(curve_group = "Limit of Detection")
+
+linear_dilution_summary <- linear_dilution_summary |> 
+  dplyr::mutate(curve_group = "Linear")
+
+combined_dilution_summary <-
+  dplyr::bind_rows(
+    saturation_dilution_summary,
+    lod_dilution_summary,
+    linear_dilution_summary
+  ) 
+```
+
+Perform some data wrangling to summarise the results later. A benchmark workflow using only Pearson Correlation Coefficient with a cut off value of $0.8$ is used to compare with Workflow $2$.
+
+```{r Data Wrangling for Simulation Results}
+
+combined_dilution_summary <- 
+  combined_dilution_summary |> 
+  dplyr::mutate(
+    curve_group = factor(.data$curve_group,
+                         levels = c("Linear",
+                                    "Saturated",
+                                    "Limit of Detection")),
+    pearson_group = dplyr::case_when(
+      .data$r_corr >= 0.8 ~ "more than or\nequal to 0.8",
+      .data$r_corr < 0.8 ~ "less than 0.8",
+    ),
+    wf2_group = stringr::str_replace(
+      string = .data$wf2_group,
+      pattern = "LOD",
+      replacement = "Limit of Detection"
+    ),
+    wf2_group = factor(.data$wf2_group,
+                         levels = c("Good Linearity",
+                                    "Saturation",
+                                    "Limit of Detection",
+                                    "Poor Linearity"))
+  ) |> 
+  labelled::set_variable_labels(
+    ID = "Unique Curve Identifier",
+    curve_group = "Simulated Curve Group",
+    wf1_group = "Workflow 1 Grouping",
+    wf2_group = "Workflow 2 Grouping",
+    pearson_group = "Pearson Correlation\nCoefficient Grouping",
+    r_corr = "Pearson Correlation\nCoefficient",
+    pra_linear = "Percent Residual\nAccuracy",
+    mandel_p_val = "Mandel's Test p Value",
+    concavity = "Concavity Of Fitted Quadratic Model",
+    r2_linear = "Coefficient Of Determination",
+    r2_adj_linear = "Adjusted Coefficient Of Determination",
+    mandel_stats = "Test statistics from Mandel's Test"
+  )
+
+```
+
+```{r Worflow 2 vs Benchmark results}
+#| column: screen-inset-right
+simulation_results <- combined_dilution_summary |> 
+  dplyr::select(c("curve_group", "wf2_group", 
+                  "pearson_group"
+                  # "r_corr", "pra_linear"
+                  )
+                ) |> 
+  dplyr::relocate(c("pearson_group")) |> 
+  gtsummary::tbl_summary(
+    by = "curve_group",
+    statistic = list(
+      pearson_group ~ "{n}/{N} ({p}%)",
+      wf2_group ~ "{n}/{N} ({p}%)"
+    ),
+    digits = list(
+      wf2_group ~ c(0, 0, 1),
+      pearson_group ~ c(0, 0, 1)
+      #r_corr ~ c(2),
+      #pra_linear ~ c(0)
+      )
+  ) |> 
+  modify_header(
+    all_stat_cols() ~ "**{level}**\nN = {n}"
+    ) |> 
+  gtsummary::modify_spanning_header(
+    all_stat_cols() ~ "**Simulated Curve Type**"
+    )
+
+simulation_results
+```
+
+Results showed that Workflow $2$ is able to identify the saturated and limit of detection curves better than the benchmark workflow.
+On the other hand, while Workflow $2$ is able to identify less linear curves than the benchmark workflow, it gives a comparable score of `r inline_text(simulation_results, variable = wf2_group, level = "Good Linearity", column = "Linear")`
+
 # Report Plots As pdf Files
@@
 ```
+
+# R Package Reference
+
+```{r package references}
+#| code-fold: true
+#| output: asis
+
+report::cite_packages() |> 
+  suppressWarnings()
+```

### 2022-10-15 Manuscript/manuscript.qmd
Update the manuscript.

@@
 ---
-title: "*DCVtestkit*: an R package for analysis of quality control dilution curves"
+title: "*DCVtestkit*: an R package for linearity assessment and analysis of quality control dilution curves"
 bibliography: bibliography.bib
@@
 
+Linearity assessment plays a significant role in the validation of quantitative analytical laboratory procedures.
 In metabolomic and lipidomic workflows, a linear response in dilution series generated from pooled quality control (QC) samples is used to assess the quality of the measurement of molecules measured before further analysis.
@@
 DCVtestkit aims to provide additional summary statistics for dilution curves, taken from previous publications but which are not implemented in the current software tools.
-It also helps to reduce the analyst’s workload by analysing many dilution curves automatically, reporting the statistical results in Excel and recording the dilution plots in a pdf file.
+It also helps to reduce the analyst's workload by analysing many dilution curves automatically, reporting the statistical results in Excel and recording the dilution plots in a pdf file.
 In addition, it can also create an interactive trellis displayed as a HTML folder for more exploratory analyses.
@@
 
-Dilution curves have been used in many areas of biomedical and pharmaceutical sciences.
+Linearity assessment is one of the criteria used to evaluate the accuracy and precision of a quantitative measurement procedure in science and engineering.
+Several applications of linearity assessment can be found in @rodríguez1993 for calibration studies, @needleman1990 for drug analysis and @sicilianidecumis2014 for environmental monitoring sensors.
+
 In the field of metabolomics and lipidomics, dilution curves for each molecule measured, usually in a quality control sample generated by pooling equal aliquots from each study sample, are plotted as proposed by @croixmarie2009 to check if the sample matrix is the same among all samples.
@@
 As such, many laboratories use commercial software to plot these dilution curves and report their corresponding Pearson Correlation Coefficient value.
-These include either mass spectrometry vendors’ software or, more in general, programs such as Excel and GraphPad Prism.
+These include either mass spectrometry vendors' software or, more in general, programs such as Excel and GraphPad Prism.
 Nevertheless, these tools have limitations.
@@
 While the Pearson Correlation Coefficient $R$ and/or Coefficient Of Determination $R^2$ are popular indicators of how well the dilution points fits a linear line, @sonnergaard2006 estimated that these are not effective standalone numeric parameter to estimate linearity.
-Using a modified version of Anscombe’s quartet, the paper showed that a high coefficient of determination does not reflect well a curve relationship.
+Using a modified version of Anscombe's quartet, the paper showed that a high coefficient of determination does not reflect well a curve relationship.
 Both @croixmarie2009 and @sands2021 support this view, by indicating that an obvious non-linear response at the high and/or low ends of the quality control sample-based dilution curve can still yield a high correlation coefficient.
@@
 
-In addition, with the advancement of the technology used for molecular identification coupled with a high emphasis on high throughput analysis and automation, today’s targeted metabolomics/lipidomics can include more than eight hundred analytes measured by a single method.
+In addition, with the advancement of the technology used for molecular identification coupled with a high emphasis on high throughput analysis and automation, today's targeted metabolomics/lipidomics can include more than eight hundred analytes measured by a single method.
 This number can also increase further in an untargeted approach.
@@
 
-::: {#fig-DCVtestkit-Workflow layout-ncol=1}
-
+::: {#fig-DCVtestkit-Workflow layout-ncol="1"}
 ![](images/README-Workflow.png)
@@
 To improve the description of the goodness-of-fit for linear dilution curves, a few additional parameters, on top of the popular Pearson Correlation Coefficient $R$, are added in the R package *DCVtestkit*.
-The first additional parameters are statistical results from Mandel’s Fitting Test (as reported in @andrade2013) in which a low $p$ value gives sufficient evidence that a quadratic model is a better fit than a linear model, indicating the curve may not be linear.
+The first additional parameters are statistical results from Mandel's Fitting Test (as reported in @andrade2013) in which a low $p$ value gives sufficient evidence that a quadratic model is a better fit than a linear model, indicating the curve may not be linear.
 Another parameter calculated is the Percent Residual Accuracy (as reported in @logue2018) which ranges from $-\infty$ to $100$.
@@
 
-Returning to @fig-curves, both the saturated and LOD curves give a much lower Mandel’s Fitting Test $p$ values, denoted as `mandel_p_val`, ($1.66 * 10^{-4}$ and $2.56 * 10^{-3}$ respectively vs $0.38$).
+Returning to @fig-curves, both the saturated and LOD curves give a much lower Mandel's Fitting Test $p$ values, denoted as `mandel_p_val`, ($1.66 * 10^{-4}$ and $2.56 * 10^{-3}$ respectively vs $0.38$).
 Correspondingly, ranging from $-\infty$ to $100$, the Percent Residual Accuracy values, denoted as `pra_linear`, are much lower in the saturated and LOD curves compared to the linear curve ($62.30$ and $74.69$ respectively vs $94.32$).
@@
 Workflow $1$ uses both the Pearson Correlation Coefficient and Percent Residual Accuracy to determine if the dilution curve is linear (labelled as Good Linearity) or not (labelled as Poor Linearity).
-Workflow $2$ goes one step further by using the Mandel’s Fitting Test and the concavity of the fitted quadratic model to check if the non-linear dilution curve plateaus at low concentrations (labelling them as limit of detection) or high concentrations (labelling them as saturation).
+Workflow $2$ goes one step further by using the Mandel's Fitting Test and the concavity of the fitted quadratic model to check if the non-linear dilution curve plateaus at low concentrations (labelling them as limit of detection) or high concentrations (labelling them as saturation).
 Non-linear dilution curves that do not follow these trends are then labelled as Poor Linearity.
 
-::: {#fig-Dilution-Grouping-Workflow layout-ncol=1}
-
+::: {#fig-Dilution-Grouping-Workflow layout-ncol="1"}
 ![](images/README-LinearEvaluation.png)
@@
 
-::: {#fig-Simulation-Result layout-ncol=1}
-
+::: {#fig-Simulation-Result layout-ncol="1"}
 ![](images/simulation_results.png)
@@
 @fig-Simulation-Result showed that Workflow $2$ is able to identify the saturated and limit of detection curves better than the benchmark workflow.
-On the other hand, while Workflow $2$ is able to identify less linear curves than the benchmark workflow, it gives a comparable score of `r inline_text(simulation_results, variable = wf2_group, level = "Good Linearity", column = "Linear")`
+On the other hand, while Workflow $2$ is able to identify less linear curves than the benchmark workflow, it gives a comparable score of `r inline_text(simulation_results, variable = wf2_group, level = "Good Linearity", column = "Linear")`.
+More details on how the simulated data is created and can be found in this report <https://dcvtestkit-simulation.netlify.app>.
+Relevant R script to generate this report can be found in the Supplementary Material or by accessing this GitHub page <https://github.com/JauntyJJS/DCVtestkit_Output>
 
@@
 
-Nevertheless, while the proposed workflow is not a perfect solution, *DCVtestkit* allows the analyst to change and optimise the threshold values, to adjust the determinants of linearity and saturation of dilution curves according to the user’s needs.
+Nevertheless, while the proposed workflow is not a perfect solution, *DCVtestkit* allows the analyst to change and optimise the threshold values, to adjust the determinants of linearity and saturation of dilution curves according to the user's needs.
 More information on how to perform such customisation can be found in the program documentation titled: ["Customise Linearity Evaluation Workflow"](https://slinghub.github.io/DCVtestkit/articles/lineval-customization.html).
@@
 
-::: {#fig-Viewing-Interactive-Curves layout-ncol=1}
-
+::: {#fig-Viewing-Interactive-Curves layout-ncol="1"}
 ![](images/README-TrellisOutput.png)
@@
 This interactive viewer can also be displayed as a report created from Quarto (https://quarto.org/), an open-source scientific and technical publishing system.
-The report can be viewed at <https://dcvtestkit-quarto-example.netlify.app/>
+The report can be viewed at <https://dcvtestkit-quarto-example.netlify.app/>.
 R script and result outputs can be found in the Supplementary Material or by accessing this GitHub page <https://github.com/JauntyJJS/DCVtestkit_Output>
@@
 
+To verify if a quantitative analytical test method is reliable, it is important to check for linearity.
 A linear response in quality control dilution curves is one of the requirements in metabolomics and lipidomics to assess the suitability of the molecules measured for further analysis.

### 2022-10-15 Quarto_Simulation/index.qmd

@@
 execute: 
-  cache: false
+  cache: true
 ---

### 2022-11-01 Manuscript/manuscript.qmd
Shorten article to < 1000 words and one picture. Added one file for supplementary figures.

--- 2022-10-14 Manuscript/manuscript.qmd
@@
 ---
-title: "*DCVtestkit*: an R package for analysis of quality control dilution curves"
+title: "*DCVtestkit*: a R package for linearity assessment and analysis of quality control dilution curves"
 bibliography: bibliography.bib
@@
 library(here)
-library(tibble)
-library(ggplot2)
-library(gridExtra)
-library(patchwork)
 library(labelled)
@@
 library(webshot2)
-library(DCVtestkit)
+
 ```
@@
 
-In metabolomic and lipidomic workflows, a linear response in dilution series generated from pooled quality control (QC) samples is used to assess the quality of the measurement of molecules measured before further analysis.
+Linearity assessment plays a significant role in the validation of quantitative analytical laboratory procedures.
+In metabolomic and lipidomic workflows, a linear response in dilution series generated from pooled quality control samples is used to assess the quality of the measurement of molecules measured before further analysis.
 Most of the currently used software only allow the analyst to repetitively plot, view and analyse the dilution curves one at a time, a tedious and time-consuming process.
-In addition, summary statistics of dilution curves are limited to the Pearson Correlation Coefficient $R$ and/or Coefficient Of Determination $R^2$, which are insufficient to fully understand the shape of the dilution curves.
-DCVtestkit aims to provide additional summary statistics for dilution curves, taken from previous publications but which are not implemented in the current software tools.
+In addition, summary statistics of dilution curves are limited to the Pearson Correlation Coefficient which is insufficient to fully understand the shape of the dilution curves.
+*DCVtestkit* aims to provide additional summary statistics for dilution curves, taken from previous publications but which are not implemented in the current software tools.
 It also helps to reduce the analyst’s workload by analysing many dilution curves automatically, reporting the statistical results in Excel and recording the dilution plots in a pdf file.
-In addition, it can also create an interactive trellis displayed as a HTML folder for more exploratory analyses.
+In addition, it can also create an interactive trellis displayed as a HTML folder for more exploratory analysis.
 
@@
 
-Dilution curves have been used in many areas of biomedical and pharmaceutical sciences.
-In the field of metabolomics and lipidomics, dilution curves for each molecule measured, usually in a quality control sample generated by pooling equal aliquots from each study sample, are plotted as proposed by @croixmarie2009 to check if the sample matrix is the same among all samples.
-Molecules that do not show a linear dilution curve can be rejected before further statistical analysis, in spite of their relevance to the study, as their quantitation in different sample groups might be compromised.
-A cut off Pearson Correlation Coefficient value of $0.8$ is commonly used to balance the risk of accepting or removing signals related to relevant molecules.
-As such, many laboratories use commercial software to plot these dilution curves and report their corresponding Pearson Correlation Coefficient value.
-These include either mass spectrometry vendors’ software or, more in general, programs such as Excel and GraphPad Prism.
-Nevertheless, these tools have limitations.
+Linearity assessment is one of the criteria used to evaluate the precision of a quantitative measurement procedure as seen in calibration studies @rodríguez1993  and drug analysis @needleman1990.
+In metabolomics/lipidomics analysis, dilution curves are plotted for each molecule measured from quality control sample, generated by pooling equal aliquots from each study sample.
+Molecules that exhibits a non-linear relationship are rejected before further statistical analysis, as their quantification in different sample groups might be compromised.
+Dilution curves are usually plotted using general-purpose software like Excel with their corresponding Pearson Correlation Coefficient value.
+A threshold value of 0.8 is used to balance the risk of accepting or removing non-linear signals related to relevant molecules.
 
-While the Pearson Correlation Coefficient $R$ and/or Coefficient Of Determination $R^2$ are popular indicators of how well the dilution points fits a linear line, @sonnergaard2006 estimated that these are not effective standalone numeric parameter to estimate linearity.
-Using a modified version of Anscombe’s quartet, the paper showed that a high coefficient of determination does not reflect well a curve relationship.
-Both @croixmarie2009 and @sands2021 support this view, by indicating that an obvious non-linear response at the high and/or low ends of the quality control sample-based dilution curve can still yield a high correlation coefficient.
-This is in agreement with @sanchez2021 findings of several saturated calibration curves with $R$ values greater than $0.995$.
+However, @sonnergaard2006 warned that the Pearson Correlation Coefficient is not an effective standalone numeric parameter to estimate linearity.
+While researchers have created other metrics for linearity evaluation, these metrics are rarely implemented in most general-purpose software.
+Furthermore, today’s metabolomics/lipidomics workflow can measure hundreds of molecules.
+Having the analyst to individually plot numerous curves to check for linearity is time consuming.
 
-Fortunately, researchers who have studied deeply model validation and misspecification have provided alternative graphical and statistical methods to improve the reliability of linearity assessments.
-For example, @vanloco2002 highlighted the presence of alternative statistics, such as the Lack-of-fit test and quality coefficient, that can be used to make better judgement on the shape of the dilution curve.
-While the progress in finding better metrics and algorithms to evaluate the linearity of dilution curves is commendable, these findings are rarely implemented in more general-purpose software.
+R package, *DCVtestkit* addresses these issues by assisting analysts, to plot dilution curves for many molecules easily with additional metrics, other than the Pearson Correlation Coefficient, that better describe the curve’s shape.
+It also provides an interactive viewer for analysts to group, filter and sort the plots, allowing them to look at the relevant ones, such as the saturated dilution curves, and identify problematic molecules quickly.
 
-In addition, with the advancement of the technology used for molecular identification coupled with a high emphasis on high throughput analysis and automation, today’s targeted metabolomics/lipidomics can include more than eight hundred analytes measured by a single method.
-This number can also increase further in an untargeted approach.
-In these cases, using general-purpose programs to plot dilution curves for every single molecule may be tedious.
-Moreover, the reports generated by these programs are static dilution plots coupled with a statistical summary table.
-Having the analyst to look at five hundred dilution curves individually is time consuming and inefficient for data evaluation.
+# Approach
 
-To address the issues mentioned above, we have created an R package, *DCVtestkit*, to assist analysts, not only to plot these dilution curves for many molecules easily but also providing additional statistical results, other than the Pearson Correlation Coefficient $R$ or coefficient of determination $R^2$, for these curves.
-These alternative statistical results may be helpful in better describing the shape of the dilution curve.
-The R package also provides several ways of reporting the dilution data, including an interactive html file.
-This allows the analyst to group, filter and sort the dilution plots, to only look at the relevant ones, such as the saturated dilution curves, and identify problematic molecules quickly.
-
-# General Workflow
-
-Here, we introduce the workflow used by our R package, *DCVtestkit* in @fig-DCVtestkit-Workflow.
-
-::: {#fig-DCVtestkit-Workflow layout-ncol=1}
-
+::: {#fig-DCVtestkit-Workflow layout-ncol="1"}
 ![](images/README-Workflow.png)
@@
 
-Beginning with the Input Data phase, the workflow starts with two tables: a table (Transition Signal Data) containing transition signals (y-axis for dilution curve) for each sample and a table (Dilution Annotation) containing dilution curve related information for each sample, such as concentration (x-axis for dilution curve) and dilution batches.
-As, the two tables share the same sample list, it can be merged together into one table (Dilution Table) using the function `create_dilution_table`.
+The workflow starts with two tables: Transition Signal Data, containing transition signals (y-axis for dilution curve) for each sample and Dilution Annotation, containing dilution curve related information, such as concentration (x-axis for dilution curve) and dilution batches.
+Using a common column Sample Name, the two tables can be merged into one table (Dilution Table) via `create_dilution_table`.
 
-During the Calculation stage of the workflow, the summary statistics are calculated using the function `summarise_dilution_table` for each dilution curve corresponding to a dilution batch and transition.
-Optionally, analysts can use the function `evaluate_linearity` to group the dilution curves based on the summary statistics.
-These tabular results can be reported as an Excel sheet using the function `write_summary_excel`.
+Next, summary statistics are calculated via `summarise_dilution_table` for each dilution curve.
+Besides the Pearson Correlation Coefficient, additional parameters introduced are results from Mandel’s Fitting Test @andrade2013 in which a low $p$ value gives sufficient evidence that a quadratic model fits better than a linear model, indicating the curve may not be linear.
+Another parameter is Percent Residual Accuracy @logue2018 which ranges from $-\infty$ to $100$.
+If the curve is linear, the value should be close to $100$.
+The software also calculates the concavity of a fitted quadratic model to identify if the curve is dominantly non-linear at high (concavity $<0$) or low (concavity $>0$) concentrations.
 
-With the summary statistics results, the workflow can proceed to the Dilution Curve Plotting phase in which static and interactive dilution plots can be created using `add_ggplot_panel` and `add_plotly_panel` respectively.
-Static plots are output as a pdf file while the interactive plots are output as a HTML folder containing several folders and one `index.html` file.
-Analysts can view the interactive plots by double clicking on the `index.html` file.
+Supplementary Figure 1 gives the summary statistics of three manually curated curves: A linear curve and curves with a plateau at higher concentrations (denoted as saturated curves) and lower concentrations (denoted as limit or detection or LOD curves) respectively.
+The corresponding Pearson Correlation Coefficient values (`r_corr`) are $\ge0.9$ ($0.99$, $0.95$ and $0.98$ respectively), even for the curves that are non-linear.
+However, both saturated and LOD curves give a much lower Mandel’s Fitting Test $p$ values (`mandel_p_val`) ($1.66 * 10^{-4}$ and $2.56 * 10^{-3}$ respectively vs $0.38$).
+Likewise, the Percent Residual Accuracy values (`pra_linear`) are much lower in the saturated and LOD curves compared to the linear curve ($62.30$ and $74.69$ respectively vs $94.32$).
 
-# Statistical Summary for Dilution Curves
-
-@fig-curves gives a plot of three manually curated curves together with their corresponding summary statistics.
-The characteristic of three curves are as follows: One is a linear curve.
-Another is having a plateau at higher concentrations, also known as a saturated curve.
-The last example is a curve with a plateau at lower concentrations or experiencing a limit of detection (denoted as LOD curves in this paper).
-It can be observed that the corresponding Pearson Correlation Coefficient values, denoted as `r_corr`, are $\ge0.9$ ($0.99$, $0.95$ and $0.98$ respectively) even for the curves that are non-linear.
-These results are in agreement with @vanloco2002 as well as @logue2018 arguments that the Pearson Correlation Coefficient is a poor descriptor of non-linear calibration curves.
-
-To improve the description of the goodness-of-fit for linear dilution curves, a few additional parameters, on top of the popular Pearson Correlation Coefficient $R$, are added in the R package *DCVtestkit*.
-The first additional parameters are statistical results from Mandel’s Fitting Test (as reported in @andrade2013) in which a low $p$ value gives sufficient evidence that a quadratic model is a better fit than a linear model, indicating the curve may not be linear.
-Another parameter calculated is the Percent Residual Accuracy (as reported in @logue2018) which ranges from $-\infty$ to $100$.
-If the curve is linear, the value should be close to $100$.
-Finally, the software also fits a quadratic model on the dilution curve and calculates the concavity, trying to verify if the dilution curve is predominantly non-linear at high (concavity $<0$) or low (concavity $>0$) concentrations.
-
-Returning to @fig-curves, both the saturated and LOD curves give a much lower Mandel’s Fitting Test $p$ values, denoted as `mandel_p_val`, ($1.66 * 10^{-4}$ and $2.56 * 10^{-3}$ respectively vs $0.38$).
-Correspondingly, ranging from $-\infty$ to $100$, the Percent Residual Accuracy values, denoted as `pra_linear`, are much lower in the saturated and LOD curves compared to the linear curve ($62.30$ and $74.69$ respectively vs $94.32$).
-
-```{r Motivation, echo = FALSE}
-#| echo: false
-
-linear_data <- data.frame(
-  conc_var = c(10, 25, 40, 50, 60,
-               75, 80, 100, 125, 150),
-  signal_var = c(25463, 63387, 90624, 131274, 138069,
-                 205353, 202407, 260205, 292257, 367924)
-)
-
-saturated_data <- data.frame(
-  conc_var = c(10, 25, 40, 50, 60,
-               75, 80, 100, 125, 150),
-  signal_var = c(5192648, 16594991, 32507833, 46499896,
-                 55388856, 62505210, 62778078, 72158161,
-                 78044338, 86158414)
-)
-
-lod_data <- data.frame(
-  conc_var = c(10, 25, 40, 50, 60,
-               75, 80, 100, 125, 150),
-  signal_var = c(500, 903, 1267, 2031, 2100,
-                 3563, 4500, 5300, 8500, 10430)
-)
-
-tabular_display <- tibble::tibble(
-  Concentration = c(10, 25, 40, 50, 60,
-                    75, 80, 100, 125, 150), 
-  `Linear signal` = c(25463, 63387, 90624, 131274, 138069,
-                    205353, 202407, 260205, 292257, 367924),
-  `Saturated signal` = c(5192648, 16594991, 32507833, 46499896,
-                       55388856, 62505210, 62778078, 72158161,
-                       78044338, 86158414),
-  `LOD signal` = c(500, 903, 1267, 2031, 2100,
-                 3563, 4500, 5300, 8500, 10430)
-)
-
-concentration_table <- gridExtra::tableGrob(
-  d = tabular_display, 
-  rows = NULL,
-  theme = gridExtra::ttheme_default(
-    core=list(fg_params=list(hjust=1, x=0.9))
-    )
-  ) 
-```
-
-```{r create linear plot}
-#| echo: false
-
-# Get dilution summary
-statistical_summary <- DCVtestkit::summarise_dilution_data(
-  linear_data, 
-  "conc_var", 
-  "signal_var")
-
-table <- DCVtestkit::plot_summary_table(statistical_summary)
-
-# Model the data
-linear_model <- DCVtestkit::create_linear_model(linear_data, 
-                                                "conc_var", "signal_var")
-quad_model <- DCVtestkit::create_quad_model(linear_data, 
-                                            "conc_var", "signal_var")
-
-dilution <- seq(min(linear_data$conc_var, na.rm = TRUE),
-                max(linear_data$conc_var, na.rm = TRUE),
-                length.out = 15)
-
-# Create the y values for the line
-y_lin_predict <- stats::predict(linear_model,
-                                tibble::tibble("conc_var" := dilution))
-y_quad_predict <- stats::predict(quad_model,
-                                 tibble::tibble("conc_var" := dilution))
-reg_data <- data.frame(
-  dilution = dilution,
-  y_lin_predict = y_lin_predict,
-  y_quad_predict = y_quad_predict
-)
-
-reg_col_vec <- c("Lin" = "black", "Quad" = "red")
-
-linear_plot <- ggplot2::ggplot(linear_data) +
-  ggplot2::aes(x = .data$conc_var,
-               y = .data$signal_var
-               ) +
-    ggplot2::geom_point(size = 5, colour = "#746ab0") +
-  ggplot2::geom_line(data = reg_data,
-                           mapping = ggplot2::aes(x = dilution, y=y_lin_predict,
-                                                  colour = "Lin")
-        ) +
-  ggplot2::geom_line(data = reg_data,
-                     mapping = ggplot2::aes(x = dilution, y=y_quad_predict,
-                                            colour = "Quad")
-  ) +
-  ggplot2::scale_colour_manual(values = c(reg_col_vec),
-                               labels = names(c(reg_col_vec)),
-                               guide = ggplot2::guide_legend(override.aes = list(
-                                 linetype = c(rep("solid", length(reg_col_vec))),
-                                 shape = c(rep(NA, length(reg_col_vec))),
-                                 colour = c(reg_col_vec)
-                               ))
-    ) +
-  ggplot2::theme(
-    legend.title = ggplot2::element_blank(),
-    legend.position = "top",
-    axis.title.y = ggplot2::element_text(angle = 0,
-                                         vjust = 1)
-  ) +
-  ggplot2::labs(title = "Linear",
-                x = "Concentration",
-                y = "Signal")
-
-linear_plot <- patchwork::wrap_plots(linear_plot, table, ncol = 2, nrow = 1)
-```
-
-```{r create saturation plot}
-#| echo: false
-
-# Get dilution summary
-statistical_summary <- DCVtestkit::summarise_dilution_data(
-  saturated_data, 
-  "conc_var", 
-  "signal_var")
-
-table <- DCVtestkit::plot_summary_table(statistical_summary)
-
-# Model the data
-linear_model <- DCVtestkit::create_linear_model(saturated_data, 
-                                                "conc_var", "signal_var")
-quad_model <- DCVtestkit::create_quad_model(saturated_data, 
-                                            "conc_var", "signal_var")
-
-dilution <- seq(min(saturated_data$conc_var, na.rm = TRUE),
-                max(saturated_data$conc_var, na.rm = TRUE),
-                length.out = 15)
-
-# Create the y values for the line
-y_lin_predict <- stats::predict(linear_model,
-                                tibble::tibble("conc_var" := dilution))
-y_quad_predict <- stats::predict(quad_model,
-                                 tibble::tibble("conc_var" := dilution))
-reg_data <- data.frame(
-  dilution = dilution,
-  y_lin_predict = y_lin_predict,
-  y_quad_predict = y_quad_predict
-)
-
-reg_col_vec <- c("Lin" = "black", "Quad" = "red")
-
-saturation_plot <- ggplot2::ggplot(saturated_data) +
-  ggplot2::aes(x = .data$conc_var,
-               y = .data$signal_var
-               ) +
-    ggplot2::geom_point(size = 5, colour = "#377eb8") +
-  ggplot2::geom_line(data = reg_data,
-                           mapping = ggplot2::aes(x = dilution, y=y_lin_predict,
-                                                  colour = "Lin")
-        ) +
-  ggplot2::geom_line(data = reg_data,
-                     mapping = ggplot2::aes(x = dilution, y=y_quad_predict,
-                                            colour = "Quad")
-  ) +
-  ggplot2::scale_colour_manual(values = c(reg_col_vec),
-                               labels = names(c(reg_col_vec)),
-                               guide = ggplot2::guide_legend(override.aes = list(
-                                 linetype = c(rep("solid", length(reg_col_vec))),
-                                 shape = c(rep(NA, length(reg_col_vec))),
-                                 colour = c(reg_col_vec)
-                               ))
-    ) +
-  ggplot2::theme(
-    legend.title = ggplot2::element_blank(),
-    legend.position = "top",
-    axis.title.y = ggplot2::element_text(angle = 0,
-                                         vjust = 1)
-  ) +
-  ggplot2::labs(title = "Saturation",
-                x = "Concentration",
-                y = "Signal")
-
-saturation_plot <- patchwork::wrap_plots(saturation_plot, table, ncol = 2, nrow = 1)
-```
-
-```{r create lod plot}
-#| echo: false
-
-# Get dilution summary
-statistical_summary <- DCVtestkit::summarise_dilution_data(
-  lod_data, 
-  "conc_var", 
-  "signal_var")
-
-table <- DCVtestkit::plot_summary_table(statistical_summary)
-
-# Model the data
-linear_model <- DCVtestkit::create_linear_model(lod_data, 
-                                                "conc_var", "signal_var")
-quad_model <- DCVtestkit::create_quad_model(lod_data, 
-                                            "conc_var", "signal_var")
-
-dilution <- seq(min(lod_data$conc_var, na.rm = TRUE),
-                max(lod_data$conc_var, na.rm = TRUE),
-                length.out = 15)
-
-# Create the y values for the line
-y_lin_predict <- stats::predict(linear_model,
-                                tibble::tibble("conc_var" := dilution))
-y_quad_predict <- stats::predict(quad_model,
-                                 tibble::tibble("conc_var" := dilution))
-reg_data <- data.frame(
-  dilution = dilution,
-  y_lin_predict = y_lin_predict,
-  y_quad_predict = y_quad_predict
-)
-
-reg_col_vec <- c("Lin" = "black", "Quad" = "red")
-
-lod_plot <- ggplot2::ggplot(lod_data) +
-  ggplot2::aes(x = .data$conc_var,
-               y = .data$signal_var
-               ) +
-    ggplot2::geom_point(size = 5, colour = "#4daf4a") +
-  ggplot2::geom_line(data = reg_data,
-                           mapping = ggplot2::aes(x = dilution, y=y_lin_predict,
-                                                  colour = "Lin")
-        ) +
-  ggplot2::geom_line(data = reg_data,
-                     mapping = ggplot2::aes(x = dilution, y=y_quad_predict,
-                                            colour = "Quad")
-  ) +
-  ggplot2::scale_colour_manual(values = c(reg_col_vec),
-                               labels = names(c(reg_col_vec)),
-                               guide = ggplot2::guide_legend(override.aes = list(
-                                 linetype = c(rep("solid", length(reg_col_vec))),
-                                 shape = c(rep(NA, length(reg_col_vec))),
-                                 colour = c(reg_col_vec)
-                               ))
-    ) +
-  ggplot2::theme(
-    legend.title = ggplot2::element_blank(),
-    legend.position = "top",
-    axis.title.y = ggplot2::element_text(angle = 0,
-                                         vjust = 1)
-  ) +
-  ggplot2::labs(title = "LOD",
-                x = "Concentration",
-                y = "Signal")
-
-lod_plot <- patchwork::wrap_plots(lod_plot, table, ncol = 2, nrow = 1)
-```
-
-```{r ViewMotivationData1}
-#| echo: false
-#| label: fig-curves
-#| fig-height: 9
-#| fig-width: 13
-#| fig-cap: "Plots and statistical results of three curves: Linear curve, Saturated curve and a curve with Limit Of Detection (LOD)"
-
-patchwork::wrap_plots(
-  concentration_table, 
-  linear_plot, 
-  saturation_plot, 
-  lod_plot, 
-  ncol = 2, 
-  nrow = 2
-)
-```
-
-# Dilution Curve Grouping
-
-*DCVtestkit* uses the function `evaluate_linearity` to group the dilution curves.
-At this moment, two workflows are proposed.
-Workflow $1$ uses both the Pearson Correlation Coefficient and Percent Residual Accuracy to determine if the dilution curve is linear (labelled as Good Linearity) or not (labelled as Poor Linearity).
-Workflow $2$ goes one step further by using the Mandel’s Fitting Test and the concavity of the fitted quadratic model to check if the non-linear dilution curve plateaus at low concentrations (labelling them as limit of detection) or high concentrations (labelling them as saturation).
-Non-linear dilution curves that do not follow these trends are then labelled as Poor Linearity.
-
-::: {#fig-Dilution-Grouping-Workflow layout-ncol=1}
-
-![](images/README-LinearEvaluation.png)
-
-Dilution Curve Grouping Workflows
-:::
+`evaluate_linearity` is used to group the curves according to the workflows proposed in Supplementary Figure 2.
+Workflow 1 uses the Pearson Correlation Coefficient and Percent Residual Accuracy to determine if the curve is linear (labelled as Good Linearity) or not (labelled as Poor Linearity).
+Workflow 2 goes one step further, using the Mandel’s Fitting Test and the fitted quadratic model’s concavity to check if the non-linear curve plateaus at low (labeled as limit of detection) or high (labelled as saturation) concentrations.
+Non-linear curves that do not follow these trends are labelled as Poor Linearity.
 
@@
 
-Workflow $2$ was tested on `r nrow(linear_dilution_summary)` simulated linear curves (labelled as Linear), `r nrow(lod_dilution_summary)` curves that plateau at low concentrations (labelled as Limit of Detection) and `r nrow(saturation_dilution_summary)` curves that plateau at high concentrations (labelled as Saturated).
-A benchmark workflow using only Pearson Correlation Coefficient with a cut off value of $0.8$ is used to compare with Workflow $2$.
-
-```{r}
+```{r Simulation Results Table}
 #| echo: false
@@
   ) |> 
-  modify_header(
-    all_stat_cols() ~ "**{level}**\nN = {n}"
+  gtsummary::modify_header(
+    gtsummary::all_stat_cols() ~ "**{level}**\nN = {n}"
     ) |> 
   gtsummary::modify_spanning_header(
-    all_stat_cols() ~ "**Simulated Curve Type**"
+    gtsummary::all_stat_cols() ~ "**Simulated Curve Type**"
     )
-
-simulation_results |> 
-  gtsummary::as_flex_table() |> 
-  flextable::set_table_properties(width = 1, layout = "autofit") |>
-  flextable::save_as_image(
-    path = here::here("Manuscript",
-                      "images",
-                      "simulation_results.png"), 
-    webshot = "webshot2")
 ```
 
-::: {#fig-Simulation-Result layout-ncol=1}
+A benchmark workflow using only Pearson Correlation Coefficient value of $0.8$ is compared with Workflow 2 on simulated data sets of `r nrow(linear_dilution_summary)` linear curves (labelled as Linear), curves that plateau at low (labelled as Limit of Detection) high (labelled as Saturated) concentrations each.
+Supplementary Figure 3 showed that Workflow 2 better identifies the saturated and limit of detection curves than the benchmark workflow.
+While it identifies less linear curves correctly than the benchmark workflow, its score of `r inline_text(simulation_results, variable = wf2_group, level = "Good Linearity", column = "Linear")` is comparable.
+See <https://dcvtestkit-simulation.netlify.app> for report details.
+While the threshold values of Pearson Correlation Coefficient and Percent Residual Accuracy are based on the interpretation of @y.h.chan2003 and @logue2018, respectively, they remain subjective and arbitrary.
+Nevertheless, *DCVtestkit* allows optimization of these threshold values according to the analyst’s determinants of linearity.
 
-![](images/simulation_results.png)
-
-Simulation Results
-:::
-
-@fig-Simulation-Result showed that Workflow $2$ is able to identify the saturated and limit of detection curves better than the benchmark workflow.
-On the other hand, while Workflow $2$ is able to identify less linear curves than the benchmark workflow, the results are comparable score of `r inline_text(simulation_results, variable = wf2_group, level = "Good Linearity", column = "Linear")`
-
-While the proposed workflows' threshold values of Pearson Correlation Coefficient and Percent Residual Accuracy are based on the interpretation given by @y.h.chan2003 and @logue2018, respectively, these cut off values remain subjective and arbitrary.
-Moreover, it is also possible for the dilution curve to exhibit a sigmoidal relationship, or non-linear, at both low and high concentrations, which the proposed workflow would be unable to identify.
-
-Nevertheless, while the proposed workflow is not a perfect solution, *DCVtestkit* allows the analyst to change and optimise the threshold values, to adjust the determinants of linearity and saturation of dilution curves according to the user’s needs.
-More information on how to perform such customisation can be found in the program documentation titled: ["Customise Linearity Evaluation Workflow"](https://slinghub.github.io/DCVtestkit/articles/lineval-customization.html).
-Furthermore, it is also possible to output these statistical summaries in Excel without the classification results.
-
-# Results Distribution
-
-Lastly, *DCVtestkit* can export the statistical results of each dilution curve in Excel.
-Furthermore, it can report the list of dilution plots as static charts with the statistical summary results included in a single pdf file.
-
-As some may find the final pdf file too complex for further interpretation, the R package also provides an interactive viewer, as a HTML folder, to look at dilution plots in a trellis display framework, as introduced in @becker1996.
-Clicking on the `index.html` file inside the folder will open the interactive viewer that allows the user to group, filter and sort these trellis charts in a meaningful way, based on @hafen2013's definition of "cognostics" or computer guiding diagnostics.
-This allows the user to do exploratory data analysis, such as identifying groups of molecules with linearity issues or finding out the effects of changing the Pearson Correlation Coefficient to another value.
-Such tasks can be challenging and time consuming if only the Excel and pdf files full of static plots were provided.
-
-::: {#fig-Viewing-Interactive-Curves layout-ncol=1}
-
-![](images/README-TrellisOutput.png)
-
-Viewing Several Interactive Dilution Curves
-:::
-
-An example of an interactive viewer created by *DCVtestkit* can be accessed from <https://dcvtestkit-interactive-example.netlify.app/>.
-Such interactive visualisation was also utilised by @hafen2019 in the exploration of proteomics, metabolomics and lipidomics data in a multi-omics approach.
-The HTML folder can be compressed as a zip file and shared as a pdf or Excel file.
-This interactive viewer can also be displayed as a report created from Quarto (https://quarto.org/), an open-source scientific and technical publishing system.
-The report can be viewed at <https://dcvtestkit-quarto-example.netlify.app/>
-R script and result outputs can be found in the Supplementary Material or by accessing this GitHub page <https://github.com/JauntyJJS/DCVtestkit_Output>
-
-An example of an interactive viewer created by *DCVtestkit* can be accessed from <https://dcvtestkit-interactive-example.netlify.app/>.
-Such interactive visualisation was also utilised by @hafen2019 in the exploration of proteomics, metabolomics, and lipidomics data in a multi-omics fashion.
-The HTML folder can be compressed as a zip file and distributed to others like a pdf or Excel file.
-This interactive viewer can also be displayed in as a report created from Quarto (<https://quarto.org/>), an open-source scientific and technical publishing system.
-The report can be viewed at <https://dcvtestkit-quarto-example.netlify.app/>.
-R script and result outputs can be found in the Supplementary Material or by accessing this GitHub page <https://github.com/JauntyJJS/DCVtestkit_Output>.
+Although *DCVtestkit* can export the results in Excel or pdf, they may be too complex for meaningful interpretation.
+Supplementary Figure 4 shows a HTML folder, exported by *DCVtestkit*, such that clicking on the `index.html` file inside the folder will open an interactive trellis plots that analysts can be grouped, filtered and sorted.
+This allows room for exploratory data analysis, such as identifying molecules with linearity issues or finding out the effects of changing the Pearson Correlation Coefficient threshold to another value.
+Such information is hard to achieve with the Excel and pdf files.
+An example of an interactive viewer created by *DCVtestkit* can be viewed at <https://dcvtestkit-interactive-example.netlify.app>
 
@@
 
-A linear response in quality control dilution curves is one of the requirements in metabolomics and lipidomics to assess the suitability of the molecules measured for further analysis.
-Despite its importance in testing data quality, the shortage of software tools to analyse dilution curves effectively and efficiently prevents researchers from fully analysing data.
-An R package called *DCVtestkit* is created to rectify this issue by allowing many dilution curves to be analysed quickly and reliably.
-This is done by the use of alternative statistics, other than the Pearson Correlation Coefficient, to better understand the linearity of the dilution curves, as well as reporting of statistical results and dilution plots that can be distributed to others.
-It is also able to provide an interactive trellis plot for exploratory data analysis.
-The R package is available on GitHub <https://github.com/SLINGhub/DCVtestkit> while the documentation and tutorials can be accessed from <https://slinghub.github.io/DCVtestkit/>.
-As *DCVtestkit* is an opensource software, it is accessible to collaboration works which can help improve its usability and performance in the future.
+To verify if a quantitative analytical test method is reliable, it is important to check for linearity.
+A linear response in quality control dilution curves is required in metabolomics/lipidomics to assess the molecules’ suitability for further analysis.
+However, there are few software that can analyse dilution curves efficiently.
+R package, *DCVtestkit*, rectifies this by plotting of many dilution curves quickly by automation and reporting alternative statistics, other than the Pearson Correlation Coefficient, to better describe the shape of dilution curves.
+It also provides an interactive trellis plot for exploratory data analysis.
+It is available on GitHub <https://github.com/SLINGhub/DCVtestkit> while the documentation and tutorials can be accessed from <https://slinghub.github.io/DCVtestkit>.
 

### 2022-11-01 Manuscript/supplementary.qmd
Shorten article to < 1000 words and one picture. Added one file for supplementary figures.

---
title: "Supplementary for *DCVtestkit*: a R package for linearity assessment and analysis of quality control dilution curves"
format: docx
---

```{r R packages}
#| echo: false
#| message: false

library(dplyr)
library(stringr)
library(here)
library(tibble)
library(ggplot2)
library(gridExtra)
library(patchwork)
library(labelled)
library(gtsummary)
library(flextable)
library(webshot2)
library(DCVtestkit)
```

```{r Motivation, echo = FALSE}
#| echo: false

linear_data <- data.frame(
  conc_var = c(10, 25, 40, 50, 60,
               75, 80, 100, 125, 150),
  signal_var = c(25463, 63387, 90624, 131274, 138069,
                 205353, 202407, 260205, 292257, 367924)
)

saturated_data <- data.frame(
  conc_var = c(10, 25, 40, 50, 60,
               75, 80, 100, 125, 150),
  signal_var = c(5192648, 16594991, 32507833, 46499896,
                 55388856, 62505210, 62778078, 72158161,
                 78044338, 86158414)
)

lod_data <- data.frame(
  conc_var = c(10, 25, 40, 50, 60,
               75, 80, 100, 125, 150),
  signal_var = c(500, 903, 1267, 2031, 2100,
                 3563, 4500, 5300, 8500, 10430)
)

tabular_display <- tibble::tibble(
  Concentration = c(10, 25, 40, 50, 60,
                    75, 80, 100, 125, 150), 
  `Linear signal` = c(25463, 63387, 90624, 131274, 138069,
                    205353, 202407, 260205, 292257, 367924),
  `Saturated signal` = c(5192648, 16594991, 32507833, 46499896,
                       55388856, 62505210, 62778078, 72158161,
                       78044338, 86158414),
  `LOD signal` = c(500, 903, 1267, 2031, 2100,
                 3563, 4500, 5300, 8500, 10430)
)

concentration_table <- gridExtra::tableGrob(
  d = tabular_display, 
  rows = NULL,
  theme = gridExtra::ttheme_default(
    core=list(fg_params=list(hjust=1, x=0.9))
    )
  ) 
```

```{r create linear plot}
#| echo: false

# Get dilution summary
statistical_summary <- DCVtestkit::summarise_dilution_data(
  linear_data, 
  "conc_var", 
  "signal_var")

table <- DCVtestkit::plot_summary_table(statistical_summary)

# Model the data
linear_model <- DCVtestkit::create_linear_model(linear_data, 
                                                "conc_var", "signal_var")
quad_model <- DCVtestkit::create_quad_model(linear_data, 
                                            "conc_var", "signal_var")

dilution <- seq(min(linear_data$conc_var, na.rm = TRUE),
                max(linear_data$conc_var, na.rm = TRUE),
                length.out = 15)

# Create the y values for the line
y_lin_predict <- stats::predict(linear_model,
                                tibble::tibble("conc_var" := dilution))
y_quad_predict <- stats::predict(quad_model,
                                 tibble::tibble("conc_var" := dilution))
reg_data <- data.frame(
  dilution = dilution,
  y_lin_predict = y_lin_predict,
  y_quad_predict = y_quad_predict
)

reg_col_vec <- c("Lin" = "black", "Quad" = "red")

linear_plot <- ggplot2::ggplot(linear_data) +
  ggplot2::aes(x = .data$conc_var,
               y = .data$signal_var
               ) +
    ggplot2::geom_point(size = 5, colour = "#746ab0") +
  ggplot2::geom_line(data = reg_data,
                           mapping = ggplot2::aes(x = dilution, y=y_lin_predict,
                                                  colour = "Lin")
        ) +
  ggplot2::geom_line(data = reg_data,
                     mapping = ggplot2::aes(x = dilution, y=y_quad_predict,
                                            colour = "Quad")
  ) +
  ggplot2::scale_colour_manual(values = c(reg_col_vec),
                               labels = names(c(reg_col_vec)),
                               guide = ggplot2::guide_legend(override.aes = list(
                                 linetype = c(rep("solid", length(reg_col_vec))),
                                 shape = c(rep(NA, length(reg_col_vec))),
                                 colour = c(reg_col_vec)
                               ))
    ) +
  ggplot2::theme(
    legend.title = ggplot2::element_blank(),
    legend.position = "top",
    axis.title.y = ggplot2::element_text(angle = 0,
                                         vjust = 1)
  ) +
  ggplot2::labs(title = "Linear",
                x = "Concentration",
                y = "Signal")

linear_plot <- patchwork::wrap_plots(linear_plot, table, ncol = 2, nrow = 1)
```

```{r create saturation plot}
#| echo: false

# Get dilution summary
statistical_summary <- DCVtestkit::summarise_dilution_data(
  saturated_data, 
  "conc_var", 
  "signal_var")

table <- DCVtestkit::plot_summary_table(statistical_summary)

# Model the data
linear_model <- DCVtestkit::create_linear_model(saturated_data, 
                                                "conc_var", "signal_var")
quad_model <- DCVtestkit::create_quad_model(saturated_data, 
                                            "conc_var", "signal_var")

dilution <- seq(min(saturated_data$conc_var, na.rm = TRUE),
                max(saturated_data$conc_var, na.rm = TRUE),
                length.out = 15)

# Create the y values for the line
y_lin_predict <- stats::predict(linear_model,
                                tibble::tibble("conc_var" := dilution))
y_quad_predict <- stats::predict(quad_model,
                                 tibble::tibble("conc_var" := dilution))
reg_data <- data.frame(
  dilution = dilution,
  y_lin_predict = y_lin_predict,
  y_quad_predict = y_quad_predict
)

reg_col_vec <- c("Lin" = "black", "Quad" = "red")

saturation_plot <- ggplot2::ggplot(saturated_data) +
  ggplot2::aes(x = .data$conc_var,
               y = .data$signal_var
               ) +
    ggplot2::geom_point(size = 5, colour = "#377eb8") +
  ggplot2::geom_line(data = reg_data,
                           mapping = ggplot2::aes(x = dilution, y=y_lin_predict,
                                                  colour = "Lin")
        ) +
  ggplot2::geom_line(data = reg_data,
                     mapping = ggplot2::aes(x = dilution, y=y_quad_predict,
                                            colour = "Quad")
  ) +
  ggplot2::scale_colour_manual(values = c(reg_col_vec),
                               labels = names(c(reg_col_vec)),
                               guide = ggplot2::guide_legend(override.aes = list(
                                 linetype = c(rep("solid", length(reg_col_vec))),
                                 shape = c(rep(NA, length(reg_col_vec))),
                                 colour = c(reg_col_vec)
                               ))
    ) +
  ggplot2::theme(
    legend.title = ggplot2::element_blank(),
    legend.position = "top",
    axis.title.y = ggplot2::element_text(angle = 0,
                                         vjust = 1)
  ) +
  ggplot2::labs(title = "Saturation",
                x = "Concentration",
                y = "Signal")

saturation_plot <- patchwork::wrap_plots(saturation_plot, table, ncol = 2, nrow = 1)
```

```{r create lod plot}
#| echo: false

# Get dilution summary
statistical_summary <- DCVtestkit::summarise_dilution_data(
  lod_data, 
  "conc_var", 
  "signal_var")

table <- DCVtestkit::plot_summary_table(statistical_summary)

# Model the data
linear_model <- DCVtestkit::create_linear_model(lod_data, 
                                                "conc_var", "signal_var")
quad_model <- DCVtestkit::create_quad_model(lod_data, 
                                            "conc_var", "signal_var")

dilution <- seq(min(lod_data$conc_var, na.rm = TRUE),
                max(lod_data$conc_var, na.rm = TRUE),
                length.out = 15)

# Create the y values for the line
y_lin_predict <- stats::predict(linear_model,
                                tibble::tibble("conc_var" := dilution))
y_quad_predict <- stats::predict(quad_model,
                                 tibble::tibble("conc_var" := dilution))
reg_data <- data.frame(
  dilution = dilution,
  y_lin_predict = y_lin_predict,
  y_quad_predict = y_quad_predict
)

reg_col_vec <- c("Lin" = "black", "Quad" = "red")

lod_plot <- ggplot2::ggplot(lod_data) +
  ggplot2::aes(x = .data$conc_var,
               y = .data$signal_var
               ) +
    ggplot2::geom_point(size = 5, colour = "#4daf4a") +
  ggplot2::geom_line(data = reg_data,
                           mapping = ggplot2::aes(x = dilution, y=y_lin_predict,
                                                  colour = "Lin")
        ) +
  ggplot2::geom_line(data = reg_data,
                     mapping = ggplot2::aes(x = dilution, y=y_quad_predict,
                                            colour = "Quad")
  ) +
  ggplot2::scale_colour_manual(values = c(reg_col_vec),
                               labels = names(c(reg_col_vec)),
                               guide = ggplot2::guide_legend(override.aes = list(
                                 linetype = c(rep("solid", length(reg_col_vec))),
                                 shape = c(rep(NA, length(reg_col_vec))),
                                 colour = c(reg_col_vec)
                               ))
    ) +
  ggplot2::theme(
    legend.title = ggplot2::element_blank(),
    legend.position = "top",
    axis.title.y = ggplot2::element_text(angle = 0,
                                         vjust = 1)
  ) +
  ggplot2::labs(title = "LOD",
                x = "Concentration",
                y = "Signal")

lod_plot <- patchwork::wrap_plots(lod_plot, table, ncol = 2, nrow = 1)
```

```{r ViewMotivationData1}
#| echo: false
#| fig-height: 9
#| fig-width: 13

patchwork::wrap_plots(
  concentration_table, 
  linear_plot, 
  saturation_plot, 
  lod_plot, 
  ncol = 2, 
  nrow = 2
)
```

*Supplementary Figure 1*:

Plots and statistical results of three curves: Linear curve, Saturated curve and a curve with Limit Of Detection (LOD)

::: {layout-ncol="1"}
![](images/README-LinearEvaluation.png)
:::

*Supplementary Figure 2*:

Dilution Curve Grouping Workflows

```{r Load Simulated Data Results}
#| echo: false
saturation_dilution_summary <-
  readRDS(file = here::here(
    "Quarto_Simulation",
    "saturation_dilution_summary.rds")
)

lod_dilution_summary <-
  readRDS(file = here::here(
    "Quarto_Simulation",
    "lod_dilution_summary.rds")
)

linear_dilution_summary <-
  readRDS(file = here::here(
    "Quarto_Simulation",
    "linear_dilution_summary.rds")
)
```

```{r Combine Simulated Data Results}
#| echo: false
saturation_dilution_summary <- saturation_dilution_summary |> 
  dplyr::mutate(curve_group = "Saturated")

lod_dilution_summary <- lod_dilution_summary |> 
  dplyr::mutate(curve_group = "Limit of Detection")

linear_dilution_summary <- linear_dilution_summary |> 
  dplyr::mutate(curve_group = "Linear")

combined_dilution_summary <-
  dplyr::bind_rows(
    saturation_dilution_summary,
    lod_dilution_summary,
    linear_dilution_summary
  ) 
```

```{r Data Wrangling for Simulation Results}
#| echo: false
combined_dilution_summary <- 
  combined_dilution_summary |> 
  dplyr::mutate(
    curve_group = factor(.data$curve_group,
                         levels = c("Linear",
                                    "Saturated",
                                    "Limit of Detection")),
    pearson_group = dplyr::case_when(
      .data$r_corr >= 0.8 ~ "more than or\nequal to 0.8",
      .data$r_corr < 0.8 ~ "less than 0.8",
    ),
    wf2_group = stringr::str_replace(
      string = .data$wf2_group,
      pattern = "LOD",
      replacement = "Limit of Detection"
    ),
    wf2_group = factor(.data$wf2_group,
                         levels = c("Good Linearity",
                                    "Saturation",
                                    "Limit of Detection",
                                    "Poor Linearity"))
  ) |> 
  labelled::set_variable_labels(
    ID = "Unique Curve Identifier",
    curve_group = "Simulated Curve Group",
    wf1_group = "Workflow 1 Grouping",
    wf2_group = "Workflow 2 Grouping",
    pearson_group = "Pearson Correlation\nCoefficient Grouping",
    r_corr = "Pearson Correlation\nCoefficient",
    pra_linear = "Percent Residual\nAccuracy",
    mandel_p_val = "Mandel's Test p Value",
    concavity = "Concavity Of Fitted Quadratic Model",
    r2_linear = "Coefficient Of Determination",
    r2_adj_linear = "Adjusted Coefficient Of Determination",
    mandel_stats = "Test statistics from Mandel's Test"
  )

```

```{r}
#| echo: false
#| output: false
simulation_results <- combined_dilution_summary |> 
  dplyr::select(c("curve_group", "wf2_group", 
                  "pearson_group"
                  # "r_corr", "pra_linear"
                  )
                ) |> 
  dplyr::relocate(c("pearson_group")) |> 
  gtsummary::tbl_summary(
    by = "curve_group",
    statistic = list(
      pearson_group ~ "{n}/{N} ({p}%)",
      wf2_group ~ "{n}/{N} ({p}%)"
    ),
    digits = list(
      wf2_group ~ c(0, 0, 1),
      pearson_group ~ c(0, 0, 1)
      #r_corr ~ c(2),
      #pra_linear ~ c(0)
      )
  ) |> 
  gtsummary::modify_header(
    gtsummary::all_stat_cols() ~ "**{level}**\nN = {n}"
    ) |> 
  gtsummary::modify_spanning_header(
    gtsummary::all_stat_cols() ~ "**Simulated Curve Type**"
    )

simulation_results |> 
  gtsummary::as_flex_table() |> 
  flextable::set_table_properties(width = 1, layout = "autofit") |>
  flextable::save_as_image(
    path = here::here("Manuscript",
                      "images",
                      "simulation_results.png"), 
    webshot = "webshot2")
```

::: {layout-ncol="1"}
![](images/simulation_results.png)
:::

*Supplementary Figure 3*:

Simulation Results

::: {layout-ncol="1"}
![](images/README-TrellisOutput.png)
:::

*Supplementary Figure 4*:

Viewing Several Interactive Dilution Curves

### 2022-11-01 Manuscript/manuscript.qmd
Fixed some citation issues.

@@
 
-Linearity assessment is one of the criteria used to evaluate the precision of a quantitative measurement procedure as seen in calibration studies @rodríguez1993  and drug analysis @needleman1990.
+Linearity assessment is one of the criteria used to evaluate the precision of a quantitative measurement procedure as seen in calibration studies from @rodríguez1993  and drug analysis from @needleman1990.
 In metabolomics/lipidomics analysis, dilution curves are plotted for each molecule measured from quality control sample, generated by pooling equal aliquots from each study sample.
@@
 Next, summary statistics are calculated via `summarise_dilution_table` for each dilution curve.
-Besides the Pearson Correlation Coefficient, additional parameters introduced are results from Mandel’s Fitting Test @andrade2013 in which a low $p$ value gives sufficient evidence that a quadratic model fits better than a linear model, indicating the curve may not be linear.
-Another parameter is Percent Residual Accuracy @logue2018 which ranges from $-\infty$ to $100$.
+Besides the Pearson Correlation Coefficient, additional parameters introduced are Mandel’s Fitting Test results from @andrade2013 in which a low $p$ value gives sufficient evidence that a quadratic model fits better than a linear model, indicating the curve may not be linear.
+Another parameter is Percent Residual Accuracy from @logue2018 which ranges from $-\infty$ to $100$.
 If the curve is linear, the value should be close to $100$.

### 2022-11-08 Manuscript/manuscript.qmd
Change figures between supplementary and manuscript. Add relevant equations.

@@
 title: "*DCVtestkit*: a R package for linearity assessment and analysis of quality control dilution curves"
+
 bibliography: bibliography.bib
@@
 format: docx
+
+crossref:
+  fig-title: Fig.
+  fig-prefix: Fig.
+  subref-labels: alpha A
+  title-delim: .
 ---
@@
 *DCVtestkit* aims to provide additional summary statistics for dilution curves, taken from previous publications but which are not implemented in the current software tools.
-It also helps to reduce the analyst’s workload by analysing many dilution curves automatically, reporting the statistical results in Excel and recording the dilution plots in a pdf file.
+It also helps to reduce the analyst's workload by analysing many dilution curves automatically, reporting the statistical results in Excel and recording the dilution plots in a pdf file.
 In addition, it can also create an interactive trellis displayed as a HTML folder for more exploratory analysis.
@@
 
+{{< pagebreak >}}
+
 # Introduction
@@
 While researchers have created other metrics for linearity evaluation, these metrics are rarely implemented in most general-purpose software.
-Furthermore, today’s metabolomics/lipidomics workflow can measure hundreds of molecules.
+Furthermore, today's metabolomics/lipidomics workflow can measure hundreds of molecules.
 Having the analyst to individually plot numerous curves to check for linearity is time consuming.
 
-R package, *DCVtestkit* addresses these issues by assisting analysts, to plot dilution curves for many molecules easily with additional metrics, other than the Pearson Correlation Coefficient, that better describe the curve’s shape.
+R package, *DCVtestkit* addresses these issues by assisting analysts, to plot dilution curves for many molecules easily with additional metrics, other than the Pearson Correlation Coefficient, that better describe the curve's shape.
 It also provides an interactive viewer for analysts to group, filter and sort the plots, allowing them to look at the relevant ones, such as the saturated dilution curves, and identify problematic molecules quickly.
@@
 
-::: {#fig-DCVtestkit-Workflow layout-ncol="1"}
-![](images/README-Workflow.png)
-
-*DCVtestkit* Workflow
-:::
-
+Supplementary Figure 1 depicts the workflow of *DCVtestkit*.
 The workflow starts with two tables: Transition Signal Data, containing transition signals (y-axis for dilution curve) for each sample and Dilution Annotation, containing dilution curve related information, such as concentration (x-axis for dilution curve) and dilution batches.
@@
 Next, summary statistics are calculated via `summarise_dilution_table` for each dilution curve.
-Besides the Pearson Correlation Coefficient, additional parameters introduced are Mandel’s Fitting Test results from @andrade2013 in which a low $p$ value gives sufficient evidence that a quadratic model fits better than a linear model, indicating the curve may not be linear.
-Another parameter is Percent Residual Accuracy from @logue2018 which ranges from $-\infty$ to $100$.
-If the curve is linear, the value should be close to $100$.
+Besides the Pearson Correlation Coefficient, one additional calculation is the Mandel's Fitting Test (@eq-mandel-test) from @andrade2013, in which $\mathrm S_{y/x,lin}^2$ and $\mathrm S_{y/x,quad}^2$ are the standard error of the regression divided by the regression's degrees of freedom for the linear model (@eq-s1) and quadratic model (@eq-s2) repsectively.
+A low $p$ value from the $F$ test gives sufficient evidence that a quadratic model fits better than a linear model, indicating the curve may not be linear.
+
+$$
+\mathrm F_{test} = \frac{(\mathrm n-2) \ \mathrm S_{y/x,lin}^2 \ - \ (\mathrm n-3) \ \mathrm S_{y/x,quad}^2}{\mathrm S_{y/x,quad}^2}
+$$ {#eq-mandel-test}
+
+$$
+\mathrm S_{y/x,lin}^2 = \frac{1}{n-2} \sum_{i=1}^{n} ( y_{i,pred} - y_{i,true})^2
+$$ {#eq-s1}
+
+$$
+\mathrm S_{y/x,quad}^2 = \frac{1}{n-3} \sum_{i=1}^{n} ( y_{i,pred} - y_{i,true})^2
+$$ {#eq-s2}
+
+Another one is Percent Residual Accuracy (@eq-pra) from @logue2018 in which $x_{i,true}$ is the true x-axis value and $x_{i,calc}$ is the predicted x-axis value from the linear model.
+Ranging from $-\infty$ to $100$, if the curve is linear, the value should be close to $100$.
+
+$$
+\% \ RA = \frac{100\%}{n} \sum_{i=1}^{n}\left(1 - \bigg| \frac{x_{i,true}-x_{i,pred}}{x_{i,true}} \bigg|\right)
+$$ {#eq-pra}
+
 The software also calculates the concavity of a fitted quadratic model to identify if the curve is dominantly non-linear at high (concavity $<0$) or low (concavity $>0$) concentrations.
 
-Supplementary Figure 1 gives the summary statistics of three manually curated curves: A linear curve and curves with a plateau at higher concentrations (denoted as saturated curves) and lower concentrations (denoted as limit or detection or LOD curves) respectively.
+Supplementary Figure 2 gives the summary statistics of three manually curated curves: A linear curve and curves with a plateau at higher concentrations (denoted as saturated curves) and lower concentrations (denoted as limit or detection or LOD curves) respectively.
 The corresponding Pearson Correlation Coefficient values (`r_corr`) are $\ge0.9$ ($0.99$, $0.95$ and $0.98$ respectively), even for the curves that are non-linear.
-However, both saturated and LOD curves give a much lower Mandel’s Fitting Test $p$ values (`mandel_p_val`) ($1.66 * 10^{-4}$ and $2.56 * 10^{-3}$ respectively vs $0.38$).
+However, both saturated and LOD curves give a much lower Mandel's Fitting Test $p$ values (`mandel_p_val`) ($1.66 * 10^{-4}$ and $2.56 * 10^{-3}$ respectively vs $0.38$).
 Likewise, the Percent Residual Accuracy values (`pra_linear`) are much lower in the saturated and LOD curves compared to the linear curve ($62.30$ and $74.69$ respectively vs $94.32$).
 
-`evaluate_linearity` is used to group the curves according to the workflows proposed in Supplementary Figure 2.
+::: {#fig-overview layout="[[50,-50], [60,-40]]"}
+![Curve Grouping Workflow](images/README-LinearEvaluation.png){#fig-linearity}
+
+![Interactive Trellis Plots](images/README-TrellisOutput.png){#fig-visualisation}
+
+*DCVtestkit*'s curve grouping workflow in @fig-linearity and interactive visualisation of curves in @fig-visualisation.
+:::
+
+`evaluate_linearity` is used to group the curves according to the workflows proposed in @fig-linearity.
 Workflow 1 uses the Pearson Correlation Coefficient and Percent Residual Accuracy to determine if the curve is linear (labelled as Good Linearity) or not (labelled as Poor Linearity).
-Workflow 2 goes one step further, using the Mandel’s Fitting Test and the fitted quadratic model’s concavity to check if the non-linear curve plateaus at low (labeled as limit of detection) or high (labelled as saturation) concentrations.
+Workflow 2 goes one step further, using the Mandel's Fitting Test and the fitted quadratic model's concavity to check if the non-linear curve plateaus at low (labeled as limit of detection) or high (labelled as saturation) concentrations.
 Non-linear curves that do not follow these trends are labelled as Poor Linearity.
@@
 While the threshold values of Pearson Correlation Coefficient and Percent Residual Accuracy are based on the interpretation of @y.h.chan2003 and @logue2018, respectively, they remain subjective and arbitrary.
-Nevertheless, *DCVtestkit* allows optimization of these threshold values according to the analyst’s determinants of linearity.
+Nevertheless, *DCVtestkit* allows optimization of these threshold values according to the analyst's determinants of linearity.
 
 Although *DCVtestkit* can export the results in Excel or pdf, they may be too complex for meaningful interpretation.
-Supplementary Figure 4 shows a HTML folder, exported by *DCVtestkit*, such that clicking on the `index.html` file inside the folder will open an interactive trellis plots that analysts can be grouped, filtered and sorted.
+@fig-visualisation shows a HTML folder, exported by *DCVtestkit*, such that clicking on the `index.html` file inside the folder will open an interactive trellis plots that analysts can be grouped, filtered and sorted.
 This allows room for exploratory data analysis, such as identifying molecules with linearity issues or finding out the effects of changing the Pearson Correlation Coefficient threshold to another value.
@@
 To verify if a quantitative analytical test method is reliable, it is important to check for linearity.
-A linear response in quality control dilution curves is required in metabolomics/lipidomics to assess the molecules’ suitability for further analysis.
+A linear response in quality control dilution curves is required in metabolomics/lipidomics to assess the molecules' suitability for further analysis.
 However, there are few software that can analyse dilution curves efficiently.

### 2022-11-08 Manuscript/supplementary.qmd
Change figures between supplementary and manuscript. Add relevant equations.

@@
 title: "Supplementary for *DCVtestkit*: a R package for linearity assessment and analysis of quality control dilution curves"
+
+bibliography: bibliography.bib
+csl: bioinfo.csl
 format: docx
+
+crossref:
+  fig-title: Supplementary Figure
 ---
@@
 ```
+
+![*DCVtestkit* Workflow](images/README-Workflow.png){#fig-DCVtestkit-Workflow}
 
@@
 #| echo: false
+#| label: fig-motivation
+#| fig-cap: "Plots and statistical results of three curves: Linear curve, Saturated curve and a curve with Limit Of Detection (LOD)."
 #| fig-height: 9
@@
 ```
-
-*Supplementary Figure 1*:
-
-Plots and statistical results of three curves: Linear curve, Saturated curve and a curve with Limit Of Detection (LOD)
-
-::: {layout-ncol="1"}
-![](images/README-LinearEvaluation.png)
-:::
-
-*Supplementary Figure 2*:
-
-Dilution Curve Grouping Workflows
 
@@
 
-::: {layout-ncol="1"}
-![](images/simulation_results.png)
-:::
-
-*Supplementary Figure 3*:
-
-Simulation Results
-
-::: {layout-ncol="1"}
-![](images/README-TrellisOutput.png)
-:::
-
-*Supplementary Figure 4*:
-
-Viewing Several Interactive Dilution Curves
+![Simulation Results](images/simulation_results.png){#fig-Simulation}

### 2022-11-09 Manuscript/manuscript.qmd
Fixed equation alignment issue and changed title.

@@
 ---
-title: "*DCVtestkit*: a R package for linearity assessment and analysis of quality control dilution curves"
+title: "*DCVtestkit*: a R package for linearity assessment and visualisation of multiple curves"
 
@@
 Next, summary statistics are calculated via `summarise_dilution_table` for each dilution curve.
-Besides the Pearson Correlation Coefficient, one additional calculation is the Mandel's Fitting Test (@eq-mandel-test) from @andrade2013, in which $\mathrm S_{y/x,lin}^2$ and $\mathrm S_{y/x,quad}^2$ are the standard error of the regression divided by the regression's degrees of freedom for the linear model (@eq-s1) and quadratic model (@eq-s2) repsectively.
+Besides the Pearson Correlation Coefficient, one additional calculation is the Mandel's Fitting Test ($F_{stats}$ in @eq-mandel-test) from @andrade2013.
 A low $p$ value from the $F$ test gives sufficient evidence that a quadratic model fits better than a linear model, indicating the curve may not be linear.
@@
 $$
-\mathrm F_{test} = \frac{(\mathrm n-2) \ \mathrm S_{y/x,lin}^2 \ - \ (\mathrm n-3) \ \mathrm S_{y/x,quad}^2}{\mathrm S_{y/x,quad}^2}
+\begin{aligned}
+&F_{stats} = \frac{(n-2) \ \mathrm S_{lin}^2 \ - \ (n-3) \ \mathrm S_{quad}^2}{\mathrm S_{quad}^2} \sim \ F(1,n-3)
+\\
+\\
+&\text{where}
+\\
+&\mathrm S_{lin}^2 = \frac{1}{n-2} \sum_{i=1}^{n} ( y_{i,lin} - y_{i,true})^2 
+\\
+&\mathrm S_{quad}^2 = \frac{1}{n-3} \sum_{i=1}^{n} ( y_{i,quad} - y_{i,true})^2
+\\ 
+&y_{i,lin} \ \text{is the linear model predicted y-axis value.}
+\\ 
+&y_{i,quad} \ \text{is the quadratic model predicted y-axis value.}
+\\ 
+&y_{i,true} \ \text{is the true y-axis value.}
+\\ 
+&n \ \text{is the number of data points.}
+\end{aligned}
 $$ {#eq-mandel-test}
+Another one is Percent Residual Accuracy ($\%RA$ in @eq-pra) from @logue2018. Ranging from $-\infty$ to $100$, if the curve is linear, the value should be close to $100$.
 
 $$
-\mathrm S_{y/x,lin}^2 = \frac{1}{n-2} \sum_{i=1}^{n} ( y_{i,pred} - y_{i,true})^2
-$$ {#eq-s1}
-
-$$
-\mathrm S_{y/x,quad}^2 = \frac{1}{n-3} \sum_{i=1}^{n} ( y_{i,pred} - y_{i,true})^2
-$$ {#eq-s2}
-
-Another one is Percent Residual Accuracy (@eq-pra) from @logue2018 in which $x_{i,true}$ is the true x-axis value and $x_{i,calc}$ is the predicted x-axis value from the linear model.
-Ranging from $-\infty$ to $100$, if the curve is linear, the value should be close to $100$.
-
-$$
-\% \ RA = \frac{100\%}{n} \sum_{i=1}^{n}\left(1 - \bigg| \frac{x_{i,true}-x_{i,pred}}{x_{i,true}} \bigg|\right)
+\begin{aligned}
+&\%RA = \frac{100\%}{n} \sum_{i=1}^{n}\left(1 - \bigg| \frac{x_{i,true}-x_{i,lin}}{x_{i,true}} \bigg|\right)
+\\
+\\
+&\text{where}
+\\
+&x_{i,true} \ \text{is the true x-axis value.}
+\\ 
+&x_{i,lin} \ \text{is the linear model predicted x-axis value.}
+\\ 
+&n \ \text{is the number of data points.}
+\end{aligned}
 $$ {#eq-pra}

### 2022-11-09 Manuscript/manuscript.qmd
Update the introduction to be more general.

@@
 
-Linearity assessment is one of the criteria used to evaluate the precision of a quantitative measurement procedure as seen in calibration studies from @rodríguez1993 and drug analysis from @needleman1990.
-In metabolomics/lipidomics analysis, dilution curves are plotted for each molecule measured from quality control sample, generated by pooling equal aliquots from each study sample.
-Molecules that exhibits a non-linear relationship are rejected before further statistical analysis, as their quantification in different sample groups might be compromised.
-Dilution curves are usually plotted using general-purpose software like Excel with their corresponding Pearson Correlation Coefficient value.
-A threshold value of 0.8 is used to balance the risk of accepting or removing non-linear signals related to relevant molecules.
+Linearity assessment, as summarised by @paulson1995, is a standard protocol to verify if an instrument or experimental method is in working condition, especially if the method is used to report quantitative results.
+It is applied in many fields in science such as calibration/dilution studies (@rodríguez1993 and @sands2021) and assay development (@ross2003 and @hsieh2008).
+During analysis, curves are plotted individually with a Pearson Correlation Coefficient value for each measurement using general-purpose software like Excel.
 
-However, @sonnergaard2006 warned that the Pearson Correlation Coefficient is not an effective standalone numeric parameter to estimate linearity.
+However, as instrument or experimental method are becoming more high throughput, many measurements can be done at a short time.
+Having the analyst to individually plot numerous curves to check for linearity is time-consuming.
+Furthermore, @sonnergaard2006 warns that the Pearson Correlation Coefficient is not an effective standalone numeric parameter to estimate linearity.
 While researchers have created other metrics for linearity evaluation, these metrics are rarely implemented in most general-purpose software.
-Furthermore, today's metabolomics/lipidomics workflow can measure hundreds of molecules.
-Having the analyst to individually plot numerous curves to check for linearity is time consuming.
 
-R package, *DCVtestkit* addresses these issues by assisting analysts, to plot dilution curves for many molecules easily with additional metrics, other than the Pearson Correlation Coefficient, that better describe the curve's shape.
-It also provides an interactive viewer for analysts to group, filter and sort the plots, allowing them to look at the relevant ones, such as the saturated dilution curves, and identify problematic molecules quickly.
+R package, *DCVtestkit* addresses these issues by assisting analysts, to plot curves from many experiments easily with additional metrics, other than the Pearson Correlation Coefficient, that better describe the curve's shape.
+It also provides an interactive viewer for analysts to group, filter and sort the plots, allowing them to look at problematic ones, such as saturated curves.
 
@@
 
-Supplementary Figure 1 depicts the workflow of *DCVtestkit*.
+Using the analysis of dilution curves in meatbolomic/lipidomic study as a running example, Supplementary Figure 1 depicts the workflow of *DCVtestkit*.
 The workflow starts with two tables: Transition Signal Data, containing transition signals (y-axis for dilution curve) for each sample and Dilution Annotation, containing dilution curve related information, such as concentration (x-axis for dilution curve) and dilution batches.
@@
 \end{aligned}
-$$ {#eq-mandel-test}
-Another one is Percent Residual Accuracy ($\%RA$ in @eq-pra) from @logue2018. Ranging from $-\infty$ to $100$, if the curve is linear, the value should be close to $100$.
+$$ {#eq-mandel-test} Another one is Percent Residual Accuracy ($\%RA$ in @eq-pra) from @logue2018. Ranging from $-\infty$ to $100$, if the curve is linear, the value should be close to $100$.
 
@@
 However, there are few software that can analyse dilution curves efficiently.
-R package, *DCVtestkit*, rectifies this by plotting of many dilution curves quickly by automation and reporting alternative statistics, other than the Pearson Correlation Coefficient, to better describe the shape of dilution curves.
+
+R package, *DCVtestkit*, rectifies this by plotting of many curves quickly by automation and reporting alternative statistics, other than the Pearson Correlation Coefficient, to better describe the shape of curves.
 It also provides an interactive trellis plot for exploratory data analysis.

### 2022-11-09 Manuscript/manuscript.qmd
Update the conclusion.

@@
 
-To verify if a quantitative analytical test method is reliable, it is important to check for linearity.
-A linear response in quality control dilution curves is required in metabolomics/lipidomics to assess the molecules' suitability for further analysis.
-However, there are few software that can analyse dilution curves efficiently.
-
+To verify if an instrument or experimental method is reliable, it is important to check for linearity.
+However, there are few software that can to do efficiently at a high throughput setting.
 R package, *DCVtestkit*, rectifies this by plotting of many curves quickly by automation and reporting alternative statistics, other than the Pearson Correlation Coefficient, to better describe the shape of curves.

### 2022-11-09 Manuscript/manuscript.qmd
Update the abstract.

@@
 
-Linearity assessment plays a significant role in the validation of quantitative analytical laboratory procedures.
-In metabolomic and lipidomic workflows, a linear response in dilution series generated from pooled quality control samples is used to assess the quality of the measurement of molecules measured before further analysis.
-Most of the currently used software only allow the analyst to repetitively plot, view and analyse the dilution curves one at a time, a tedious and time-consuming process.
-In addition, summary statistics of dilution curves are limited to the Pearson Correlation Coefficient which is insufficient to fully understand the shape of the dilution curves.
-*DCVtestkit* aims to provide additional summary statistics for dilution curves, taken from previous publications but which are not implemented in the current software tools.
-It also helps to reduce the analyst's workload by analysing many dilution curves automatically, reporting the statistical results in Excel and recording the dilution plots in a pdf file.
+Linearity assessment plays a significant role in the validation of instrumentation and experimental procedures.
+As technology progresses, many of these methods are becoming more high throughput, providing analysts with many measurements generated at a short time.
+Commonly used software, like Excel, only allow the analyst to repetitively plot, view and analyse the linearity of curves one at a time, a tedious and time-consuming process.
+In addition, summary statistics of these curves are limited to the Pearson Correlation Coefficient which is insufficient to fully understand the shape of the curves.
+*DCVtestkit* aims to provide additional summary statistics for assessing linearity of curves, taken from previous publications but which are not implemented in the current software tools.
+It also helps to reduce the analyst's workload by analysing many curves automatically, reporting the statistical results in Excel and recording the plots in a pdf file.
 In addition, it can also create an interactive trellis displayed as a HTML folder for more exploratory analysis.
@@
 To verify if an instrument or experimental method is reliable, it is important to check for linearity.
-However, there are few software that can to do efficiently at a high throughput setting.
+However, there are few software that can do this efficiently at a high throughput setting.
 R package, *DCVtestkit*, rectifies this by plotting of many curves quickly by automation and reporting alternative statistics, other than the Pearson Correlation Coefficient, to better describe the shape of curves.

### 2022-11-09 Manuscript/manuscript.qmd
Make the figure size bigger.

@@
 
-::: {#fig-overview layout="[[50,-50], [60,-40]]"}
+{{< pagebreak >}}
+
+::: {#fig-overview layout="[[60,-40], [70,-30]]"}
 ![Curve Grouping Workflow](images/README-LinearEvaluation.png){#fig-linearity}
 
-![Interactive Trellis Plots](images/README-TrellisOutput.png){#fig-visualisation}
+![Interactive Visualisation](images/README-TrellisOutput.png){#fig-visualisation}
 
@@
 :::
+
+{{< pagebreak >}}
 

### 2022-11-16 Manuscript/manuscript.qmd
change repository name to lancer_output

@@
 ---
-title: "*DCVtestkit*: a R package for linearity assessment and visualisation of multiple curves"
+title: "*lancer*: a R package for linearity assessment and visualisation of multiple curves"
 
@@
 In addition, summary statistics of these curves are limited to the Pearson Correlation Coefficient which is insufficient to fully understand the shape of the curves.
-*DCVtestkit* aims to provide additional summary statistics for assessing linearity of curves, taken from previous publications but which are not implemented in the current software tools.
+*lancer* aims to provide additional summary statistics for assessing linearity of curves, taken from previous publications but which are not implemented in the current software tools.
 It also helps to reduce the analyst's workload by analysing many curves automatically, reporting the statistical results in Excel and recording the plots in a pdf file.
@@
 
-*DCVtestkit* is available on GitHub <https://github.com/SLINGhub/DCVtestkit>. The documentation and tutorials can be accessed from <https://slinghub.github.io/DCVtestkit/>
+*lancer* is available on GitHub <https://github.com/SLINGhub/lancer>. The documentation and tutorials can be accessed from <https://slinghub.github.io/lancer/>
 
@@
 
-R package, *DCVtestkit* addresses these issues by assisting analysts, to plot curves from many experiments easily with additional metrics, other than the Pearson Correlation Coefficient, that better describe the curve's shape.
+R package, *lancer* addresses these issues by assisting analysts, to plot curves from many experiments easily with additional metrics, other than the Pearson Correlation Coefficient, that better describe the curve's shape.
 It also provides an interactive viewer for analysts to group, filter and sort the plots, allowing them to look at problematic ones, such as saturated curves.
@@
 
-Using the analysis of dilution curves in meatbolomic/lipidomic study as a running example, Supplementary Figure 1 depicts the workflow of *DCVtestkit*.
+Using the analysis of dilution curves in meatbolomic/lipidomic study as a running example, Supplementary Figure 1 depicts the workflow of *lancer*.
 The workflow starts with two tables: Transition Signal Data, containing transition signals (y-axis for dilution curve) for each sample and Dilution Annotation, containing dilution curve related information, such as concentration (x-axis for dilution curve) and dilution batches.
@@
 
-*DCVtestkit*'s curve grouping workflow in @fig-linearity and interactive visualisation of curves in @fig-visualisation.
+*lancer*'s curve grouping workflow in @fig-linearity and interactive visualisation of curves in @fig-visualisation.
 :::
@@
 While it identifies less linear curves correctly than the benchmark workflow, its score of `r inline_text(simulation_results, variable = wf2_group, level = "Good Linearity", column = "Linear")` is comparable.
-See <https://dcvtestkit-simulation.netlify.app> for report details.
+See <https://lancer-simulation.netlify.app> for report details.
 While the threshold values of Pearson Correlation Coefficient and Percent Residual Accuracy are based on the interpretation of @y.h.chan2003 and @logue2018, respectively, they remain subjective and arbitrary.
-Nevertheless, *DCVtestkit* allows optimization of these threshold values according to the analyst's determinants of linearity.
+Nevertheless, *lancer* allows optimization of these threshold values according to the analyst's determinants of linearity.
 
-Although *DCVtestkit* can export the results in Excel or pdf, they may be too complex for meaningful interpretation.
-@fig-visualisation shows a HTML folder, exported by *DCVtestkit*, such that clicking on the `index.html` file inside the folder will open an interactive trellis plots that analysts can be grouped, filtered and sorted.
+Although *lancer* can export the results in Excel or pdf, they may be too complex for meaningful interpretation.
+@fig-visualisation shows a HTML folder, exported by *lancer*, such that clicking on the `index.html` file inside the folder will open an interactive trellis plots that analysts can be grouped, filtered and sorted.
 This allows room for exploratory data analysis, such as identifying molecules with linearity issues or finding out the effects of changing the Pearson Correlation Coefficient threshold to another value.
 Such information is hard to achieve with the Excel and pdf files.
-An example of an interactive viewer created by *DCVtestkit* can be viewed at <https://dcvtestkit-interactive-example.netlify.app>
+An example of an interactive viewer created by *lancer* can be viewed at <https://lancer-interactive-example.netlify.app>
 
@@
 However, there are few software that can do this efficiently at a high throughput setting.
-R package, *DCVtestkit*, rectifies this by plotting of many curves quickly by automation and reporting alternative statistics, other than the Pearson Correlation Coefficient, to better describe the shape of curves.
+R package, *lancer*, rectifies this by plotting of many curves quickly by automation and reporting alternative statistics, other than the Pearson Correlation Coefficient, to better describe the shape of curves.
 It also provides an interactive trellis plot for exploratory data analysis.
-It is available on GitHub <https://github.com/SLINGhub/DCVtestkit> while the documentation and tutorials can be accessed from <https://slinghub.github.io/DCVtestkit>.
+It is available on GitHub <https://github.com/SLINGhub/lancer> while the documentation and tutorials can be accessed from <https://slinghub.github.io/lancer>.
 

### 2022-11-16 Manuscript/supplementary.qmd
Fixed equation alignment issue and changed title.
change repository name to lancer_output

@@
 ---
-title: "Supplementary for *DCVtestkit*: a R package for linearity assessment and analysis of quality control dilution curves"
+title: "Supplementary for *lancer*: a R package for linearity assessment and visualisation of multiple curves"
 
@@
 library(webshot2)
-library(DCVtestkit)
+library(lancer)
 ```
 
-![*DCVtestkit* Workflow](images/README-Workflow.png){#fig-DCVtestkit-Workflow}
+![*lancer* Workflow](images/README-Workflow.png){#fig-lancer-Workflow}
 
@@
 # Get dilution summary
-statistical_summary <- DCVtestkit::summarise_dilution_data(
+statistical_summary <- lancer::summarise_dilution_data(
   linear_data, 
@@
 
-table <- DCVtestkit::plot_summary_table(statistical_summary)
+table <- lancer::plot_summary_table(statistical_summary)
 
 # Model the data
-linear_model <- DCVtestkit::create_linear_model(linear_data, 
+linear_model <- lancer::create_linear_model(linear_data, 
                                                 "conc_var", "signal_var")
-quad_model <- DCVtestkit::create_quad_model(linear_data, 
+quad_model <- lancer::create_quad_model(linear_data, 
                                             "conc_var", "signal_var")
@@
 # Get dilution summary
-statistical_summary <- DCVtestkit::summarise_dilution_data(
+statistical_summary <- lancer::summarise_dilution_data(
   saturated_data, 
@@
 
-table <- DCVtestkit::plot_summary_table(statistical_summary)
+table <- lancer::plot_summary_table(statistical_summary)
 
 # Model the data
-linear_model <- DCVtestkit::create_linear_model(saturated_data, 
+linear_model <- lancer::create_linear_model(saturated_data, 
                                                 "conc_var", "signal_var")
-quad_model <- DCVtestkit::create_quad_model(saturated_data, 
+quad_model <- lancer::create_quad_model(saturated_data, 
                                             "conc_var", "signal_var")
@@
 # Get dilution summary
-statistical_summary <- DCVtestkit::summarise_dilution_data(
+statistical_summary <- lancer::summarise_dilution_data(
   lod_data, 
@@
 
-table <- DCVtestkit::plot_summary_table(statistical_summary)
+table <- lancer::plot_summary_table(statistical_summary)
 
 # Model the data
-linear_model <- DCVtestkit::create_linear_model(lod_data, 
+linear_model <- lancer::create_linear_model(lod_data, 
                                                 "conc_var", "signal_var")
-quad_model <- DCVtestkit::create_quad_model(lod_data, 
+quad_model <- lancer::create_quad_model(lod_data, 
                                             "conc_var", "signal_var")

### 2022-11-16 Quarto_Simulation/index.qmd
change repository name to lancer_output

@@
 library(deSolve)
-library(DCVtestkit)
+library(lancer)
 library(labelled)
@@
 saturation_dilution_summary <- 
-  DCVtestkit::summarise_dilution_table(
+  lancer::summarise_dilution_table(
     dilution_table = saturation_simulated_database,
@@
     signal_var = "y") |> 
-  DCVtestkit::evaluate_linearity(
+  lancer::evaluate_linearity(
     grouping_variable = c("ID")
@@
 lod_dilution_summary <- 
-  DCVtestkit::summarise_dilution_table(
+  lancer::summarise_dilution_table(
     dilution_table = lod_simulated_database,
@@
 linear_dilution_summary <-
-  DCVtestkit::summarise_dilution_table(
+  lancer::summarise_dilution_table(
     dilution_table = linear_simulated_database,
@@
 ```{r plots as pdf saturated}
-saturation_ggplot_table <- DCVtestkit::add_ggplot_panel(
+saturation_ggplot_table <- lancer::add_ggplot_panel(
   dilution_table = saturation_simulated_database,
@@
 
-DCVtestkit::view_ggplot_pdf(
+lancer::view_ggplot_pdf(
   ggplot_list = saturation_ggplot_list,
@@
 ```{r plots as pdf lod}
-lod_ggplot_table <- DCVtestkit::add_ggplot_panel(
+lod_ggplot_table <- lancer::add_ggplot_panel(
   dilution_table = lod_simulated_database,
@@
 
-DCVtestkit::view_ggplot_pdf(
+lancer::view_ggplot_pdf(
   ggplot_list = lod_ggplot_list,
@@
 ```{r plots as pdf linear}
-linear_ggplot_table <- DCVtestkit::add_ggplot_panel(
+linear_ggplot_table <- lancer::add_ggplot_panel(
   dilution_table = linear_simulated_database,
@@
 
-DCVtestkit::view_ggplot_pdf(
+lancer::view_ggplot_pdf(
   ggplot_list = linear_ggplot_list,
@@
 
-saturation_trellis_table <- DCVtestkit::add_plotly_panel(
+saturation_trellis_table <- lancer::add_plotly_panel(
   dilution_table = saturation_simulated_database,
@@
 ) |> 
-  DCVtestkit::convert_to_cog(
+  lancer::convert_to_cog(
     grouping_variable = "ID",
@@
 
-DCVtestkit::view_trellis_html(
+lancer::view_trellis_html(
   trellis_table = saturation_trellis_table,
@@
 
-lod_trellis_table <- DCVtestkit::add_plotly_panel(
+lod_trellis_table <- lancer::add_plotly_panel(
   dilution_table = lod_simulated_database,
@@
 
-DCVtestkit::view_trellis_html(
+lancer::view_trellis_html(
   trellis_table = lod_trellis_table,
@@
 
-linear_trellis_table <- DCVtestkit::add_plotly_panel(
+linear_trellis_table <- lancer::add_plotly_panel(
   dilution_table = linear_simulated_database,
@@
 
-DCVtestkit::view_trellis_html(
+lancer::view_trellis_html(
   trellis_table = linear_trellis_table,

### 2022-11-16 README.qmd
Update the manuscript.
change repository name to lancer_output

--- 2022-10-10 README.qmd
@@
 ---
-title: "DCVtestkit Output Examples"
+title: "`lancer` Output Examples"
 format: gfm
@@
 
-Here is where I store some output example of the R package [`DCVtestkit`](https://github.com/SLINGhub/DCVtestkit)
+Here is where I store some output example of the R package [`lancer`](https://github.com/SLINGhub/lancer)
 
@@
 
-[`dilution_summary.xlsx`] is the output in Excel.
+[`dilution_summary.xlsx`](https://raw.githubusercontent.com/JauntyJJS/lancer_output/main/dilution_summary.xlsx) is the output in Excel.
 
@@
 
-[`dilution_plot.xlsx`] is the output in pdf.
+[`dilution_plot.pdf`](https://raw.githubusercontent.com/JauntyJJS/lancer_output/main/dilution_plot.pdf) is the output in pdf.
 
@@
 
-https://dcvtestkit-interactive-example.netlify.app is the output as an interactive trellis plot from the `Dilution_Plot_Folder` when the `index.html` file is clicked.
+https://lancer-interactive-example.netlify.app is the output as an interactive trellis plot from the `Dilution_Plot_Folder` when the `index.html` file is clicked.
 
@@
 
-https://dcvtestkit-quarto-example.netlify.app is the output of a html file generated using [Quarto](https://quarto.org/)
+https://lancer-quarto-example.netlify.app is the output of a html file generated using [Quarto](https://quarto.org/)
+
+## Simulation Report
+
+https://lancer-simulation.netlify.app is the report of a simulation experiment done in the paper.

### 2022-11-16 Quarto_Simulation/index.qmd
Add Quarto version

@@
 #| code-fold: true
+
+# Taken from https://github.com/r-lib/sessioninfo/issues/75
+get_quarto_version <- function() {
+  if (isNamespaceLoaded("quarto")) {
+    path <- quarto::quarto_path()
+    ver <- system("quarto -V", intern = TRUE)
+    if (is.null(path)) {
+      "NA (via quarto)"
+    } else {
+      paste0(ver, " @ ", path, "/ (via quarto)")
+    }
+  } else {
+    path <- Sys.which("quarto")
+    if (path == "") {
+      "NA"
+    } else {
+      ver <- system("quarto -V", intern = TRUE)
+      paste0(ver, " @ ", path)
+    }
+  }
+}
+
 r_platform_table <- sessioninfo::platform_info()
+r_platform_table[["quarto"]] <- get_quarto_version()[1]
 

### 2023-01-04 README.qmd
Fix typo.
Replace dilution with curve in Quarto Example folder.

@@
 
-Here is where I store some output example of the R package [`lancer`](https://github.com/SLINGhub/lancer)
+Here is where I store some output example of the R package [`lancer`](https://github.com/SLINGhub/lancer).
 
@@
 
-[`dilution_summary.xlsx`](https://raw.githubusercontent.com/JauntyJJS/lancer_output/main/dilution_summary.xlsx) is the output in Excel.
+[`curve_summary.xlsx`](https://raw.githubusercontent.com/JauntyJJS/lancer_output/main/curve_summary.xlsx) is the output in Excel.
 
@@
 
-[`dilution_plot.pdf`](https://raw.githubusercontent.com/JauntyJJS/lancer_output/main/dilution_plot.pdf) is the output in pdf.
+[`curve_plot.pdf`](https://raw.githubusercontent.com/JauntyJJS/lancer_output/main/curve_plot.pdf) is the output in pdf.
 
@@
 
-https://lancer-interactive-example.netlify.app is the output as an interactive trellis plot from the `Dilution_Plot_Folder` when the `index.html` file is clicked.
+https://lancer-interactive-example.netlify.app is the output as an interactive trellis plot from the `Curve_Plot_Folder` when the `index.html` file is clicked.
 

### 2023-01-04 Quarto_Simulation/index.qmd
Replace dilution with curve in index.qmd in Quarto Simulation

@@
 
-## Saturated Curve
+## Saturation Regime Curve
 
-```{r Saturation Many Data}
+```{r Saturation Regime Curve Simulation Functions}
 
-simulate_saturation <- function(id) {
+simulate_saturation_regime <- function(id) {
 
@@
 
-  saturation_simulation <- tibble::tibble(
+  saturation_regime_simulation <- tibble::tibble(
     x = mono_model$time,
@@
 
-  return(saturation_simulation)
+  return(saturation_regime_simulation)
 
@@
 
-## Limit of Detection Curve
+## Noise Regime Curve
 
-```{r LOD Many Data}
+```{r Noise Regime Curve Simulation Functions}
 
-simulate_lod <- function(id) {
+simulate_noise_regime <- function(id) {
 
@@
 
-  lod_simulation <- tibble::tibble(
+  noise_regime_simulation <- tibble::tibble(
     x = exp_model$time,
@@
 
-  return(lod_simulation)
+  return(noise_regime_simulation)
 
@@
 
-```{r Linear Many Data}
+```{r Linear Curve Simulation Functions}
 
 #diffeq model as function
-model.constant = function(times, y, parms) {
+model_constant = function(times, y, parms) {
   ## times = current times
@@
     parms <- c(a = r[k])
-    ode_logi <- deSolve::ode(InitCond, steps, model.constant, parms)
+    ode_logi <- deSolve::ode(InitCond, steps, model_constant, parms)
     y[k + 1] <- ode_logi[length(ode_logi[, 2]), 2]
@@
 
-We simulate $200$ curves (saturated, limit of detection and linear) using $7$ points from $0$ to $200$ on the x-axis. A unique id is added for each simulated data.
+We simulate $200$ curves (saturation regime, noise regime and linear) using $7$ points from $0$ to $200$ on the x-axis. A unique id is added for each simulated data.
 
@@
 
-## Saturated Curve
+## Saturation Regime Curve
 
-```{r Create Simulated Data Saturated}
+```{r Create Simulated Data Saturation Regime}
 
-nested_saturation_simulated_database <-
+nested_saturation_regime_simulated_database <-
   tibble::tibble(
-    ID = paste("Saturation", 
+    ID = paste("Saturation Regime", 
                stringr::str_pad(1:200, width = 3, pad = "0")),
-    `Dilution Batch Name` = "Saturation"
+    `Curve Batch Name` = "Saturation Regime"
 
@@
   dplyr::mutate(
-    dilution_data = purrr::map(
+    curve_data = purrr::map(
       .x = .data$ID,
-      .f = simulate_saturation
+      .f = simulate_saturation_regime
       )
@@
 
-## Limit of Detection Curve
+## Noise Regime Curve
 
-```{r Create Simulated Data LOD}
+```{r Create Simulated Data Noise Regime}
 
-nested_lod_simulated_database <-
+nested_noise_regime_simulated_database <-
   tibble::tibble(
-    ID = paste("Limit Of Detection", 
+    ID = paste("Noise Regime", 
                stringr::str_pad(1:200, width = 3, pad = "0")),
-    `Dilution Batch Name` = "Limit Of Detection"
+    `Curve Batch Name` = "Noise Regime"
 
@@
   dplyr::mutate(
-    dilution_data = purrr::map(
+    curve_data = purrr::map(
       .x = .data$ID,
-      .f = simulate_lod
+      .f = simulate_noise_regime
       )
@@
                stringr::str_pad(1:200, width = 3, pad = "0")),
-    `Dilution Batch Name` = "Linear"
+    `Curve Batch Name` = "Linear"
 
@@
   dplyr::mutate(
-    dilution_data = purrr::map(
+    curve_data = purrr::map(
       .x = .data$ID,
@@
 
-# Unnest Simulated Data
+# Unnest Simulated Curve Data
 
-While nested dilution (having a column of data frames) is easier to view with a human eye, it can be hard to be read and processed by a computer.
+While nested curve data (having a column of data frames) is easier to view with a human eye, it can be hard to be read and processed by a computer.
 We need flattened the data frames back into columns.
 To do this, we use [`tidyr::unnest`](https://tidyr.tidyverse.org/reference/nest.html)
+## Saturation Regime Curve
 
-## Saturated Curve
-
-```{r Nest Simulated Data Saturated}
-saturation_simulated_database <-
-  nested_saturation_simulated_database |> 
-  tidyr::unnest("dilution_data")
+```{r Nest Simulated Data Saturation Regime}
+saturation_regime_simulated_database <-
+  nested_saturation_regime_simulated_database |> 
+  tidyr::unnest("curve_data")
 ```
 
-## Limit of Detection Curve
+## Noise Regime Curve
 
-```{r Nest Simulated Data LOD}
-lod_simulated_database <-
-  nested_lod_simulated_database |> 
-  tidyr::unnest("dilution_data")
+```{r Nest Simulated Data Noise Regime}
+noise_regime_simulated_database <-
+  nested_noise_regime_simulated_database |> 
+  tidyr::unnest("curve_data")
 ```
@@
   nested_linear_simulated_database |> 
-  tidyr::unnest("dilution_data")
+  tidyr::unnest("curve_data")
 ```
@@
 
-## Saturated Curve
+## Saturation Regime Curve
 
 ```{r Save Simulated Data Saturated}
-saveRDS(saturation_simulated_database, 
-        file = "saturation_simulated_database.rds")
+saveRDS(saturation_regime_simulated_database, 
+        file = "saturation_regime_simulated_database.rds")
 
-write.csv(x = saturation_simulated_database,
-          file = "saturation_simulated_database.csv", 
+write.csv(x = saturation_regime_simulated_database,
+          file = "saturation_regime_simulated_database.csv", 
           row.names = FALSE)
@@
 
-## Limit of Detection Curve
+## Noise Regime Curve
 
-```{r Save Simulated Data LOD}
-saveRDS(lod_simulated_database, 
-        file = "lod_simulated_database.rds")
+```{r Save Simulated Data Noise Regime}
+saveRDS(noise_regime_simulated_database, 
+        file = "noise_regime_simulated_database.rds")
 
-write.csv(x = saturation_simulated_database,
-          file = "lod_simulated_database.csv", 
+write.csv(x = noise_regime_simulated_database,
+          file = "noise_regime_simulated_database.csv", 
           row.names = FALSE)
@@
 
-We now calculate the statistical summary for each dilution curve. In addition, we export statistical summary as a csv and rds files.
+We now calculate the statistical summary for each curve. In addition, we export statistical summary as a csv and rds files.
 
@@
 
-## Saturated Curve
+## Saturation Regime Curve
 
-```{r dilution statistical summary saturated}
+```{r curve statistical summary saturation regime}
 #| message: false
-saturation_dilution_summary <- 
-  lancer::summarise_dilution_table(
-    dilution_table = saturation_simulated_database,
+saturation_regime_curve_summary <- 
+  lancer::summarise_curve_table(
+    curve_table = saturation_regime_simulated_database,
     grouping_variable = c("ID"),
@@
 
-```{r save dilution statistical summary saturated}
-saveRDS(saturation_dilution_summary, 
-        file = "saturation_dilution_summary.rds")
+```{r save curve statistical summary saturation regime}
+saveRDS(saturation_regime_curve_summary, 
+        file = "saturation_regime_curve_summary.rds")
 
-write.csv(x = saturation_dilution_summary,
-          file = "saturation_dilution_summary.csv", 
+write.csv(x = saturation_regime_curve_summary,
+          file = "saturation_regime_curve_summary.csv", 
           row.names = FALSE)
@@
 
-## Limit of Detection Curve
+## Noise Regime Curve
 
-```{r dilution statistical summary lod}
+```{r curve statistical summary noise regime}
 #| message: false
-lod_dilution_summary <- 
-  lancer::summarise_dilution_table(
-    dilution_table = lod_simulated_database,
+noise_regime_curve_summary <- 
+  lancer::summarise_curve_table(
+    curve_table = noise_regime_simulated_database,
     grouping_variable = c("ID"),
@@
 
-```{r save dilution statistical summary lod}
-saveRDS(lod_dilution_summary, 
-        file = "lod_dilution_summary.rds")
+```{r save curve statistical summary lod}
+saveRDS(noise_regime_curve_summary, 
+        file = "noise_regime_curve_summary.rds")
 
-write.csv(x = lod_dilution_summary,
-          file = "lod_dilution_summary.csv", 
+write.csv(x = noise_regime_curve_summary,
+          file = "noise_regime_curve_summary.csv", 
           row.names = FALSE)
@@
 
-```{r dilution statistical summary linear}
+```{r curve statistical summary linear}
 #| message: false
-linear_dilution_summary <-
-  lancer::summarise_dilution_table(
-    dilution_table = linear_simulated_database,
+linear_curve_summary <-
+  lancer::summarise_curve_table(
+    curve_table = linear_simulated_database,
     grouping_variable = c("ID"),
@@
 
-```{r save dilution statistical summary linear}
-saveRDS(linear_dilution_summary, 
-        file = "linear_dilution_summary.rds")
+```{r save curve statistical summary linear}
+saveRDS(linear_curve_summary, 
+        file = "linear_curve_summary.rds")
 
-write.csv(x = linear_dilution_summary,
-          file = "linear_dilution_summary.csv", 
+write.csv(x = linear_curve_summary,
+          file = "linear_curve_summary.csv", 
           row.names = FALSE)
@@
 
-## Saturated Curve
+## Saturation Regime Curve
 
-```{r Print Simulated Data Saturated}
+```{r Print Simulated Data Saturation Regime}
 #| layout-ncol: 1
 
-nested_saturation_simulated_database |> 
+nested_saturation_regime_simulated_database |> 
   reactable::reactable(
@@
         minWidth = 200),
-      dilution_data = reactable::colDef(
+      curve_data = reactable::colDef(
         details = function(index) {
-          filtered_data <- nested_saturation_simulated_database[["dilution_data"]][index][[1]]
+          filtered_data <- nested_saturation_regime_simulated_database[["curve_data"]][index][[1]]
           htmltools::div(style = "padding: 1rem",
@@
 
-saturation_dilution_summary |> 
+saturation_regime_curve_summary |> 
   reactable::reactable(
@@
 
-## Limit of Detection Curve
+## Noise Regime Curve
 
-```{r Print Simulated Data LOD}
+```{r Print Simulated Data Noise Regime}
 #| layout-ncol: 1
 
-nested_lod_simulated_database |> 
+nested_noise_regime_simulated_database |> 
   reactable::reactable(
@@
         minWidth = 200),
-      dilution_data = reactable::colDef(
+      curve_data = reactable::colDef(
         details = function(index) {
-          filtered_data <- nested_lod_simulated_database[["dilution_data"]][index][[1]]
+          filtered_data <- nested_noise_regime_simulated_database[["curve_data"]][index][[1]]
           htmltools::div(style = "padding: 1rem",
@@
 
-lod_dilution_summary |> 
+noise_regime_curve_summary |> 
   reactable::reactable(
@@
         minWidth = 200),  
-      dilution_data = reactable::colDef(
+      curve_data = reactable::colDef(
         details = function(index) {
-          filtered_data <- nested_linear_simulated_database[["dilution_data"]][index][[1]]
+          filtered_data <- nested_linear_simulated_database[["curve_data"]][index][[1]]
           htmltools::div(style = "padding: 1rem",
@@
 
-linear_dilution_summary |> 
+linear_curve_summary |> 
   reactable::reactable(
@@
 
-saturation_dilution_summary <- saturation_dilution_summary |> 
-  dplyr::mutate(curve_group = "Saturated")
+saturation_regime_curve_summary <- 
+  saturation_regime_curve_summary |> 
+  dplyr::mutate(curve_group = "Saturation Regime")
 
-lod_dilution_summary <- lod_dilution_summary |> 
-  dplyr::mutate(curve_group = "Limit of Detection")
+noise_regime_curve_summary <- noise_regime_curve_summary |> 
+  dplyr::mutate(curve_group = "Noise Regime")
 
-linear_dilution_summary <- linear_dilution_summary |> 
-  dplyr::mutate(curve_group = "Linear")
+linear_curve_summary <- linear_curve_summary |> 
+  dplyr::mutate(curve_group = "Good Linearity")
 
-combined_dilution_summary <-
+combined_curve_summary <-
   dplyr::bind_rows(
-    saturation_dilution_summary,
-    lod_dilution_summary,
-    linear_dilution_summary
+    saturation_regime_curve_summary,
+    noise_regime_curve_summary,
+    linear_curve_summary
   ) 
@@
 
-combined_dilution_summary <- 
-  combined_dilution_summary |> 
+combined_curve_summary <- 
+  combined_curve_summary |> 
   dplyr::mutate(
     curve_group = factor(.data$curve_group,
-                         levels = c("Linear",
-                                    "Saturated",
-                                    "Limit of Detection")),
+                         levels = c("Good Linearity",
+                                    "Saturation Regime",
+                                    "Noise Regime")),
     pearson_group = dplyr::case_when(
@@
     ),
-    wf2_group = stringr::str_replace(
-      string = .data$wf2_group,
-      pattern = "LOD",
-      replacement = "Limit of Detection"
-    ),
+    # wf2_group = stringr::str_replace(
+    #   string = .data$wf2_group,
+    #   pattern = "Noise Regime",
+    #   replacement = "Noise Regime"
+    # ),
     wf2_group = factor(.data$wf2_group,
                        levels = c("Good Linearity",
-                                    "Saturation",
-                                    "Limit of Detection",
+                                  "Saturation Regime",
+                                  "Noise Regime",
                                   "Poor Linearity"))
@@
 #| column: screen-inset-right
-simulation_results <- combined_dilution_summary |> 
+simulation_results <- combined_curve_summary |> 
   dplyr::select(c("curve_group", "wf2_group", 
@@
   ) |> 
-  modify_header(
-    all_stat_cols() ~ "**{level}**\nN = {n}"
+  gtsummary::modify_header(
+    gtsummary::all_stat_cols() ~ "**{level}**\nN = {n}"
     ) |> 
   gtsummary::modify_spanning_header(
-    all_stat_cols() ~ "**Simulated Curve Type**"
+    gtsummary::all_stat_cols() ~ "**Simulated Curve Type**"
     )
@@
 Results showed that Workflow $2$ is able to identify the saturated and limit of detection curves better than the benchmark workflow.
-On the other hand, while Workflow $2$ is able to identify less linear curves than the benchmark workflow, it gives a comparable score of `r inline_text(simulation_results, variable = wf2_group, level = "Good Linearity", column = "Linear")`
+On the other hand, while Workflow $2$ is able to identify less linear curves than the benchmark workflow, it gives a comparable score of `r inline_text(simulation_results, variable = wf2_group, level = "Good Linearity", column = "Good Linearity")`
 
@@
 
-## Saturated Curve
+## Saturation Regime Curve
 
-```{r plots as pdf saturated}
-saturation_ggplot_table <- lancer::add_ggplot_panel(
-  dilution_table = saturation_simulated_database,
-  dilution_summary = saturation_dilution_summary,
+```{r plots as pdf saturation regime}
+saturation_regime_ggplot_table <- lancer::add_ggplot_panel(
+  curve_table = saturation_regime_simulated_database,
+  curve_summary = saturation_regime_curve_summary,
   grouping_variable = c("ID"),
-  dil_batch_var = "Dilution Batch Name",
+  curve_batch_var = "Curve Batch Name",
   conc_var = "x",
@@
 
-saturation_ggplot_list <- saturation_ggplot_table$panel
+saturation_regime_ggplot_list <-
+  saturation_regime_ggplot_table$panel
 
 lancer::view_ggplot_pdf(
-  ggplot_list = saturation_ggplot_list,
-  filename = "dilution_plot_saturated.pdf",
+  ggplot_list = saturation_regime_ggplot_list,
+  filename = "curve_plot_saturation_regime.pdf",
   ncol_per_page = 2,
@@
 
-## Limit of Detection Curve
+## Noise Regime Curve
 
-```{r plots as pdf lod}
-lod_ggplot_table <- lancer::add_ggplot_panel(
-  dilution_table = lod_simulated_database,
-  dilution_summary = lod_dilution_summary,
+```{r plots as pdf noise regime}
+noise_regime_ggplot_table <- lancer::add_ggplot_panel(
+  curve_table = noise_regime_simulated_database,
+  curve_summary = noise_regime_curve_summary,
   grouping_variable = c("ID"),
-  dil_batch_var = "Dilution Batch Name",
+  curve_batch_var = "Curve Batch Name",
   conc_var = "x",
@@
 
-lod_ggplot_list <- lod_ggplot_table$panel
+noise_regime_ggplot_list <- noise_regime_ggplot_table$panel
 
 lancer::view_ggplot_pdf(
-  ggplot_list = lod_ggplot_list,
-  filename = "dilution_plot_lod.pdf",
+  ggplot_list = noise_regime_ggplot_list,
+  filename = "curve_plot_noise_regime.pdf",
   ncol_per_page = 2,
@@
 linear_ggplot_table <- lancer::add_ggplot_panel(
-  dilution_table = linear_simulated_database,
-  dilution_summary = linear_dilution_summary,
+  curve_table = linear_simulated_database,
+  curve_summary = linear_curve_summary,
   grouping_variable = c("ID"),
-  dil_batch_var = "Dilution Batch Name",
+  curve_batch_var = "Curve Batch Name",
   conc_var = "x",
@@
   ggplot_list = linear_ggplot_list,
-  filename = "dilution_plot_linear.pdf",
+  filename = "curve_plot_linear.pdf",
   ncol_per_page = 2,
@@
 
-## Saturated Curve
+## Saturation Regime Curve
 
-```{r plots as trellis saturated}
+```{r plots as trellis saturation regime}
 #| column: screen-inset-right
 
-saturation_trellis_table <- lancer::add_plotly_panel(
-  dilution_table = saturation_simulated_database,
-  dilution_summary = saturation_dilution_summary,
+saturation_regime_trellis_table <- lancer::add_plotly_panel(
+  curve_table = saturation_regime_simulated_database,
+  curve_summary = saturation_regime_curve_summary,
   grouping_variable = c("ID"),
   sample_name_var = "Sample Name",
-  dil_batch_var = "Dilution Batch Name",
-  dil_batch_col = c(
+  curve_batch_var = "Curve Batch Name",
+  curve_batch_col = c(
     "#377eb8"),
@@
 lancer::view_trellis_html(
-  trellis_table = saturation_trellis_table,
+  trellis_table = saturation_regime_trellis_table,
   grouping_variable = c("ID"),
-  trellis_report_name = "Dilution_Plot_Saturated",
-  trellis_report_folder = "Dilution_Saturated_Folder",
+  trellis_report_name = "Curve_Plot_Saturation_Regime",
+  trellis_report_folder = "Curve_Saturation_Regime_Folder",
   panel_variable = "panel"
@@
 
-## Limit of Detection Curve
+## Noise Regime Curve
 
@@
 
-lod_trellis_table <- lancer::add_plotly_panel(
-  dilution_table = lod_simulated_database,
-  dilution_summary = lod_dilution_summary,
+noise_regime_trellis_table <- lancer::add_plotly_panel(
+  curve_table = noise_regime_simulated_database,
+  curve_summary = noise_regime_curve_summary,
   grouping_variable = c("ID"),
   sample_name_var = "Sample Name",
-  dil_batch_var = "Dilution Batch Name",
-  dil_batch_col = c(
+  curve_batch_var = "Curve Batch Name",
+  curve_batch_col = c(
     "#377eb8"),
@@
 lancer::view_trellis_html(
-  trellis_table = lod_trellis_table,
+  trellis_table = noise_regime_trellis_table,
   grouping_variable = c("ID"),
-  trellis_report_name = "Dilution_Plot_LOD",
-  trellis_report_folder = "Dilution_LOD_Folder",
+  trellis_report_name = "Curve_Plot_Noise_Regime",
+  trellis_report_folder = "Curve_Noise_Regime_Folder",
   panel_variable = "panel"
@@
 linear_trellis_table <- lancer::add_plotly_panel(
-  dilution_table = linear_simulated_database,
-  dilution_summary = linear_dilution_summary,
+  curve_table = linear_simulated_database,
+  curve_summary = linear_curve_summary,
   grouping_variable = c("ID"),
   sample_name_var = "Sample Name",
-  dil_batch_var = "Dilution Batch Name",
-  dil_batch_col = c(
+  curve_batch_var = "Curve Batch Name",
+  curve_batch_col = c(
     "#377eb8"),
@@
   grouping_variable = c("ID"),
-  trellis_report_name = "Dilution_Plot_Linear",
-  trellis_report_folder = "Dilution_Linear_Folder",
+  trellis_report_name = "Curve_Plot_Linear",
+  trellis_report_folder = "Curve_Linear_Folder",
   panel_variable = "panel"

### 2023-01-04 Manuscript/supplementary.qmd
Update Quarto Example.

@@
 
-saturated_data <- data.frame(
+saturation_regime_data <- data.frame(
   conc_var = c(10, 25, 40, 50, 60,
@@
 
-lod_data <- data.frame(
+noise_regime_data <- data.frame(
   conc_var = c(10, 25, 40, 50, 60,
@@
                     75, 80, 100, 125, 150), 
-  `Linear signal` = c(25463, 63387, 90624, 131274, 138069,
+  `Linear Curve` = c(25463, 63387, 90624, 131274, 138069,
                      205353, 202407, 260205, 292257, 367924),
-  `Saturated signal` = c(5192648, 16594991, 32507833, 46499896,
+  `Saturation Regime Curve` = c(5192648, 16594991, 32507833, 46499896,
                                 55388856, 62505210, 62778078, 72158161,
                                 78044338, 86158414), 
-  `LOD signal` = c(500, 903, 1267, 2031, 2100,
+  `Noise Regime Curve` = c(500, 903, 1267, 2031, 2100,
                            3563, 4500, 5300, 8500, 10430)
@@
 
-# Get dilution summary
-statistical_summary <- lancer::summarise_dilution_data(
+# Get curve summary
+statistical_summary <- lancer::summarise_curve_data(
   linear_data, 
@@
 linear_model <- lancer::create_linear_model(linear_data, 
-                                                "conc_var", "signal_var")
+                                            "conc_var", 
+                                            "signal_var")
+
 quad_model <- lancer::create_quad_model(linear_data, 
-                                            "conc_var", "signal_var")
+                                        "conc_var", 
+                                        "signal_var")
 
-dilution <- seq(min(linear_data$conc_var, na.rm = TRUE),
+curve <- seq(min(linear_data$conc_var, na.rm = TRUE),
              max(linear_data$conc_var, na.rm = TRUE),
@@
 y_lin_predict <- stats::predict(linear_model,
-                                tibble::tibble("conc_var" := dilution))
+                                tibble::tibble("conc_var" := curve))
+
 y_quad_predict <- stats::predict(quad_model,
-                                 tibble::tibble("conc_var" := dilution))
+                                 tibble::tibble("conc_var" := curve))
 reg_data <- data.frame(
-  dilution = dilution,
+  curve = curve,
   y_lin_predict = y_lin_predict,
@@
   ggplot2::geom_line(data = reg_data,
-                           mapping = ggplot2::aes(x = dilution, y=y_lin_predict,
-                                                  colour = "Lin")
-        ) +
+                     mapping = ggplot2::aes(x = curve, 
+                                            y = y_lin_predict,
+                                            colour = "Lin")) +
   ggplot2::geom_line(data = reg_data,
-                     mapping = ggplot2::aes(x = dilution, y=y_quad_predict,
-                                            colour = "Quad")
-  ) +
+                     mapping = ggplot2::aes(x = curve, 
+                                            y = y_quad_predict,
+                                            colour = "Quad")) +
   ggplot2::scale_colour_manual(values = c(reg_col_vec),
@@
                                  colour = c(reg_col_vec)
-                               ))
-    ) +
+                               ))) +
   ggplot2::theme(
@@
   ) +
-  ggplot2::labs(title = "Linear",
+  ggplot2::labs(title = "Linear Curve",
                 x = "Concentration",
@@
 
-```{r create saturation plot}
+```{r create saturation regime plot}
 #| echo: false
 
-# Get dilution summary
-statistical_summary <- lancer::summarise_dilution_data(
-  saturated_data, 
+# Get curve summary
+statistical_summary <- lancer::summarise_curve_data(
+  saturation_regime_data, 
   "conc_var", 
@@
 # Model the data
-linear_model <- lancer::create_linear_model(saturated_data, 
-                                                "conc_var", "signal_var")
-quad_model <- lancer::create_quad_model(saturated_data, 
-                                            "conc_var", "signal_var")
+linear_model <- lancer::create_linear_model(saturation_regime_data, 
+                                            "conc_var", 
+                                            "signal_var")
 
-dilution <- seq(min(saturated_data$conc_var, na.rm = TRUE),
-                max(saturated_data$conc_var, na.rm = TRUE),
+quad_model <- lancer::create_quad_model(saturation_regime_data, 
+                                        "conc_var", 
+                                        "signal_var")
+
+curve <- seq(min(saturation_regime_data$conc_var, na.rm = TRUE),
+             max(saturation_regime_data$conc_var, na.rm = TRUE),
              length.out = 15)
@@
 
-saturation_plot <- ggplot2::ggplot(saturated_data) +
+saturation_regime_plot <- ggplot2::ggplot(saturation_regime_data) +
   ggplot2::aes(x = .data$conc_var,
-               y = .data$signal_var
-               ) +
+               y = .data$signal_var) +
     ggplot2::geom_point(size = 5, colour = "#377eb8") +
   ggplot2::geom_line(data = reg_data,
-                           mapping = ggplot2::aes(x = dilution, y=y_lin_predict,
-                                                  colour = "Lin")
-        ) +
+                     mapping = ggplot2::aes(x = curve, 
+                                            y = y_lin_predict,
+                                            colour = "Lin")) +
   ggplot2::geom_line(data = reg_data,
-                     mapping = ggplot2::aes(x = dilution, y=y_quad_predict,
-                                            colour = "Quad")
-  ) +
+                     mapping = ggplot2::aes(x = curve, 
+                                            y = y_quad_predict,
+                                            colour = "Quad")) +
   ggplot2::scale_colour_manual(values = c(reg_col_vec),
@@
   ) +
-  ggplot2::labs(title = "Saturation",
+  ggplot2::labs(title = "Saturation Regime Curve",
                 x = "Concentration",
@@
 
-saturation_plot <- patchwork::wrap_plots(saturation_plot, table, ncol = 2, nrow = 1)
+saturation_regime_plot <- patchwork::wrap_plots(saturation_regime_plot, 
+                                                table, 
+                                                ncol = 2, 
+                                                nrow = 1)
 ```
 
-```{r create lod plot}
+```{r create noise regime plot}
 #| echo: false
 
-# Get dilution summary
-statistical_summary <- lancer::summarise_dilution_data(
-  lod_data, 
+# Get curve summary
+statistical_summary <- lancer::summarise_curve_data(
+  noise_regime_data, 
   "conc_var", 
@@
 # Model the data
-linear_model <- lancer::create_linear_model(lod_data, 
-                                                "conc_var", "signal_var")
-quad_model <- lancer::create_quad_model(lod_data, 
-                                            "conc_var", "signal_var")
+linear_model <- lancer::create_linear_model(noise_regime_data, 
+                                            "conc_var", 
+                                            "signal_var")
 
-dilution <- seq(min(lod_data$conc_var, na.rm = TRUE),
-                max(lod_data$conc_var, na.rm = TRUE),
+quad_model <- lancer::create_quad_model(noise_regime_data, 
+                                        "conc_var", 
+                                        "signal_var")
+
+curve <- seq(min(noise_regime_data$conc_var, na.rm = TRUE),
+             max(noise_regime_data$conc_var, na.rm = TRUE),
              length.out = 15)
@@
 
-lod_plot <- ggplot2::ggplot(lod_data) +
+noise_regime_plot <- ggplot2::ggplot(noise_regime_data) +
   ggplot2::aes(x = .data$conc_var,
-               y = .data$signal_var
-               ) +
+               y = .data$signal_var) +
   ggplot2::geom_point(size = 5, colour = "#4daf4a") +
   ggplot2::geom_line(data = reg_data,
-                           mapping = ggplot2::aes(x = dilution, y=y_lin_predict,
-                                                  colour = "Lin")
-        ) +
+                     mapping = ggplot2::aes(x = curve, 
+                                            y = y_lin_predict,
+                                            colour = "Lin")) +
   ggplot2::geom_line(data = reg_data,
-                     mapping = ggplot2::aes(x = dilution, y=y_quad_predict,
-                                            colour = "Quad")
-  ) +
+                     mapping = ggplot2::aes(x = curve, 
+                                            y = y_quad_predict,
+                                            colour = "Quad")) +
   ggplot2::scale_colour_manual(values = c(reg_col_vec),
@@
     axis.title.y = ggplot2::element_text(angle = 0,
-                                         vjust = 1)
-  ) +
-  ggplot2::labs(title = "LOD",
+                                         vjust = 1)) +
+  ggplot2::labs(title = "Noise Regime Curve",
                 x = "Concentration",
@@
 
-lod_plot <- patchwork::wrap_plots(lod_plot, table, ncol = 2, nrow = 1)
+noise_regime_plot <- patchwork::wrap_plots(noise_regime_plot, 
+                                           table, 
+                                           ncol = 2, 
+                                           nrow = 1)
 ```
@@
 #| label: fig-motivation
-#| fig-cap: "Plots and statistical results of three curves: Linear curve, Saturated curve and a curve with Limit Of Detection (LOD)."
-#| fig-height: 9
-#| fig-width: 13
+#| fig-cap: "Plots and statistical results of three curves: Linear Curve, Saturation Regime Curve and Noise Regime Curve."
+#| fig-height: 10
+#| fig-width: 14
 
@@
   linear_plot, 
-  saturation_plot, 
-  lod_plot, 
+  saturation_regime_plot, 
+  noise_regime_plot, 
   ncol = 2, 
@@
 #| echo: false
-saturation_dilution_summary <-
+saturation_regime_curve_summary <-
   readRDS(file = here::here(
     "Quarto_Simulation",
-    "saturation_dilution_summary.rds")
+    "saturation_regime_curve_summary.rds")
 )
 
-lod_dilution_summary <-
+noise_regime_curve_summary <-
   readRDS(file = here::here(
     "Quarto_Simulation",
-    "lod_dilution_summary.rds")
+    "noise_regime_curve_summary.rds")
 )
 
-linear_dilution_summary <-
+linear_curve_summary <-
   readRDS(file = here::here(
     "Quarto_Simulation",
-    "linear_dilution_summary.rds")
+    "linear_curve_summary.rds")
 )
@@
 #| echo: false
-saturation_dilution_summary <- saturation_dilution_summary |> 
-  dplyr::mutate(curve_group = "Saturated")
+saturation_regime_curve_summary <- saturation_regime_curve_summary |> 
+  dplyr::mutate(curve_group = "Saturation Regime")
 
-lod_dilution_summary <- lod_dilution_summary |> 
-  dplyr::mutate(curve_group = "Limit of Detection")
+noise_regime_curve_summary <- noise_regime_curve_summary |> 
+  dplyr::mutate(curve_group = "Noise Regime")
 
-linear_dilution_summary <- linear_dilution_summary |> 
-  dplyr::mutate(curve_group = "Linear")
+linear_curve_summary <- linear_curve_summary |> 
+  dplyr::mutate(curve_group = "Good Linearity")
 
-combined_dilution_summary <-
+combined_curve_summary <-
   dplyr::bind_rows(
-    saturation_dilution_summary,
-    lod_dilution_summary,
-    linear_dilution_summary
+    saturation_regime_curve_summary,
+    noise_regime_curve_summary,
+    linear_curve_summary
   ) 
@@
 #| echo: false
-combined_dilution_summary <- 
-  combined_dilution_summary |> 
+combined_curve_summary <- 
+  combined_curve_summary |> 
   dplyr::mutate(
     curve_group = factor(.data$curve_group,
-                         levels = c("Linear",
-                                    "Saturated",
-                                    "Limit of Detection")),
+                         levels = c("Good Linearity",
+                                    "Saturation Regime",
+                                    "Noise Regime")),
     pearson_group = dplyr::case_when(
@@
     ),
-    wf2_group = stringr::str_replace(
-      string = .data$wf2_group,
-      pattern = "LOD",
-      replacement = "Limit of Detection"
-    ),
     wf2_group = factor(.data$wf2_group,
                          levels = c("Good Linearity",
-                                    "Saturation",
-                                    "Limit of Detection",
+                                    "Saturation Regime",
+                                    "Noise Regime",
                                     "Poor Linearity"))
@@
 #| output: false
-simulation_results <- combined_dilution_summary |> 
+simulation_results <- combined_curve_summary |> 
   dplyr::select(c("curve_group", "wf2_group", 

### 2023-01-04 Manuscript/manuscript.qmd
Update images.

@@
 
-::: {#fig-overview layout="[[60,-40], [70,-30]]"}
+::: {#fig-overview layout="[[60,-40], [65,-35]]"}
 ![Curve Grouping Workflow](images/README-LinearEvaluation.png){#fig-linearity}
@@
 #| echo: false
-saturation_dilution_summary <- saturation_dilution_summary |> 
-  dplyr::mutate(curve_group = "Saturated")
+saturation_regime_curve_summary <- saturation_regime_curve_summary |> 
+  dplyr::mutate(curve_group = "Saturation Regime")
 
-lod_dilution_summary <- lod_dilution_summary |> 
-  dplyr::mutate(curve_group = "Limit of Detection")
+noise_regime_curve_summary <- noise_regime_curve_summary |> 
+  dplyr::mutate(curve_group = "Noise Regime")
 
-linear_dilution_summary <- linear_dilution_summary |> 
+linear_curve_summary <- linear_curve_summary |> 
   dplyr::mutate(curve_group = "Linear")
 
-combined_dilution_summary <-
+combined_curve_summary <-
   dplyr::bind_rows(
-    saturation_dilution_summary,
-    lod_dilution_summary,
-    linear_dilution_summary
+    saturation_regime_curve_summary,
+    noise_regime_curve_summary,
+    linear_curve_summary
   ) 
@@
       .data$r_corr < 0.8 ~ "less than 0.8",
-    ),
-    wf2_group = stringr::str_replace(
-      string = .data$wf2_group,
-      pattern = "LOD",
-      replacement = "Limit of Detection"
     ),
@@
 
-A benchmark workflow using only Pearson Correlation Coefficient value of $0.8$ is compared with Workflow 2 on simulated data sets of `r nrow(linear_dilution_summary)` linear curves (labelled as Linear), curves that plateau at low (labelled as Limit of Detection) high (labelled as Saturated) concentrations each.
+A benchmark workflow using only Pearson Correlation Coefficient value of $0.8$ is compared with Workflow 2 on simulated data sets of `r nrow(linear_curve_summary)` linear curves (labelled as Linear), curves that plateau at low (labelled as Limit of Detection) high (labelled as Saturated) concentrations each.
 Supplementary Figure 3 showed that Workflow 2 better identifies the saturated and limit of detection curves than the benchmark workflow.
-While it identifies less linear curves correctly than the benchmark workflow, its score of `r inline_text(simulation_results, variable = wf2_group, level = "Good Linearity", column = "Linear")` is comparable.
+While it identifies less linear curves correctly than the benchmark workflow, its score of `r inline_text(simulation_results, variable = wf2_group, level = "Good Linearity", column = "Good Linearity")` is comparable.
 See <https://lancer-simulation.netlify.app> for report details.

### 2023-01-04 Manuscript/manuscript.qmd
Update manuscript based on corrections made.

@@
 ---
-title: "*lancer*: a R package for linearity assessment and visualisation of multiple curves"
+title: "*lancer*: an R package for linearity assessment and visualisation of multiple curves"
 
@@
 Linearity assessment plays a significant role in the validation of instrumentation and experimental procedures.
-As technology progresses, many of these methods are becoming more high throughput, providing analysts with many measurements generated at a short time.
+As technology progresses, methods are becoming more high throughput, providing analysts with many measurements generated in a short time.
 Commonly used software, like Excel, only allow the analyst to repetitively plot, view and analyse the linearity of curves one at a time, a tedious and time-consuming process.
-In addition, summary statistics of these curves are limited to the Pearson Correlation Coefficient which is insufficient to fully understand the shape of the curves.
+In addition, summary statistics of these curves are mostly limited to the Pearson Correlation Coefficient which is insufficient to fully clarify the shape of the curves.
 *lancer* aims to provide additional summary statistics for assessing linearity of curves, taken from previous publications but which are not implemented in the current software tools.
@@
 It is applied in many fields in science such as calibration/dilution studies (@rodríguez1993 and @sands2021) and assay development (@ross2003 and @hsieh2008).
-During analysis, curves are plotted individually with a Pearson Correlation Coefficient value for each measurement using general-purpose software like Excel.
+After analysis, curve points are plotted individually for each analyte of interest with a Pearson Correlation Coefficient value for each plotted curve points using general-purpose software like Excel.
 
-However, as instrument or experimental method are becoming more high throughput, many measurements can be done at a short time.
+However, as instrument or experimental method are becoming more high throughput, many measurements can be done in a short time.
 Having the analyst to individually plot numerous curves to check for linearity is time-consuming.
 Furthermore, @sonnergaard2006 warns that the Pearson Correlation Coefficient is not an effective standalone numeric parameter to estimate linearity.
-While researchers have created other metrics for linearity evaluation, these metrics are rarely implemented in most general-purpose software.
+While researchers have created other metrics for linearity evaluation, these metrics are rarely implemented in most of the general-purpose software.
 
-R package, *lancer* addresses these issues by assisting analysts, to plot curves from many experiments easily with additional metrics, other than the Pearson Correlation Coefficient, that better describe the curve's shape.
-It also provides an interactive viewer for analysts to group, filter and sort the plots, allowing them to look at problematic ones, such as saturated curves.
+The R package, *lancer* addresses these issues by assisting analysts, to plot curves from many experiments easily with additional metrics, other than the Pearson Correlation Coefficient, that better describe the curve's shape.
+It also provides an interactive viewer for analysts to group, filter and sort the plots, allowing them to examine problematic ones, such as saturated curves.
 
@@
 
-Using the analysis of dilution curves in meatbolomic/lipidomic study as a running example, Supplementary Figure 1 depicts the workflow of *lancer*.
-The workflow starts with two tables: Transition Signal Data, containing transition signals (y-axis for dilution curve) for each sample and Dilution Annotation, containing dilution curve related information, such as concentration (x-axis for dilution curve) and dilution batches.
-Using a common column Sample Name, the two tables can be merged into one table (Dilution Table) via `create_dilution_table`.
+Using the analysis of response curves in metabolomic/lipidomic studies as an example, Supplementary Figure 1 depicts the workflow of *lancer*. The workflow starts with two tables:
 
-Next, summary statistics are calculated via `summarise_dilution_table` for each dilution curve.
-Besides the Pearson Correlation Coefficient, one additional calculation is the Mandel's Fitting Test ($F_{stats}$ in @eq-mandel-test) from @andrade2013.
+*    Curve Signal Data, containing response signals (y-axis for response curve) for each sample and curve. 
+*    Curve Batch Annotation, containing curve related information, such as concentration (x-axis for response curve) and response curve batches if any.
+
+Using a common column Sample Name, the two tables can be merged into one table (Curve Table) via `create_curve_table`.
+
+Next, summary statistics are calculated via `summarise_curve_table` for each response curve.
+Besides the Pearson Correlation Coefficient, one additional calculation is the Mandel's Fitting Test ($F_{stats}$ in @eq-mandel-test) described by @andrade2013.
 A low $p$ value from the $F$ test gives sufficient evidence that a quadratic model fits better than a linear model, indicating the curve may not be linear.
@@
 \end{aligned}
-$$ {#eq-mandel-test} Another one is Percent Residual Accuracy ($\%RA$ in @eq-pra) from @logue2018. Ranging from $-\infty$ to $100$, if the curve is linear, the value should be close to $100$.
+$$ {#eq-mandel-test} Another calculation is Percent Residual Accuracy ($\%RA$ in @eq-pra) from @logue2018.
+Ranging from $-\infty$ to $100$, if the curve is linear, the $\%RA$ value should be close to $100$.
 
@@
 
-Supplementary Figure 2 gives the summary statistics of three manually curated curves: A linear curve and curves with a plateau at higher concentrations (denoted as saturated curves) and lower concentrations (denoted as limit or detection or LOD curves) respectively.
-The corresponding Pearson Correlation Coefficient values (`r_corr`) are $\ge0.9$ ($0.99$, $0.95$ and $0.98$ respectively), even for the curves that are non-linear.
-However, both saturated and LOD curves give a much lower Mandel's Fitting Test $p$ values (`mandel_p_val`) ($1.66 * 10^{-4}$ and $2.56 * 10^{-3}$ respectively vs $0.38$).
-Likewise, the Percent Residual Accuracy values (`pra_linear`) are much lower in the saturated and LOD curves compared to the linear curve ($62.30$ and $74.69$ respectively vs $94.32$).
+Supplementary Figure 2 gives the summary statistics of three manually generated curves: A linear curve and two curves with a plateau at high concentrations (denoted as saturation regime curves) and low concentrations (denoted as noise regime curves) respectively.
+The corresponding Pearson Correlation Coefficient values (`r_corr`) are $\ge0.9$ ($0.99$, $0.95$ and $0.98$ respectively), even for the curves that are clearly non-linear.
+However, both non-linear curves give a much lower Mandel's Fitting Test $p$ values (`mandel_p_val`) ($1.66 * 10^{-4}$ and $2.56 * 10^{-3}$ respectively vs $0.38$).
+Likewise, the Percent Residual Accuracy values (`pra_linear`) are much lower in the non-linear curves compared to the linear curve ($62.30$ and $74.69$ respectively vs $94.32$).
 
@@
 
-`evaluate_linearity` is used to group the curves according to the workflows proposed in @fig-linearity.
+After calculating the summary statistics for each curve, *lancer* uses the function `evaluate_linearity` to group the curves according to the workflows proposed in @fig-linearity.
 Workflow 1 uses the Pearson Correlation Coefficient and Percent Residual Accuracy to determine if the curve is linear (labelled as Good Linearity) or not (labelled as Poor Linearity).
@@
 
-A benchmark workflow using only Pearson Correlation Coefficient value of $0.8$ is compared with Workflow 2 on simulated data sets of `r nrow(linear_curve_summary)` linear curves (labelled as Linear), curves that plateau at low (labelled as Limit of Detection) high (labelled as Saturated) concentrations each.
-Supplementary Figure 3 showed that Workflow 2 better identifies the saturated and limit of detection curves than the benchmark workflow.
-While it identifies less linear curves correctly than the benchmark workflow, its score of `r inline_text(simulation_results, variable = wf2_group, level = "Good Linearity", column = "Good Linearity")` is comparable.
+A benchmark workflow using only Pearson Correlation Coefficient value of $0.8$ is compared with Workflow 2 on simulated data sets of `r nrow(linear_curve_summary)` linear curves (labelled as Linear), curves that plateau at low (labelled as Limit of Detection) or high (labelled as Saturated) concentrations.
+Supplementary Figure 3 shows that Workflow 2 better identifies the saturated and limit of detection curves than the benchmark workflow.
+While it correctly classifies less linear curves than the benchmark workflow, its score of `r inline_text(simulation_results, variable = wf2_group, level = "Good Linearity", column = "Good Linearity")` is comparable.
 See <https://lancer-simulation.netlify.app> for report details.
 While the threshold values of Pearson Correlation Coefficient and Percent Residual Accuracy are based on the interpretation of @y.h.chan2003 and @logue2018, respectively, they remain subjective and arbitrary.
-Nevertheless, *lancer* allows optimization of these threshold values according to the analyst's determinants of linearity.
+Nevertheless, *lancer* allows optimization of these threshold values according to the analyst's preference of linearity.
 
 Although *lancer* can export the results in Excel or pdf, they may be too complex for meaningful interpretation.
-@fig-visualisation shows a HTML folder, exported by *lancer*, such that clicking on the `index.html` file inside the folder will open an interactive trellis plots that analysts can be grouped, filtered and sorted.
+@fig-visualisation shows a HTML folder, exported by *lancer*, such that clicking on the `index.html` file inside the folder will open an interactive trellis plot that can group, filter and sort cruves.
 This allows room for exploratory data analysis, such as identifying molecules with linearity issues or finding out the effects of changing the Pearson Correlation Coefficient threshold to another value.

### 2023-01-04 Quarto_Simulation/index.qmd
Remove Latex

@@
 
-We simulate $200$ curves (saturation regime, noise regime and linear) using $7$ points from $0$ to $200$ on the x-axis. A unique id is added for each simulated data.
+We simulate 200 curves (saturation regime, noise regime and linear) using 7 points from 0 to 200 on the x-axis. A unique id is added for each simulated data.
 
@@
 
-# Report Workflow $2$ Results
+# Report Workflow 2 Results
 
@@
 
-Perform some data wrangling to summarise the results later. A benchmark workflow using only Pearson Correlation Coefficient with a cut off value of $0.8$ is used to compare with Workflow $2$.
+Perform some data wrangling to summarise the results later. A benchmark workflow using only Pearson Correlation Coefficient with a cut off value of 0.8 is used to compare with Workflow 2.
 
@@
 
-Results showed that Workflow $2$ is able to identify the saturated and limit of detection curves better than the benchmark workflow.
-On the other hand, while Workflow $2$ is able to identify less linear curves than the benchmark workflow, it gives a comparable score of `r inline_text(simulation_results, variable = wf2_group, level = "Good Linearity", column = "Good Linearity")`
+Results showed that Workflow 2 is able to identify the saturated and limit of detection curves better than the benchmark workflow.
+On the other hand, while Workflow 2 is able to identify less linear curves than the benchmark workflow, it gives a comparable score of `r inline_text(simulation_results, variable = wf2_group, level = "Good Linearity", column = "Good Linearity")`
 

### 2023-01-05 Manuscript/manuscript.qmd
Update Manuscript.

@@
 
-Linearity assessment, as summarised by @paulson1995, is a standard protocol to verify if an instrument or experimental method is in working condition, especially if the method is used to report quantitative results.
-It is applied in many fields in science such as calibration/dilution studies (@rodríguez1993 and @sands2021) and assay development (@ross2003 and @hsieh2008).
-After analysis, curve points are plotted individually for each analyte of interest with a Pearson Correlation Coefficient value for each plotted curve points using general-purpose software like Excel.
+Linearity assessment is an important quality control to verify if the quantitative acquisition range of an instrument or experimental method is reliable.
+It is applied in many fields in analytical science such as calibration/dilution studies (@rodríguez1993 and @sands2021) and assay development (@ross2003 and @hsieh2008).
+After analysis, curves are plotted individually for each analyte of interest with a Pearson Correlation Coefficient value for each plotted curve using general-purpose software like Excel.
+A non-linear curve suggests possible human, systematic or analytical errors that need to be addressed.
+Examples of these errors are incorrect amount of analyte, imprecise pipette calibration, expired reagents or equipment malfunction.
 
@@
 Having the analyst to individually plot numerous curves to check for linearity is time-consuming.
-Furthermore, @sonnergaard2006 warns that the Pearson Correlation Coefficient is not an effective standalone numeric parameter to estimate linearity.
-While researchers have created other metrics for linearity evaluation, these metrics are rarely implemented in most of the general-purpose software.
+Furthermore, @sonnergaard2006 warns that the Pearson Correlation Coefficient is an ineffective standalone numeric parameter to estimate linearity.
+While researchers have created other metrics for linearity evaluation, these metrics are rarely implemented in most general-purpose software.
 
 The R package, *lancer* addresses these issues by assisting analysts, to plot curves from many experiments easily with additional metrics, other than the Pearson Correlation Coefficient, that better describe the curve's shape.
-It also provides an interactive viewer for analysts to group, filter and sort the plots, allowing them to examine problematic ones, such as saturated curves.
+It also provides an interactive viewer for analysts to group, filter and sort the curves, allowing them to examine problematic ones, such as saturated curves.
 
@@
 
-Using the analysis of response curves in metabolomic/lipidomic studies as an example, Supplementary Figure 1 depicts the workflow of *lancer*. The workflow starts with two tables:
+Using response curves in metabolomic/lipidomic studies as an example, Supplementary Figure 1 depicts the workflow of *lancer*. The workflow starts with two tables:
 
@@
 
-Next, summary statistics are calculated via `summarise_curve_table` for each response curve.
+Next, summary statistics are calculated via `summarise_curve_table` for each curve.
 Besides the Pearson Correlation Coefficient, one additional calculation is the Mandel's Fitting Test ($F_{stats}$ in @eq-mandel-test) described by @andrade2013.
-A low $p$ value from the $F$ test gives sufficient evidence that a quadratic model fits better than a linear model, indicating the curve may not be linear.
+A low $p$ value from the $F$ test gives sufficient evidence that a quadratic model fits better than a linear model, indicating a non-linear curve.
 
@@
 \end{aligned}
-$$ {#eq-mandel-test} Another calculation is Percent Residual Accuracy ($\%RA$ in @eq-pra) from @logue2018.
-Ranging from $-\infty$ to $100$, if the curve is linear, the $\%RA$ value should be close to $100$.
+$$ {#eq-mandel-test} Another calculation is Percent Residual Accuracy ($\%RA$ in @eq-pra) from @logue2018. Ranging from $-\infty$ to $100$, a linear curve gives a $\%RA$ value close to $100$.
 
@@
 
-The software also calculates the concavity of a fitted quadratic model to identify if the curve is dominantly non-linear at high (concavity $<0$) or low (concavity $>0$) concentrations.
+The software also calculates the concavity of the fitted quadratic model to identify if the curve is dominantly non-linear at high (concavity $<0$) or low (concavity $>0$) concentrations.
 
-Supplementary Figure 2 gives the summary statistics of three manually generated curves: A linear curve and two curves with a plateau at high concentrations (denoted as saturation regime curves) and low concentrations (denoted as noise regime curves) respectively.
-The corresponding Pearson Correlation Coefficient values (`r_corr`) are $\ge0.9$ ($0.99$, $0.95$ and $0.98$ respectively), even for the curves that are clearly non-linear.
+Supplementary Figure 2 gives the summary statistics of three manually generated curves: A linear curve and two curves with a plateau at high concentrations (denoted as saturation regime curve) and low concentrations (denoted as noise regime curve) respectively.
+The corresponding Pearson Correlation Coefficient values (`r_corr`) are $\ge0.9$ ($0.99$, $0.95$ and $0.98$ respectively), even for the non-linear curves.
 However, both non-linear curves give a much lower Mandel's Fitting Test $p$ values (`mandel_p_val`) ($1.66 * 10^{-4}$ and $2.56 * 10^{-3}$ respectively vs $0.38$).
@@
 linear_curve_summary <- linear_curve_summary |> 
-  dplyr::mutate(curve_group = "Linear")
+  dplyr::mutate(curve_group = "Good Linearity")
 
@@
                        levels = c("Good Linearity",
-                                    "Saturation",
-                                    "Limit of Detection",
+                                  "Saturation Regime",
+                                  "Noise Regime",
                                   "Poor Linearity"))
@@
 
-A benchmark workflow using only Pearson Correlation Coefficient value of $0.8$ is compared with Workflow 2 on simulated data sets of `r nrow(linear_curve_summary)` linear curves (labelled as Linear), curves that plateau at low (labelled as Limit of Detection) or high (labelled as Saturated) concentrations.
-Supplementary Figure 3 shows that Workflow 2 better identifies the saturated and limit of detection curves than the benchmark workflow.
-While it correctly classifies less linear curves than the benchmark workflow, its score of `r inline_text(simulation_results, variable = wf2_group, level = "Good Linearity", column = "Good Linearity")` is comparable.
+A benchmark workflow using only Pearson Correlation Coefficient value of $0.8$ is compared with Workflow 2 on simulated data sets of `r nrow(linear_curve_summary)` linear curves (labelled as Linear), curves that plateau at low (labelled as Noise Regime) or high (labelled as Saturation Regime) concentrations.
+Supplementary Figure 3 shows that Workflow 2 better identifies the saturation and noise regime curves than the benchmark workflow.
+While Workflow 2 correctly classifies less linear curves than the benchmark workflow, its percentage of correctly classified linear curves `r inline_text(simulation_results, variable = wf2_group, level = "Good Linearity", column = "Good Linearity")` is high.
 See <https://lancer-simulation.netlify.app> for report details.
 While the threshold values of Pearson Correlation Coefficient and Percent Residual Accuracy are based on the interpretation of @y.h.chan2003 and @logue2018, respectively, they remain subjective and arbitrary.
-Nevertheless, *lancer* allows optimization of these threshold values according to the analyst's preference of linearity.
+Nevertheless, *lancer* allows optimization of these threshold values according to the analyst's preference.
 
 Although *lancer* can export the results in Excel or pdf, they may be too complex for meaningful interpretation.
-@fig-visualisation shows a HTML folder, exported by *lancer*, such that clicking on the `index.html` file inside the folder will open an interactive trellis plot that can group, filter and sort cruves.
-This allows room for exploratory data analysis, such as identifying molecules with linearity issues or finding out the effects of changing the Pearson Correlation Coefficient threshold to another value.
+@fig-visualisation shows a HTML folder, exported by *lancer*, such that clicking on the `index.html` file inside the folder will open an interactive trellis plot that can group, filter and sort curves.
+This allows room for exploratory data analysis, such as identifying curves with linearity issues or understanding the effects of changing the Pearson Correlation Coefficient threshold to another value.
 Such information is hard to achieve with the Excel and pdf files.
@@
 
-To verify if an instrument or experimental method is reliable, it is important to check for linearity.
+To check if an instrument or experimental method is reliable, it is crucial to check for linearity.
 However, there are few software that can do this efficiently at a high throughput setting.
-R package, *lancer*, rectifies this by plotting of many curves quickly by automation and reporting alternative statistics, other than the Pearson Correlation Coefficient, to better describe the shape of curves.
+R package, *lancer*, rectifies this with functions that plots
+many curves quickly and reports alternative curve summary statistics, other than the Pearson Correlation Coefficient, to better describe the shape of curves.
 It also provides an interactive trellis plot for exploratory data analysis.

### 2023-01-21 Manuscript/manuscript.qmd
Update the introduction.

@@
 Linearity assessment plays a significant role in the validation of instrumentation and experimental procedures.
-As technology progresses, methods are becoming more high throughput, providing analysts with many measurements generated in a short time.
-Commonly used software, like Excel, only allow the analyst to repetitively plot, view and analyse the linearity of curves one at a time, a tedious and time-consuming process.
-In addition, summary statistics of these curves are mostly limited to the Pearson Correlation Coefficient which is insufficient to fully clarify the shape of the curves.
-*lancer* aims to provide additional summary statistics for assessing linearity of curves, taken from previous publications but which are not implemented in the current software tools.
-It also helps to reduce the analyst's workload by analysing many curves automatically, reporting the statistical results in Excel and recording the plots in a pdf file.
-In addition, it can also create an interactive trellis displayed as a HTML folder for more exploratory analysis.
+Linearity can be tested by applying several graphical and numerical approaches.
+Commonly used spreadsheet software, e.g.
+Microsoft Excel, only allow the analyst to repetitively plot, view and analyse the linearity of curves one at a time, a tedious and time-consuming process.
+In addition, summary statistics of these curves are mostly limited to the Pearson Correlation Coefficient, which is insufficient to fully test the for linearity.
+While plotting of many curves at once and calculation of additional summary statistics for assessing linearity of curves can be done using programming languages like R, implementing this from scratch can be arduous task for the analyst.
+As such, we created the R package *lancer* so that curves can be analysed efficiently with a few functions.
+To our knowledge, this is currently not implemented in other software or programming languages.
+*lancer* furthermore reports the statistical results in tables/spreadsheets and records the plots in a pdf file.
+In addition, *lancer* can also create interactive trellis plots, displayed as a HTML folder, for exploratory analysis, helping analysts when dealing with large datasets.
 

### 2023-01-21 Manuscript/manuscript.qmd
Update scripts based on teams suggestions.

@@
 
-Linearity assessment is an important quality control to verify if the quantitative acquisition range of an instrument or experimental method is reliable.
-It is applied in many fields in analytical science such as calibration/dilution studies (@rodríguez1993 and @sands2021) and assay development (@ross2003 and @hsieh2008).
-After analysis, curves are plotted individually for each analyte of interest with a Pearson Correlation Coefficient value for each plotted curve using general-purpose software like Excel.
-A non-linear curve suggests possible human, systematic or analytical errors that need to be addressed.
-Examples of these errors are incorrect amount of analyte, imprecise pipette calibration, expired reagents or equipment malfunction.
+Linearity assessment is an important performance test of an analytical instrument or method when a linear response is assumed.
+It is applied in many fields in analytical sciences, such as assay development (@ross2003 and @hsieh2008), calibration/dilution studies (@rodríguez1993 and @sands2021) and laboratory tests.
+After analysis, curves representing response values versus concentration are plotted for each analyte of interest.
+As the accuracy of an analytical method is linked to linearity, a non-linear behaviour must be recognized and addressed accordingly.
+Visual inspection of curves is still useful but it must be accompanied by statistical tests as decision parameters.
 
-However, as instrument or experimental method are becoming more high throughput, many measurements can be done in a short time.
-Having the analyst to individually plot numerous curves to check for linearity is time-consuming.
-Furthermore, @sonnergaard2006 warns that the Pearson Correlation Coefficient is an ineffective standalone numeric parameter to estimate linearity.
-While researchers have created other metrics for linearity evaluation, these metrics are rarely implemented in most general-purpose software.
+To individually plot numerous curves and check for linearity is time-consuming.
+Furthermore, @sonnergaard2006 suggests that the Pearson Correlation Coefficient, a commonly used test, is an ineffective standalone numeric parameter to estimate linearity.
+While researchers like @vanloco2002, @sanchez2021 and @logue2018 have indicated other metrics for linearity evaluation, these metrics are generally not implemented in most software.
 
-The R package, *lancer* addresses these issues by assisting analysts, to plot curves from many experiments easily with additional metrics, other than the Pearson Correlation Coefficient, that better describe the curve's shape.
-It also provides an interactive viewer for analysts to group, filter and sort the curves, allowing them to examine problematic ones, such as saturated curves.
+The R package *lancer* addresses these issues by assisting analysts to plot curves from many experiments, with additional metrics that better describe the characteristics of the curve.
+It also provides users with an interactive viewer to group, filter and sort the curves, allowing the examination of problematic cases, such as the ones generated by saturated signals.
 
@@
 
-Using response curves in metabolomic/lipidomic studies as an example, Supplementary Figure 1 depicts the workflow of *lancer*. The workflow starts with two tables:
+Using response curves in metabolomic/lipidomic studies from @croixmarie2009 and @sands2021 as an example, Supplementary Figure 1 depicts the workflow of *lancer*. The workflow starts with two tables:
 
-*    Curve Signal Data, containing response signals (y-axis for response curve) for each sample and curve. 
-*    Curve Batch Annotation, containing curve related information, such as concentration (x-axis for response curve) and response curve batches if any.
+*    Curve Batch Annotation, describing the curve(s), such as concentration (x-axis) and response curve batches, if any.
+*    Curve Signal Data, containing response values (y-axis) for each sample and curve.
 
@@
 Next, summary statistics are calculated via `summarise_curve_table` for each curve.
-Besides the Pearson Correlation Coefficient, one additional calculation is the Mandel's Fitting Test ($F_{stats}$ in @eq-mandel-test) described by @andrade2013.
-A low $p$ value from the $F$ test gives sufficient evidence that a quadratic model fits better than a linear model, indicating a non-linear curve.
+Besides the Pearson Correlation Coefficient, an additional statistical test is the Mandel’s Fitting Test ($F_{stats}$ in @eq-mandel-test) as described by @andrade2013.
+The $F$ test can give evidence that a quadratic model fits better than a linear model, indicating a non-linear curve.
 
@@
 \end{aligned}
-$$ {#eq-mandel-test} Another calculation is Percent Residual Accuracy ($\%RA$ in @eq-pra) from @logue2018. Ranging from $-\infty$ to $100$, a linear curve gives a $\%RA$ value close to $100$.
+$$ {#eq-mandel-test} Another statistical test is Percent Residual Accuracy ($\%RA$ in @eq-pra) from @logue2018.
+Ranging from $-\infty$ to $100$, according to which a perfectly linear curve gives a $\%RA$ value of $100$.
 
@@
 
-The software also calculates the concavity of the fitted quadratic model to identify if the curve is dominantly non-linear at high (concavity $<0$) or low (concavity $>0$) concentrations.
+The software also calculates the concavity of the fitted quadratic model, to identify if the curve is dominantly non-linear at high (concavity $<0$) or low (concavity $>0$) concentrations.
 
-Supplementary Figure 2 gives the summary statistics of three manually generated curves: A linear curve and two curves with a plateau at high concentrations (denoted as saturation regime curve) and low concentrations (denoted as noise regime curve) respectively.
-The corresponding Pearson Correlation Coefficient values (`r_corr`) are $\ge0.9$ ($0.99$, $0.95$ and $0.98$ respectively), even for the non-linear curves.
-However, both non-linear curves give a much lower Mandel's Fitting Test $p$ values (`mandel_p_val`) ($1.66 * 10^{-4}$ and $2.56 * 10^{-3}$ respectively vs $0.38$).
-Likewise, the Percent Residual Accuracy values (`pra_linear`) are much lower in the non-linear curves compared to the linear curve ($62.30$ and $74.69$ respectively vs $94.32$).
+Supplementary Figure 2 gives the summary statistics of three simulated curves (as examples), where one curve is linear and two curves show a plateau at high concentrations (denoted as saturation regime curve) and low concentrations (denoted as noise regime curve), respectively.
+The corresponding Pearson Correlation Coefficient values (`r_corr`) are $\ge0.9$ ($0.99$, $0.95$ and $0.98$ respectively) even for the non-linear curves.
+However, non-linear curves are detected by much lower Mandel’s Fitting Test $p$ values (`mandel_p_val`) ($1.66 * 10^{-4}$ and $2.56 * 10^{-3}$ respectively vs $0.38$ for the linear curve) and Percent Residual Accuracy values (`pra_linear`) ($62.30$ and $74.69$ respectively vs $94.32$ for the linear curve).
 
@@
 Workflow 1 uses the Pearson Correlation Coefficient and Percent Residual Accuracy to determine if the curve is linear (labelled as Good Linearity) or not (labelled as Poor Linearity).
-Workflow 2 goes one step further, using the Mandel's Fitting Test and the fitted quadratic model's concavity to check if the non-linear curve plateaus at low (labeled as limit of detection) or high (labelled as saturation) concentrations.
+Workflow 2 goes one step further, using the Mandel’s Fitting Test and the fitted quadratic model’s concavity to check if a non-linear curve plateaus at low (labeled as Noise Regime) or high (labelled as Saturation Regime) concentrations.
 Non-linear curves that do not follow these trends are labelled as Poor Linearity.
@@
 Supplementary Figure 3 shows that Workflow 2 better identifies the saturation and noise regime curves than the benchmark workflow.
-While Workflow 2 correctly classifies less linear curves than the benchmark workflow, its percentage of correctly classified linear curves `r inline_text(simulation_results, variable = wf2_group, level = "Good Linearity", column = "Good Linearity")` is high.
+While Workflow 2 correctly classifies a lower number of linear curves than the benchmark workflow, its percentage of correctly classified linear curves, `r inline_text(simulation_results, variable = wf2_group, level = "Good Linearity", column = "Good Linearity")`, is high.
 See <https://lancer-simulation.netlify.app> for report details.
-While the threshold values of Pearson Correlation Coefficient and Percent Residual Accuracy are based on the interpretation of @y.h.chan2003 and @logue2018, respectively, they remain subjective and arbitrary.
-Nevertheless, *lancer* allows optimization of these threshold values according to the analyst's preference.
+While the threshold values of Pearson Correlation Coefficient and Percent Residual Accuracy are based on the interpretation of @y.h.chan2003 and @logue2018, they remain subjective and arbitrary.
+Nevertheless, *lancer* allows optimization of these threshold values according to the analyst’s preference.
 
-Although *lancer* can export the results in Excel or pdf, they may be too complex for meaningful interpretation.
-@fig-visualisation shows a HTML folder, exported by *lancer*, such that clicking on the `index.html` file inside the folder will open an interactive trellis plot that can group, filter and sort curves.
+Although *lancer* can export the results in Excel or pdf, an interactive user interface can generate a better overview of the data.
+@fig-visualisation shows a HTML folder, exported by *lancer*, such that clicking on the index.html file inside the folder will open an interactive trellis plot that can group, filter and sort curves.
 This allows room for exploratory data analysis, such as identifying curves with linearity issues or understanding the effects of changing the Pearson Correlation Coefficient threshold to another value.
-Such information is hard to achieve with the Excel and pdf files.
-An example of an interactive viewer created by *lancer* can be viewed at <https://lancer-interactive-example.netlify.app>
+Such information is hard to achieve with other common software.
+An example of an interactive viewer created by *lancer* can be found at <https://lancer-interactive-example.netlify.app>
 
@@
 
-To check if an instrument or experimental method is reliable, it is crucial to check for linearity.
-However, there are few software that can do this efficiently at a high throughput setting.
-R package, *lancer*, rectifies this with functions that plots
-many curves quickly and reports alternative curve summary statistics, other than the Pearson Correlation Coefficient, to better describe the shape of curves.
+Linearity is one of the most important parameters of an analytical method to be evaluated.
+Our R package, *lancer*, can estimate linearity efficiently in high-throughput settings and with functions that plot many curves quickly, reporting curve summary statistics to better describe the shape of the datasets.
 It also provides an interactive trellis plot for exploratory data analysis.

### 2023-01-21 Manuscript/manuscript.qmd
Swap statictical summary issue and plotting of many curves issue.

@@
 Linearity can be tested by applying several graphical and numerical approaches.
-Commonly used spreadsheet software, e.g.
+Summary statistics of these curves are mostly limited to the Pearson Correlation Coefficient, which is insufficient to fully test the for linearity.
+In addition, spreadsheet software, e.g.
 Microsoft Excel, only allow the analyst to repetitively plot, view and analyse the linearity of curves one at a time, a tedious and time-consuming process.
-In addition, summary statistics of these curves are mostly limited to the Pearson Correlation Coefficient, which is insufficient to fully test the for linearity.
 While plotting of many curves at once and calculation of additional summary statistics for assessing linearity of curves can be done using programming languages like R, implementing this from scratch can be arduous task for the analyst.
@@
 As the accuracy of an analytical method is linked to linearity, a non-linear behaviour must be recognized and addressed accordingly.
-Visual inspection of curves is still useful but it must be accompanied by statistical tests as decision parameters.
 
-To individually plot numerous curves and check for linearity is time-consuming.
-Furthermore, @sonnergaard2006 suggests that the Pearson Correlation Coefficient, a commonly used test, is an ineffective standalone numeric parameter to estimate linearity.
+Visual inspection of curves is useful but it must be accompanied by statistical tests as decision parameters.
+A commonly used test is the Pearson Correlation Coefficient.
+However, @sonnergaard2006 suggests that it is an ineffective standalone numeric parameter to estimate linearity.
 While researchers like @vanloco2002, @sanchez2021 and @logue2018 have indicated other metrics for linearity evaluation, these metrics are generally not implemented in most software.
+Furthermore, using spreadsheet software, e.g.
+Microsoft Excel, to individually plot numerous curves is time-consuming.
+While programming languages like R can plot numerous curve easily, it is hard to implement for a novice analyst.
 
-The R package *lancer* addresses these issues by assisting analysts to plot curves from many experiments, with additional metrics that better describe the characteristics of the curve.
-It also provides users with an interactive viewer to group, filter and sort the curves, allowing the examination of problematic cases, such as the ones generated by saturated signals.
+The R package *lancer* addresses these issues by assisting analysts useful functions to plot many curves with additional metrics that better describe the curves' characteristics.
+It also provides analysts with an interactive viewer to group, filter and sort the curves, for examination of problematic cases, such as curves generated by saturated signals.
 

### 2023-01-22 Manuscript/manuscript.qmd
Update documents. See NEWS.md for more information.

@@
 Summary statistics of these curves are mostly limited to the Pearson Correlation Coefficient, which is insufficient to fully test the for linearity.
-In addition, spreadsheet software, e.g.
-Microsoft Excel, only allow the analyst to repetitively plot, view and analyse the linearity of curves one at a time, a tedious and time-consuming process.
-While plotting of many curves at once and calculation of additional summary statistics for assessing linearity of curves can be done using programming languages like R, implementing this from scratch can be arduous task for the analyst.
+In addition, spreadsheet software only allow the analyst to repetitively plot, view and analyse the linearity of curves one at a time, a tedious and time-consuming process.
+While plotting of many curves at once and calculation of additional summary statistics for assessing linearity of curves can be done using R, implementing this from scratch can be arduous task for the analyst.
 As such, we created the R package *lancer* so that curves can be analysed efficiently with a few functions.
@@
 
-Visual inspection of curves is useful but it must be accompanied by statistical tests as decision parameters.
+Visual inspection of curves is useful but must be accompanied by statistical tests as decision parameters.
 A commonly used test is the Pearson Correlation Coefficient.
-However, @sonnergaard2006 suggests that it is an ineffective standalone numeric parameter to estimate linearity.
-While researchers like @vanloco2002, @sanchez2021 and @logue2018 have indicated other metrics for linearity evaluation, these metrics are generally not implemented in most software.
-Furthermore, using spreadsheet software, e.g.
-Microsoft Excel, to individually plot numerous curves is time-consuming.
-While programming languages like R can plot numerous curve easily, it is hard to implement for a novice analyst.
+However, @sonnergaard2006 suggests that it is an ineffective standalone numeric parameter for accessing linearity.
+While @vanloco2002, @sanchez2021 and @logue2018 have indicated other metrics for linearity evaluation, these metrics are generally not implemented in most software.
+Furthermore, using spreadsheet software to individually plot numerous curves is time-consuming.
+While R (@rprogramming) can plot numerous curve easily, it is hard to implement for a novice analyst.
 
-The R package *lancer* addresses these issues by assisting analysts useful functions to plot many curves with additional metrics that better describe the curves' characteristics.
-It also provides analysts with an interactive viewer to group, filter and sort the curves, for examination of problematic cases, such as curves generated by saturated signals.
+The R package *lancer* addresses these issues by assisting analysts with useful functions to plot many curves with additional metrics that better describe the curves' characteristics.
+@fig-visualisation shows that *lancer* also provides an interactive viewer to group, filter and sort the curves, for examination of problematic cases, such as curves generated by saturated signals.
+
+![*lancer*'s interactive visualisation of curves](images/README-TrellisOutput.png){#fig-visualisation}
 
@@
 
-Using a common column Sample Name, the two tables can be merged into one table (Curve Table) via `create_curve_table`.
+Using a common column Sample Name, the two tables are merged into one table (Curve Table) via `create_curve_table`.
 
-Next, summary statistics are calculated via `summarise_curve_table` for each curve.
+Next, each curve's summary statistics are calculated via `summarise_curve_table`.
 Besides the Pearson Correlation Coefficient, an additional statistical test is the Mandel’s Fitting Test ($F_{stats}$ in @eq-mandel-test) as described by @andrade2013.
@@
 
-Supplementary Figure 2 gives the summary statistics of three simulated curves (as examples), where one curve is linear and two curves show a plateau at high concentrations (denoted as saturation regime curve) and low concentrations (denoted as noise regime curve), respectively.
+Supplementary Figure 2 gives the summary statistics of three simulated curves as examples, where one curve is linear and two non-linear curves with a plateau at high and low concentrations, denoted as saturation and noise regime curve respectively as defined by @galitzine2018.
 The corresponding Pearson Correlation Coefficient values (`r_corr`) are $\ge0.9$ ($0.99$, $0.95$ and $0.98$ respectively) even for the non-linear curves.
@@
 
-{{< pagebreak >}}
-
-::: {#fig-overview layout="[[60,-40], [65,-35]]"}
-![Curve Grouping Workflow](images/README-LinearEvaluation.png){#fig-linearity}
-
-![Interactive Visualisation](images/README-TrellisOutput.png){#fig-visualisation}
-
-*lancer*'s curve grouping workflow in @fig-linearity and interactive visualisation of curves in @fig-visualisation.
-:::
-
-{{< pagebreak >}}
-
-After calculating the summary statistics for each curve, *lancer* uses the function `evaluate_linearity` to group the curves according to the workflows proposed in @fig-linearity.
-Workflow 1 uses the Pearson Correlation Coefficient and Percent Residual Accuracy to determine if the curve is linear (labelled as Good Linearity) or not (labelled as Poor Linearity).
-Workflow 2 goes one step further, using the Mandel’s Fitting Test and the fitted quadratic model’s concavity to check if a non-linear curve plateaus at low (labeled as Noise Regime) or high (labelled as Saturation Regime) concentrations.
-Non-linear curves that do not follow these trends are labelled as Poor Linearity.
+After calculating the summary statistics for each curve, *lancer* uses the function `evaluate_linearity` to group the curves according to the workflows proposed in Supplementary Figure 3.
+Workflow 1 uses the Pearson Correlation Coefficient and Percent Residual Accuracy to determine if the curve is linear or not, labelled as Good or Poor Linearity respectively.
+Workflow 2 goes one step further, using Mandel’s Fitting Test and the fitted quadratic model’s concavity to label a non-linear curve as Saturation or Noise Regime, if it plateaus at high or low concentrations respectively.
+Non-linear curves that do not follow these trends are then labelled as Poor Linearity.
 
@@
 
-A benchmark workflow using only Pearson Correlation Coefficient value of $0.8$ is compared with Workflow 2 on simulated data sets of `r nrow(linear_curve_summary)` linear curves (labelled as Linear), curves that plateau at low (labelled as Noise Regime) or high (labelled as Saturation Regime) concentrations.
-Supplementary Figure 3 shows that Workflow 2 better identifies the saturation and noise regime curves than the benchmark workflow.
+A benchmark workflow using only Pearson Correlation Coefficient value of $0.8$ is compared with Workflow 2 on simulated data sets of `r nrow(linear_curve_summary)` linear curves (labelled as Linear), non-linear curves that plateau at high and low concentrations (labelled as Saturation and Noise Regime respectively).
+Supplementary Figure 4 shows that Workflow 2 better identifies the saturation and noise regime curves than the benchmark workflow.
 While Workflow 2 correctly classifies a lower number of linear curves than the benchmark workflow, its percentage of correctly classified linear curves, `r inline_text(simulation_results, variable = wf2_group, level = "Good Linearity", column = "Good Linearity")`, is high.
@@
 
-Although *lancer* can export the results in Excel or pdf, an interactive user interface can generate a better overview of the data.
-@fig-visualisation shows a HTML folder, exported by *lancer*, such that clicking on the index.html file inside the folder will open an interactive trellis plot that can group, filter and sort curves.
-This allows room for exploratory data analysis, such as identifying curves with linearity issues or understanding the effects of changing the Pearson Correlation Coefficient threshold to another value.
-Such information is hard to achieve with other common software.
-An example of an interactive viewer created by *lancer* can be found at <https://lancer-interactive-example.netlify.app>
+Although *lancer* can export the results in Excel or pdf, an interactive interface can generate a better overview.
+@fig-visualisation shows a HTML folder, exported by *lancer*.
+Clicking on the `index.html` file inside the folder opens an interactive plot that can group, filter and sort curves.
+This allows room for exploratory data analysis, such as identifying curves with linearity issues or understanding the consequence of changing the Pearson Correlation Coefficient threshold to another value.
+Such information is hard to achieve with static plots alone.
+An interactive viewer example created by *lancer* can be found at <https://lancer-interactive-example.netlify.app>
 
@@
 
-Linearity is one of the most important parameters of an analytical method to be evaluated.
-Our R package, *lancer*, can estimate linearity efficiently in high-throughput settings and with functions that plot many curves quickly, reporting curve summary statistics to better describe the shape of the datasets.
-It also provides an interactive trellis plot for exploratory data analysis.
-It is available on GitHub <https://github.com/SLINGhub/lancer> while the documentation and tutorials can be accessed from <https://slinghub.github.io/lancer>.
+Linearity is one of the most important parameter of an analytical method to be evaluated.
+Our R package, *lancer*, can access linearity efficiently using functions that quickly plot and report curve summary statistics, which better describe the shape of the curve.
+It also provides an interactive plot for exploratory data analysis.
+*lancer* is available on GitHub <https://github.com/SLINGhub/lancer> while the documentation and tutorials can be accessed from <https://slinghub.github.io/lancer>.
 

### 2023-01-22 Manuscript/supplementary.qmd
Update documents. See NEWS.md for more information.

@@
 
-![*lancer* Workflow](images/README-Workflow.png){#fig-lancer-Workflow}
+![*lancer* Workflow](images/README-Workflow.png){#fig-lancer-workflow}
 
@@
 
+![Curve Grouping Workflow](images/README-LinearEvaluation.png){#fig-linearity}
+
 ```{r Load Simulated Data Results}
@@
 
-![Simulation Results](images/simulation_results.png){#fig-Simulation}
+![Simulation Results](images/simulation_results.png){#fig-simulation}

### 2023-01-27 README.qmd
Test figshare doi badge.

@@
 ---
+
+[![DOI](https://img.shields.io/badge/doi-10.26180/5c6e1160b8d8a-blue.svg?style=flat&labelColor=whitesmoke&logo=data%3Aimage%2Fpng%3Bbase64%2CiVBORw0KGgoAAAANSUhEUgAAAB8AAAAfCAYAAAAfrhY5AAAJsklEQVR42qWXd1DTaRrHf%2BiB2Hdt5zhrAUKz4IKEYu9IGiGFFJJQ0gkJCAKiWFDWBRdFhCQUF3UVdeVcRQEBxUI3yY9iEnQHb3bdW1fPubnyz%2F11M7lvEHfOQee2ZOYzPyDv%2B3yf9%2Fk95YX4fx%2BltfUt08GcFEuPR4U9hDDZ%2FVngIlhb%2FSiI6InkTgLzgDcgfvtnovhH4BzoVlrbwr55QnhCtBW4QHXnFrZbPBaQoBh4%2FSYH2EnpBEtqcDMVzB93wA%2F8AFwa23XFGcc8CkT3mxz%2BfXWtq9T9IQlLIXYEuHojudb%2BCM7Hgdq8ydi%2FAHiBXyY%2BLjwFlAEnS6Jnar%2FvnQVhvdzasad0eKvWZKe8hvDB2ofLZ%2FZEcWsh%2BhyIuyO5Bxs2iZIE4nRv7NWAb0EO8AC%2FWPxjYAWuOEX2MSXZVgPxzmRL3xKz3ScGpx6p6QnOx4mDIFqO0w6Q4fEhO5IzwxlSwyD2FYHzwAW%2BAZ4fEsf74gCumykwNHskLM7taQxLYjjIyy8MUtraGhTWdkfhkFJqtvuVl%2F9l2ZquDfEyrH8B0W06nnpH3JtIyRGpH1iJ6SfxDIHjRXHJmdQjLpfHeN54gnfFx4W9QRnovx%2FN20aXZeTD2J84hn3%2BqoF2Tqr14VqTPUCIcP%2B5%2Fly4qC%2BUL3sYxSvNj1NwsVYPsWdMUfomsdkYm3Tj0nbV0N1wRKwFe1MgKACDIBdMAhPE%2FwicwNWxll8Ag40w%2BFfhibJkGHmutjYeQ8gVlaN%2BjO51nDysa9TwNUFMqaGbKdRJZFfOJSp6mkRKsv0rRIpEVWjAvyFkxNOEpwvcAVPfEe%2Bl8ojeNTx3nXLBcWRrYGxSRjDEk0VlpxYrbe1ZmaQ5xuT0u3r%2B2qe5j0J5uytiZPGsRL2Jm32AldpxPUNJ3jmmsN4x62z1cXrbedXBQf2yvIFCeZrtyicZZG2U2nrrBJzYorI2EXLrvTfCSB43s41PKEvbZDEfQby6L4JTj%2FfIwam%2B4%2BwucBu%2BDgNK05Nle1rSt9HvR%2FKPC4U6LTfvUIaip1mjIa8fPzykii23h2eanT57zQ7fsyYH5QjywwlooAUcAdOh5QumgTHx6aAO7%2FL52eaQNEShrxfhL6albEDmfhGflrsT4tps8gTHNOJbeDeBlt0WJWDHSgxs6cW6lQqyg1FpD5ZVDfhn1HYFF1y4Eiaqa18pQf3zzYMBhcanlBjYfgWNayAf%2FASOgklu8bmgD7hADrk4cRlOL7NSOewEcbqSmaivT33QuFdHXj5sdvjlN5yMDrAECmdgDWG2L8P%2BAKLs9ZLZ7dJda%2BB4Xl84t7QvnKfvpXJv9obz2KgK8dXyqISyV0sXGZ0U47hOA%2FAiigbEMECJxC9aoKp86re5O5prxOlHkcksutSQJzxZRlPZmrOKhsQBF5zEZKybUC0vVjG8PqOnhOq46qyDTDnj5gZBriWCk4DvXrudQnXQmnXblebhAC2cCB6zIbM4PYgGl0elPSgIf3iFEA21aLdHYLHUQuVkpgi02SxFdrG862Y8ymYGMvXDzUmiX8DS5vKZyZlGmsSgQqfLub5RyLNS4zfDiZc9Edzh%2FtCE%2BX8j9k%2FqWB071rcZyMImne1SLkL4GRw4UPHMV3jjwEYpPG5uW5fAEot0aTSJnsGAwHJi2nvF1Y5OIqWziVCQd5NT7t6Q8guOSpgS%2Fa1dSRn8JGGaCD3BPXDyQRG4Bqhu8XrgAp0yy8DMSvvyVXDgJcJTcr1wQ2BvFKf65jqhvmxXUuDpGBlRvV36XvGjQzLi8KAKT2lYOnmxQPGorURSV0NhyTIuIyqOmKTMhQ%2BieEsgOgpc4KBbfDM4B3SIgFljvfHF6cef7qpyLBXAiQcXvg5l3Iunp%2FWv4dH6qFziO%2BL9PbrimQ9RY6MQphEfGUpOmma7KkGzuS8sPUFnCtIYcKCaI9EXo4HlQLgGrBjbiK5EqMj2AKWt9QWcIFMtnVvQVDQV9lXJJqdPVtUQpbh6gCI2Ov1nvZts7yYdsnvRgxiWFOtNJcOMVLn1vgptVi6qrNiFOfEjHCDB3J%2BHDLqUB77YgQGwX%2Fb1eYna3hGKdlqJKIyiE4nSbV8VFgxmxR4b5mVkkeUhMgs5YTi4ja2XZ009xJRHdkfwMi%2BfocaancuO7h%2FMlcLOa0V%2FSw6Dq47CumRQAKhgbOP8t%2BMTjuxjJGhXCY6XpmDDFqWlVYbQ1aDJ5Cptdw4oLbf3Ck%2BdWkVP0LpH7s9XLPXI%2FQX8ws%2Bj2In63IcRvOOo%2BTTjiN%2BlssfRsanW%2B3REVKoavBOAPTXABW4AL7e4NygHdpAKBscmlDh9Jysp4wxbnUNna3L3xBvyE1jyrGIkUHaqQMuxhHElV6oj1picvgL1QEuS5PyZTEaivqh5vUCKJqOuIgPFGESns8kyFk7%2FDxyima3cYxi%2FYOQCj%2F%2B9Ms2Ll%2Bhn4FmKnl7JkGXQGDKDAz9rUGL1TIlBpuJr9Be2JjK6qPzyDg495UxXYF7JY1qKimw9jWjF0iV6DRIqE%2B%2FeWG0J2ofmZTk0mLYVd4GLiFCOoKR0Cg727tWq981InYynvCuKW43aXgEjofVbxIqrm0VL76zlH3gQzWP3R3Bv9oXxclrlO7VVtgBRpSP4hMFWJ8BrUSBCJXC07l40X4jWuvtc42ofNCxtlX2JH6bdeojXgTh5TxOBKEyY5wvBE%2BACh8BtOPNPkApjoxi5h%2B%2FFMQQNpWvZaMH7MKFu5Ax8HoCQdmGkJrtnOiLHwD3uS5y8%2F2xTSDrE%2F4PT1yqtt6vGe8ldMBVMEPd6KwqiYECHDlfbvzphcWP%2BJiZuL5swoWQYlS%2Br7Yu5mNUiGD2retxBi9fl6RDGn4Ti9B1oyYy%2BMP5G87D%2FCpRlvdnuy0PY6RC8BzTA40NXqckQ9TaOUDywkYsudxJzPgyDoAWn%2BB6nEFbaVxxC6UXjJiuDkW9TWq7uRBOJocky9iMfUhGpv%2FdQuVVIuGjYqACbXf8aa%2BPeYNIHZsM7l4s5gAQuUAzRUoT51hnH3EWofXf2vkD5HJJ33vwE%2FaEWp36GHr6GpMaH4AAPuqM5eabH%2FhfG9zcCz4nN6cPinuAw6IHwtvyB%2FdO1toZciBaPh25U0ducR2PI3Zl7mokyLWKkSnEDOg1x5fCsJE9EKhH7HwFNhWMGMS7%2BqxyYsbHHRUDUH4I%2FAheQY7wujJNnFUH4KdCju83riuQeHU9WEqNzjsJFuF%2FdTDAZ%2FK7%2F1WaAU%2BAWymT59pVMT4g2AxcwNa0XEBDdBDpAPvgDIH73R25teeuAF5ime2Ul0OUIiG4GpSAEJeYW9wDTf43wfwHgHLKJoPznkwAAAABJRU5ErkJggg%3D%3D)](https://doi.org/10.6084/m9.figshare.21965324)
 

### 2023-01-27 README.qmd
Add a figshare doi badge.

--- 2023-01-04 README.qmd
@@
 ---
+
+[](https://img.shields.io/badge/doi-10.6084/m9.figshare.21965324-blue.svg?style=flat&labelColor=whitesmoke&logo=data%3Aimage%2Fpng%3Bbase64%2CiVBORw0KGgoAAAANSUhEUgAAAB8AAAAfCAYAAAAfrhY5AAAJsklEQVR42qWXd1DTaRrHf%2BiB2Hdt5zhrAUKz4IKEYu9IGiGFFJJQ0gkJCAKiWFDWBRdFhCQUF3UVdeVcRQEBxUI3yY9iEnQHb3bdW1fPubnyz%2F11M7lvEHfOQee2ZOYzPyDv%2B3yf9%2Fk95YX4fx%2BltfUt08GcFEuPR4U9hDDZ%2FVngIlhb%2FSiI6InkTgLzgDcgfvtnovhH4BzoVlrbwr55QnhCtBW4QHXnFrZbPBaQoBh4%2FSYH2EnpBEtqcDMVzB93wA%2F8AFwa23XFGcc8CkT3mxz%2BfXWtq9T9IQlLIXYEuHojudb%2BCM7Hgdq8ydi%2FAHiBXyY%2BLjwFlAEnS6Jnar%2FvnQVhvdzasad0eKvWZKe8hvDB2ofLZ%2FZEcWsh%2BhyIuyO5Bxs2iZIE4nRv7NWAb0EO8AC%2FWPxjYAWuOEX2MSXZVgPxzmRL3xKz3ScGpx6p6QnOx4mDIFqO0w6Q4fEhO5IzwxlSwyD2FYHzwAW%2BAZ4fEsf74gCumykwNHskLM7taQxLYjjIyy8MUtraGhTWdkfhkFJqtvuVl%2F9l2ZquDfEyrH8B0W06nnpH3JtIyRGpH1iJ6SfxDIHjRXHJmdQjLpfHeN54gnfFx4W9QRnovx%2FN20aXZeTD2J84hn3%2BqoF2Tqr14VqTPUCIcP%2B5%2Fly4qC%2BUL3sYxSvNj1NwsVYPsWdMUfomsdkYm3Tj0nbV0N1wRKwFe1MgKACDIBdMAhPE%2FwicwNWxll8Ag40w%2BFfhibJkGHmutjYeQ8gVlaN%2BjO51nDysa9TwNUFMqaGbKdRJZFfOJSp6mkRKsv0rRIpEVWjAvyFkxNOEpwvcAVPfEe%2Bl8ojeNTx3nXLBcWRrYGxSRjDEk0VlpxYrbe1ZmaQ5xuT0u3r%2B2qe5j0J5uytiZPGsRL2Jm32AldpxPUNJ3jmmsN4x62z1cXrbedXBQf2yvIFCeZrtyicZZG2U2nrrBJzYorI2EXLrvTfCSB43s41PKEvbZDEfQby6L4JTj%2FfIwam%2B4%2BwucBu%2BDgNK05Nle1rSt9HvR%2FKPC4U6LTfvUIaip1mjIa8fPzykii23h2eanT57zQ7fsyYH5QjywwlooAUcAdOh5QumgTHx6aAO7%2FL52eaQNEShrxfhL6albEDmfhGflrsT4tps8gTHNOJbeDeBlt0WJWDHSgxs6cW6lQqyg1FpD5ZVDfhn1HYFF1y4Eiaqa18pQf3zzYMBhcanlBjYfgWNayAf%2FASOgklu8bmgD7hADrk4cRlOL7NSOewEcbqSmaivT33QuFdHXj5sdvjlN5yMDrAECmdgDWG2L8P%2BAKLs9ZLZ7dJda%2BB4Xl84t7QvnKfvpXJv9obz2KgK8dXyqISyV0sXGZ0U47hOA%2FAiigbEMECJxC9aoKp86re5O5prxOlHkcksutSQJzxZRlPZmrOKhsQBF5zEZKybUC0vVjG8PqOnhOq46qyDTDnj5gZBriWCk4DvXrudQnXQmnXblebhAC2cCB6zIbM4PYgGl0elPSgIf3iFEA21aLdHYLHUQuVkpgi02SxFdrG862Y8ymYGMvXDzUmiX8DS5vKZyZlGmsSgQqfLub5RyLNS4zfDiZc9Edzh%2FtCE%2BX8j9k%2FqWB071rcZyMImne1SLkL4GRw4UPHMV3jjwEYpPG5uW5fAEot0aTSJnsGAwHJi2nvF1Y5OIqWziVCQd5NT7t6Q8guOSpgS%2Fa1dSRn8JGGaCD3BPXDyQRG4Bqhu8XrgAp0yy8DMSvvyVXDgJcJTcr1wQ2BvFKf65jqhvmxXUuDpGBlRvV36XvGjQzLi8KAKT2lYOnmxQPGorURSV0NhyTIuIyqOmKTMhQ%2BieEsgOgpc4KBbfDM4B3SIgFljvfHF6cef7qpyLBXAiQcXvg5l3Iunp%2FWv4dH6qFziO%2BL9PbrimQ9RY6MQphEfGUpOmma7KkGzuS8sPUFnCtIYcKCaI9EXo4HlQLgGrBjbiK5EqMj2AKWt9QWcIFMtnVvQVDQV9lXJJqdPVtUQpbh6gCI2Ov1nvZts7yYdsnvRgxiWFOtNJcOMVLn1vgptVi6qrNiFOfEjHCDB3J%2BHDLqUB77YgQGwX%2Fb1eYna3hGKdlqJKIyiE4nSbV8VFgxmxR4b5mVkkeUhMgs5YTi4ja2XZ009xJRHdkfwMi%2BfocaancuO7h%2FMlcLOa0V%2FSw6Dq47CumRQAKhgbOP8t%2BMTjuxjJGhXCY6XpmDDFqWlVYbQ1aDJ5Cptdw4oLbf3Ck%2BdWkVP0LpH7s9XLPXI%2FQX8ws%2Bj2In63IcRvOOo%2BTTjiN%2BlssfRsanW%2B3REVKoavBOAPTXABW4AL7e4NygHdpAKBscmlDh9Jysp4wxbnUNna3L3xBvyE1jyrGIkUHaqQMuxhHElV6oj1picvgL1QEuS5PyZTEaivqh5vUCKJqOuIgPFGESns8kyFk7%2FDxyima3cYxi%2FYOQCj%2F%2B9Ms2Ll%2Bhn4FmKnl7JkGXQGDKDAz9rUGL1TIlBpuJr9Be2JjK6qPzyDg495UxXYF7JY1qKimw9jWjF0iV6DRIqE%2B%2FeWG0J2ofmZTk0mLYVd4GLiFCOoKR0Cg727tWq981InYynvCuKW43aXgEjofVbxIqrm0VL76zlH3gQzWP3R3Bv9oXxclrlO7VVtgBRpSP4hMFWJ8BrUSBCJXC07l40X4jWuvtc42ofNCxtlX2JH6bdeojXgTh5TxOBKEyY5wvBE%2BACh8BtOPNPkApjoxi5h%2B%2FFMQQNpWvZaMH7MKFu5Ax8HoCQdmGkJrtnOiLHwD3uS5y8%2F2xTSDrE%2F4PT1yqtt6vGe8ldMBVMEPd6KwqiYECHDlfbvzphcWP%2BJiZuL5swoWQYlS%2Br7Yu5mNUiGD2retxBi9fl6RDGn4Ti9B1oyYy%2BMP5G87D%2FCpRlvdnuy0PY6RC8BzTA40NXqckQ9TaOUDywkYsudxJzPgyDoAWn%2BB6nEFbaVxxC6UXjJiuDkW9TWq7uRBOJocky9iMfUhGpv%2FdQuVVIuGjYqACbXf8aa%2BPeYNIHZsM7l4s5gAQuUAzRUoT51hnH3EWofXf2vkD5HJJ33vwE%2FaEWp36GHr6GpMaH4AAPuqM5eabH%2FhfG9zcCz4nN6cPinuAw6IHwtvyB%2FdO1toZciBaPh25U0ducR2PI3Zl7mokyLWKkSnEDOg1x5fCsJE9EKhH7HwFNhWMGMS7%2BqxyYsbHHRUDUH4I%2FAheQY7wujJNnFUH4KdCju83riuQeHU9WEqNzjsJFuF%2FdTDAZ%2FK7%2F1WaAU%2BAWymT59pVMT4g2AxcwNa0XEBDdBDpAPvgDIH73R25teeuAF5ime2Ul0OUIiG4GpSAEJeYW9wDTf43wfwHgHLKJoPznkwAAAABJRU5ErkJggg%3D%3D)](https://doi.org/10.6084/m9.figshare.21965324)
 

### 2023-01-27 README.qmd
Try again

--- 2023-01-04 README.qmd
@@
 ---
+
+[[DOI](https://img.shields.io/badge/doi-10.6084/m9.figshare.21965324-blue.svg?style=flat&labelColor=whitesmoke&logo=data%3Aimage%2Fpng%3Bbase64%2CiVBORw0KGgoAAAANSUhEUgAAAB8AAAAfCAYAAAAfrhY5AAAJsklEQVR42qWXd1DTaRrHf%2BiB2Hdt5zhrAUKz4IKEYu9IGiGFFJJQ0gkJCAKiWFDWBRdFhCQUF3UVdeVcRQEBxUI3yY9iEnQHb3bdW1fPubnyz%2F11M7lvEHfOQee2ZOYzPyDv%2B3yf9%2Fk95YX4fx%2BltfUt08GcFEuPR4U9hDDZ%2FVngIlhb%2FSiI6InkTgLzgDcgfvtnovhH4BzoVlrbwr55QnhCtBW4QHXnFrZbPBaQoBh4%2FSYH2EnpBEtqcDMVzB93wA%2F8AFwa23XFGcc8CkT3mxz%2BfXWtq9T9IQlLIXYEuHojudb%2BCM7Hgdq8ydi%2FAHiBXyY%2BLjwFlAEnS6Jnar%2FvnQVhvdzasad0eKvWZKe8hvDB2ofLZ%2FZEcWsh%2BhyIuyO5Bxs2iZIE4nRv7NWAb0EO8AC%2FWPxjYAWuOEX2MSXZVgPxzmRL3xKz3ScGpx6p6QnOx4mDIFqO0w6Q4fEhO5IzwxlSwyD2FYHzwAW%2BAZ4fEsf74gCumykwNHskLM7taQxLYjjIyy8MUtraGhTWdkfhkFJqtvuVl%2F9l2ZquDfEyrH8B0W06nnpH3JtIyRGpH1iJ6SfxDIHjRXHJmdQjLpfHeN54gnfFx4W9QRnovx%2FN20aXZeTD2J84hn3%2BqoF2Tqr14VqTPUCIcP%2B5%2Fly4qC%2BUL3sYxSvNj1NwsVYPsWdMUfomsdkYm3Tj0nbV0N1wRKwFe1MgKACDIBdMAhPE%2FwicwNWxll8Ag40w%2BFfhibJkGHmutjYeQ8gVlaN%2BjO51nDysa9TwNUFMqaGbKdRJZFfOJSp6mkRKsv0rRIpEVWjAvyFkxNOEpwvcAVPfEe%2Bl8ojeNTx3nXLBcWRrYGxSRjDEk0VlpxYrbe1ZmaQ5xuT0u3r%2B2qe5j0J5uytiZPGsRL2Jm32AldpxPUNJ3jmmsN4x62z1cXrbedXBQf2yvIFCeZrtyicZZG2U2nrrBJzYorI2EXLrvTfCSB43s41PKEvbZDEfQby6L4JTj%2FfIwam%2B4%2BwucBu%2BDgNK05Nle1rSt9HvR%2FKPC4U6LTfvUIaip1mjIa8fPzykii23h2eanT57zQ7fsyYH5QjywwlooAUcAdOh5QumgTHx6aAO7%2FL52eaQNEShrxfhL6albEDmfhGflrsT4tps8gTHNOJbeDeBlt0WJWDHSgxs6cW6lQqyg1FpD5ZVDfhn1HYFF1y4Eiaqa18pQf3zzYMBhcanlBjYfgWNayAf%2FASOgklu8bmgD7hADrk4cRlOL7NSOewEcbqSmaivT33QuFdHXj5sdvjlN5yMDrAECmdgDWG2L8P%2BAKLs9ZLZ7dJda%2BB4Xl84t7QvnKfvpXJv9obz2KgK8dXyqISyV0sXGZ0U47hOA%2FAiigbEMECJxC9aoKp86re5O5prxOlHkcksutSQJzxZRlPZmrOKhsQBF5zEZKybUC0vVjG8PqOnhOq46qyDTDnj5gZBriWCk4DvXrudQnXQmnXblebhAC2cCB6zIbM4PYgGl0elPSgIf3iFEA21aLdHYLHUQuVkpgi02SxFdrG862Y8ymYGMvXDzUmiX8DS5vKZyZlGmsSgQqfLub5RyLNS4zfDiZc9Edzh%2FtCE%2BX8j9k%2FqWB071rcZyMImne1SLkL4GRw4UPHMV3jjwEYpPG5uW5fAEot0aTSJnsGAwHJi2nvF1Y5OIqWziVCQd5NT7t6Q8guOSpgS%2Fa1dSRn8JGGaCD3BPXDyQRG4Bqhu8XrgAp0yy8DMSvvyVXDgJcJTcr1wQ2BvFKf65jqhvmxXUuDpGBlRvV36XvGjQzLi8KAKT2lYOnmxQPGorURSV0NhyTIuIyqOmKTMhQ%2BieEsgOgpc4KBbfDM4B3SIgFljvfHF6cef7qpyLBXAiQcXvg5l3Iunp%2FWv4dH6qFziO%2BL9PbrimQ9RY6MQphEfGUpOmma7KkGzuS8sPUFnCtIYcKCaI9EXo4HlQLgGrBjbiK5EqMj2AKWt9QWcIFMtnVvQVDQV9lXJJqdPVtUQpbh6gCI2Ov1nvZts7yYdsnvRgxiWFOtNJcOMVLn1vgptVi6qrNiFOfEjHCDB3J%2BHDLqUB77YgQGwX%2Fb1eYna3hGKdlqJKIyiE4nSbV8VFgxmxR4b5mVkkeUhMgs5YTi4ja2XZ009xJRHdkfwMi%2BfocaancuO7h%2FMlcLOa0V%2FSw6Dq47CumRQAKhgbOP8t%2BMTjuxjJGhXCY6XpmDDFqWlVYbQ1aDJ5Cptdw4oLbf3Ck%2BdWkVP0LpH7s9XLPXI%2FQX8ws%2Bj2In63IcRvOOo%2BTTjiN%2BlssfRsanW%2B3REVKoavBOAPTXABW4AL7e4NygHdpAKBscmlDh9Jysp4wxbnUNna3L3xBvyE1jyrGIkUHaqQMuxhHElV6oj1picvgL1QEuS5PyZTEaivqh5vUCKJqOuIgPFGESns8kyFk7%2FDxyima3cYxi%2FYOQCj%2F%2B9Ms2Ll%2Bhn4FmKnl7JkGXQGDKDAz9rUGL1TIlBpuJr9Be2JjK6qPzyDg495UxXYF7JY1qKimw9jWjF0iV6DRIqE%2B%2FeWG0J2ofmZTk0mLYVd4GLiFCOoKR0Cg727tWq981InYynvCuKW43aXgEjofVbxIqrm0VL76zlH3gQzWP3R3Bv9oXxclrlO7VVtgBRpSP4hMFWJ8BrUSBCJXC07l40X4jWuvtc42ofNCxtlX2JH6bdeojXgTh5TxOBKEyY5wvBE%2BACh8BtOPNPkApjoxi5h%2B%2FFMQQNpWvZaMH7MKFu5Ax8HoCQdmGkJrtnOiLHwD3uS5y8%2F2xTSDrE%2F4PT1yqtt6vGe8ldMBVMEPd6KwqiYECHDlfbvzphcWP%2BJiZuL5swoWQYlS%2Br7Yu5mNUiGD2retxBi9fl6RDGn4Ti9B1oyYy%2BMP5G87D%2FCpRlvdnuy0PY6RC8BzTA40NXqckQ9TaOUDywkYsudxJzPgyDoAWn%2BB6nEFbaVxxC6UXjJiuDkW9TWq7uRBOJocky9iMfUhGpv%2FdQuVVIuGjYqACbXf8aa%2BPeYNIHZsM7l4s5gAQuUAzRUoT51hnH3EWofXf2vkD5HJJ33vwE%2FaEWp36GHr6GpMaH4AAPuqM5eabH%2FhfG9zcCz4nN6cPinuAw6IHwtvyB%2FdO1toZciBaPh25U0ducR2PI3Zl7mokyLWKkSnEDOg1x5fCsJE9EKhH7HwFNhWMGMS7%2BqxyYsbHHRUDUH4I%2FAheQY7wujJNnFUH4KdCju83riuQeHU9WEqNzjsJFuF%2FdTDAZ%2FK7%2F1WaAU%2BAWymT59pVMT4g2AxcwNa0XEBDdBDpAPvgDIH73R25teeuAF5ime2Ul0OUIiG4GpSAEJeYW9wDTf43wfwHgHLKJoPznkwAAAABJRU5ErkJggg%3D%3D)](https://doi.org/10.6084/m9.figshare.21965324)
 

### 2023-01-27 README.qmd
Try again.

--- 2023-01-27 README.qmd
@@
 
-[![DOI](https://img.shields.io/badge/doi-10.26180/5c6e1160b8d8a-blue.svg?style=flat&labelColor=whitesmoke&logo=data%3Aimage%2Fpng%3Bbase64%2CiVBORw0KGgoAAAANSUhEUgAAAB8AAAAfCAYAAAAfrhY5AAAJsklEQVR42qWXd1DTaRrHf%2BiB2Hdt5zhrAUKz4IKEYu9IGiGFFJJQ0gkJCAKiWFDWBRdFhCQUF3UVdeVcRQEBxUI3yY9iEnQHb3bdW1fPubnyz%2F11M7lvEHfOQee2ZOYzPyDv%2B3yf9%2Fk95YX4fx%2BltfUt08GcFEuPR4U9hDDZ%2FVngIlhb%2FSiI6InkTgLzgDcgfvtnovhH4BzoVlrbwr55QnhCtBW4QHXnFrZbPBaQoBh4%2FSYH2EnpBEtqcDMVzB93wA%2F8AFwa23XFGcc8CkT3mxz%2BfXWtq9T9IQlLIXYEuHojudb%2BCM7Hgdq8ydi%2FAHiBXyY%2BLjwFlAEnS6Jnar%2FvnQVhvdzasad0eKvWZKe8hvDB2ofLZ%2FZEcWsh%2BhyIuyO5Bxs2iZIE4nRv7NWAb0EO8AC%2FWPxjYAWuOEX2MSXZVgPxzmRL3xKz3ScGpx6p6QnOx4mDIFqO0w6Q4fEhO5IzwxlSwyD2FYHzwAW%2BAZ4fEsf74gCumykwNHskLM7taQxLYjjIyy8MUtraGhTWdkfhkFJqtvuVl%2F9l2ZquDfEyrH8B0W06nnpH3JtIyRGpH1iJ6SfxDIHjRXHJmdQjLpfHeN54gnfFx4W9QRnovx%2FN20aXZeTD2J84hn3%2BqoF2Tqr14VqTPUCIcP%2B5%2Fly4qC%2BUL3sYxSvNj1NwsVYPsWdMUfomsdkYm3Tj0nbV0N1wRKwFe1MgKACDIBdMAhPE%2FwicwNWxll8Ag40w%2BFfhibJkGHmutjYeQ8gVlaN%2BjO51nDysa9TwNUFMqaGbKdRJZFfOJSp6mkRKsv0rRIpEVWjAvyFkxNOEpwvcAVPfEe%2Bl8ojeNTx3nXLBcWRrYGxSRjDEk0VlpxYrbe1ZmaQ5xuT0u3r%2B2qe5j0J5uytiZPGsRL2Jm32AldpxPUNJ3jmmsN4x62z1cXrbedXBQf2yvIFCeZrtyicZZG2U2nrrBJzYorI2EXLrvTfCSB43s41PKEvbZDEfQby6L4JTj%2FfIwam%2B4%2BwucBu%2BDgNK05Nle1rSt9HvR%2FKPC4U6LTfvUIaip1mjIa8fPzykii23h2eanT57zQ7fsyYH5QjywwlooAUcAdOh5QumgTHx6aAO7%2FL52eaQNEShrxfhL6albEDmfhGflrsT4tps8gTHNOJbeDeBlt0WJWDHSgxs6cW6lQqyg1FpD5ZVDfhn1HYFF1y4Eiaqa18pQf3zzYMBhcanlBjYfgWNayAf%2FASOgklu8bmgD7hADrk4cRlOL7NSOewEcbqSmaivT33QuFdHXj5sdvjlN5yMDrAECmdgDWG2L8P%2BAKLs9ZLZ7dJda%2BB4Xl84t7QvnKfvpXJv9obz2KgK8dXyqISyV0sXGZ0U47hOA%2FAiigbEMECJxC9aoKp86re5O5prxOlHkcksutSQJzxZRlPZmrOKhsQBF5zEZKybUC0vVjG8PqOnhOq46qyDTDnj5gZBriWCk4DvXrudQnXQmnXblebhAC2cCB6zIbM4PYgGl0elPSgIf3iFEA21aLdHYLHUQuVkpgi02SxFdrG862Y8ymYGMvXDzUmiX8DS5vKZyZlGmsSgQqfLub5RyLNS4zfDiZc9Edzh%2FtCE%2BX8j9k%2FqWB071rcZyMImne1SLkL4GRw4UPHMV3jjwEYpPG5uW5fAEot0aTSJnsGAwHJi2nvF1Y5OIqWziVCQd5NT7t6Q8guOSpgS%2Fa1dSRn8JGGaCD3BPXDyQRG4Bqhu8XrgAp0yy8DMSvvyVXDgJcJTcr1wQ2BvFKf65jqhvmxXUuDpGBlRvV36XvGjQzLi8KAKT2lYOnmxQPGorURSV0NhyTIuIyqOmKTMhQ%2BieEsgOgpc4KBbfDM4B3SIgFljvfHF6cef7qpyLBXAiQcXvg5l3Iunp%2FWv4dH6qFziO%2BL9PbrimQ9RY6MQphEfGUpOmma7KkGzuS8sPUFnCtIYcKCaI9EXo4HlQLgGrBjbiK5EqMj2AKWt9QWcIFMtnVvQVDQV9lXJJqdPVtUQpbh6gCI2Ov1nvZts7yYdsnvRgxiWFOtNJcOMVLn1vgptVi6qrNiFOfEjHCDB3J%2BHDLqUB77YgQGwX%2Fb1eYna3hGKdlqJKIyiE4nSbV8VFgxmxR4b5mVkkeUhMgs5YTi4ja2XZ009xJRHdkfwMi%2BfocaancuO7h%2FMlcLOa0V%2FSw6Dq47CumRQAKhgbOP8t%2BMTjuxjJGhXCY6XpmDDFqWlVYbQ1aDJ5Cptdw4oLbf3Ck%2BdWkVP0LpH7s9XLPXI%2FQX8ws%2Bj2In63IcRvOOo%2BTTjiN%2BlssfRsanW%2B3REVKoavBOAPTXABW4AL7e4NygHdpAKBscmlDh9Jysp4wxbnUNna3L3xBvyE1jyrGIkUHaqQMuxhHElV6oj1picvgL1QEuS5PyZTEaivqh5vUCKJqOuIgPFGESns8kyFk7%2FDxyima3cYxi%2FYOQCj%2F%2B9Ms2Ll%2Bhn4FmKnl7JkGXQGDKDAz9rUGL1TIlBpuJr9Be2JjK6qPzyDg495UxXYF7JY1qKimw9jWjF0iV6DRIqE%2B%2FeWG0J2ofmZTk0mLYVd4GLiFCOoKR0Cg727tWq981InYynvCuKW43aXgEjofVbxIqrm0VL76zlH3gQzWP3R3Bv9oXxclrlO7VVtgBRpSP4hMFWJ8BrUSBCJXC07l40X4jWuvtc42ofNCxtlX2JH6bdeojXgTh5TxOBKEyY5wvBE%2BACh8BtOPNPkApjoxi5h%2B%2FFMQQNpWvZaMH7MKFu5Ax8HoCQdmGkJrtnOiLHwD3uS5y8%2F2xTSDrE%2F4PT1yqtt6vGe8ldMBVMEPd6KwqiYECHDlfbvzphcWP%2BJiZuL5swoWQYlS%2Br7Yu5mNUiGD2retxBi9fl6RDGn4Ti9B1oyYy%2BMP5G87D%2FCpRlvdnuy0PY6RC8BzTA40NXqckQ9TaOUDywkYsudxJzPgyDoAWn%2BB6nEFbaVxxC6UXjJiuDkW9TWq7uRBOJocky9iMfUhGpv%2FdQuVVIuGjYqACbXf8aa%2BPeYNIHZsM7l4s5gAQuUAzRUoT51hnH3EWofXf2vkD5HJJ33vwE%2FaEWp36GHr6GpMaH4AAPuqM5eabH%2FhfG9zcCz4nN6cPinuAw6IHwtvyB%2FdO1toZciBaPh25U0ducR2PI3Zl7mokyLWKkSnEDOg1x5fCsJE9EKhH7HwFNhWMGMS7%2BqxyYsbHHRUDUH4I%2FAheQY7wujJNnFUH4KdCju83riuQeHU9WEqNzjsJFuF%2FdTDAZ%2FK7%2F1WaAU%2BAWymT59pVMT4g2AxcwNa0XEBDdBDpAPvgDIH73R25teeuAF5ime2Ul0OUIiG4GpSAEJeYW9wDTf43wfwHgHLKJoPznkwAAAABJRU5ErkJggg%3D%3D)](https://doi.org/10.6084/m9.figshare.21965324)
+[![](https://img.shields.io/badge/doi-10.6084/m9.figshare.21965324-blue.svg?style=flat&labelColor=whitesmoke&logo=data%3Aimage%2Fpng%3Bbase64%2CiVBORw0KGgoAAAANSUhEUgAAAB8AAAAfCAYAAAAfrhY5AAAJsklEQVR42qWXd1DTaRrHf%2BiB2Hdt5zhrAUKz4IKEYu9IGiGFFJJQ0gkJCAKiWFDWBRdFhCQUF3UVdeVcRQEBxUI3yY9iEnQHb3bdW1fPubnyz%2F11M7lvEHfOQee2ZOYzPyDv%2B3yf9%2Fk95YX4fx%2BltfUt08GcFEuPR4U9hDDZ%2FVngIlhb%2FSiI6InkTgLzgDcgfvtnovhH4BzoVlrbwr55QnhCtBW4QHXnFrZbPBaQoBh4%2FSYH2EnpBEtqcDMVzB93wA%2F8AFwa23XFGcc8CkT3mxz%2BfXWtq9T9IQlLIXYEuHojudb%2BCM7Hgdq8ydi%2FAHiBXyY%2BLjwFlAEnS6Jnar%2FvnQVhvdzasad0eKvWZKe8hvDB2ofLZ%2FZEcWsh%2BhyIuyO5Bxs2iZIE4nRv7NWAb0EO8AC%2FWPxjYAWuOEX2MSXZVgPxzmRL3xKz3ScGpx6p6QnOx4mDIFqO0w6Q4fEhO5IzwxlSwyD2FYHzwAW%2BAZ4fEsf74gCumykwNHskLM7taQxLYjjIyy8MUtraGhTWdkfhkFJqtvuVl%2F9l2ZquDfEyrH8B0W06nnpH3JtIyRGpH1iJ6SfxDIHjRXHJmdQjLpfHeN54gnfFx4W9QRnovx%2FN20aXZeTD2J84hn3%2BqoF2Tqr14VqTPUCIcP%2B5%2Fly4qC%2BUL3sYxSvNj1NwsVYPsWdMUfomsdkYm3Tj0nbV0N1wRKwFe1MgKACDIBdMAhPE%2FwicwNWxll8Ag40w%2BFfhibJkGHmutjYeQ8gVlaN%2BjO51nDysa9TwNUFMqaGbKdRJZFfOJSp6mkRKsv0rRIpEVWjAvyFkxNOEpwvcAVPfEe%2Bl8ojeNTx3nXLBcWRrYGxSRjDEk0VlpxYrbe1ZmaQ5xuT0u3r%2B2qe5j0J5uytiZPGsRL2Jm32AldpxPUNJ3jmmsN4x62z1cXrbedXBQf2yvIFCeZrtyicZZG2U2nrrBJzYorI2EXLrvTfCSB43s41PKEvbZDEfQby6L4JTj%2FfIwam%2B4%2BwucBu%2BDgNK05Nle1rSt9HvR%2FKPC4U6LTfvUIaip1mjIa8fPzykii23h2eanT57zQ7fsyYH5QjywwlooAUcAdOh5QumgTHx6aAO7%2FL52eaQNEShrxfhL6albEDmfhGflrsT4tps8gTHNOJbeDeBlt0WJWDHSgxs6cW6lQqyg1FpD5ZVDfhn1HYFF1y4Eiaqa18pQf3zzYMBhcanlBjYfgWNayAf%2FASOgklu8bmgD7hADrk4cRlOL7NSOewEcbqSmaivT33QuFdHXj5sdvjlN5yMDrAECmdgDWG2L8P%2BAKLs9ZLZ7dJda%2BB4Xl84t7QvnKfvpXJv9obz2KgK8dXyqISyV0sXGZ0U47hOA%2FAiigbEMECJxC9aoKp86re5O5prxOlHkcksutSQJzxZRlPZmrOKhsQBF5zEZKybUC0vVjG8PqOnhOq46qyDTDnj5gZBriWCk4DvXrudQnXQmnXblebhAC2cCB6zIbM4PYgGl0elPSgIf3iFEA21aLdHYLHUQuVkpgi02SxFdrG862Y8ymYGMvXDzUmiX8DS5vKZyZlGmsSgQqfLub5RyLNS4zfDiZc9Edzh%2FtCE%2BX8j9k%2FqWB071rcZyMImne1SLkL4GRw4UPHMV3jjwEYpPG5uW5fAEot0aTSJnsGAwHJi2nvF1Y5OIqWziVCQd5NT7t6Q8guOSpgS%2Fa1dSRn8JGGaCD3BPXDyQRG4Bqhu8XrgAp0yy8DMSvvyVXDgJcJTcr1wQ2BvFKf65jqhvmxXUuDpGBlRvV36XvGjQzLi8KAKT2lYOnmxQPGorURSV0NhyTIuIyqOmKTMhQ%2BieEsgOgpc4KBbfDM4B3SIgFljvfHF6cef7qpyLBXAiQcXvg5l3Iunp%2FWv4dH6qFziO%2BL9PbrimQ9RY6MQphEfGUpOmma7KkGzuS8sPUFnCtIYcKCaI9EXo4HlQLgGrBjbiK5EqMj2AKWt9QWcIFMtnVvQVDQV9lXJJqdPVtUQpbh6gCI2Ov1nvZts7yYdsnvRgxiWFOtNJcOMVLn1vgptVi6qrNiFOfEjHCDB3J%2BHDLqUB77YgQGwX%2Fb1eYna3hGKdlqJKIyiE4nSbV8VFgxmxR4b5mVkkeUhMgs5YTi4ja2XZ009xJRHdkfwMi%2BfocaancuO7h%2FMlcLOa0V%2FSw6Dq47CumRQAKhgbOP8t%2BMTjuxjJGhXCY6XpmDDFqWlVYbQ1aDJ5Cptdw4oLbf3Ck%2BdWkVP0LpH7s9XLPXI%2FQX8ws%2Bj2In63IcRvOOo%2BTTjiN%2BlssfRsanW%2B3REVKoavBOAPTXABW4AL7e4NygHdpAKBscmlDh9Jysp4wxbnUNna3L3xBvyE1jyrGIkUHaqQMuxhHElV6oj1picvgL1QEuS5PyZTEaivqh5vUCKJqOuIgPFGESns8kyFk7%2FDxyima3cYxi%2FYOQCj%2F%2B9Ms2Ll%2Bhn4FmKnl7JkGXQGDKDAz9rUGL1TIlBpuJr9Be2JjK6qPzyDg495UxXYF7JY1qKimw9jWjF0iV6DRIqE%2B%2FeWG0J2ofmZTk0mLYVd4GLiFCOoKR0Cg727tWq981InYynvCuKW43aXgEjofVbxIqrm0VL76zlH3gQzWP3R3Bv9oXxclrlO7VVtgBRpSP4hMFWJ8BrUSBCJXC07l40X4jWuvtc42ofNCxtlX2JH6bdeojXgTh5TxOBKEyY5wvBE%2BACh8BtOPNPkApjoxi5h%2B%2FFMQQNpWvZaMH7MKFu5Ax8HoCQdmGkJrtnOiLHwD3uS5y8%2F2xTSDrE%2F4PT1yqtt6vGe8ldMBVMEPd6KwqiYECHDlfbvzphcWP%2BJiZuL5swoWQYlS%2Br7Yu5mNUiGD2retxBi9fl6RDGn4Ti9B1oyYy%2BMP5G87D%2FCpRlvdnuy0PY6RC8BzTA40NXqckQ9TaOUDywkYsudxJzPgyDoAWn%2BB6nEFbaVxxC6UXjJiuDkW9TWq7uRBOJocky9iMfUhGpv%2FdQuVVIuGjYqACbXf8aa%2BPeYNIHZsM7l4s5gAQuUAzRUoT51hnH3EWofXf2vkD5HJJ33vwE%2FaEWp36GHr6GpMaH4AAPuqM5eabH%2FhfG9zcCz4nN6cPinuAw6IHwtvyB%2FdO1toZciBaPh25U0ducR2PI3Zl7mokyLWKkSnEDOg1x5fCsJE9EKhH7HwFNhWMGMS7%2BqxyYsbHHRUDUH4I%2FAheQY7wujJNnFUH4KdCju83riuQeHU9WEqNzjsJFuF%2FdTDAZ%2FK7%2F1WaAU%2BAWymT59pVMT4g2AxcwNa0XEBDdBDpAPvgDIH73R25teeuAF5ime2Ul0OUIiG4GpSAEJeYW9wDTf43wfwHgHLKJoPznkwAAAABJRU5ErkJggg%3D%3D)](https://doi.org/10.6084/m9.figshare.21965324)
 

### 2023-01-27 README.qmd
Update Readme to include setting up procedures.

--- 2023-01-27 README.qmd
@@
 
-[](https://img.shields.io/badge/doi-10.6084/m9.figshare.21965324-blue.svg?style=flat&labelColor=whitesmoke&logo=data%3Aimage%2Fpng%3Bbase64%2CiVBORw0KGgoAAAANSUhEUgAAAB8AAAAfCAYAAAAfrhY5AAAJsklEQVR42qWXd1DTaRrHf%2BiB2Hdt5zhrAUKz4IKEYu9IGiGFFJJQ0gkJCAKiWFDWBRdFhCQUF3UVdeVcRQEBxUI3yY9iEnQHb3bdW1fPubnyz%2F11M7lvEHfOQee2ZOYzPyDv%2B3yf9%2Fk95YX4fx%2BltfUt08GcFEuPR4U9hDDZ%2FVngIlhb%2FSiI6InkTgLzgDcgfvtnovhH4BzoVlrbwr55QnhCtBW4QHXnFrZbPBaQoBh4%2FSYH2EnpBEtqcDMVzB93wA%2F8AFwa23XFGcc8CkT3mxz%2BfXWtq9T9IQlLIXYEuHojudb%2BCM7Hgdq8ydi%2FAHiBXyY%2BLjwFlAEnS6Jnar%2FvnQVhvdzasad0eKvWZKe8hvDB2ofLZ%2FZEcWsh%2BhyIuyO5Bxs2iZIE4nRv7NWAb0EO8AC%2FWPxjYAWuOEX2MSXZVgPxzmRL3xKz3ScGpx6p6QnOx4mDIFqO0w6Q4fEhO5IzwxlSwyD2FYHzwAW%2BAZ4fEsf74gCumykwNHskLM7taQxLYjjIyy8MUtraGhTWdkfhkFJqtvuVl%2F9l2ZquDfEyrH8B0W06nnpH3JtIyRGpH1iJ6SfxDIHjRXHJmdQjLpfHeN54gnfFx4W9QRnovx%2FN20aXZeTD2J84hn3%2BqoF2Tqr14VqTPUCIcP%2B5%2Fly4qC%2BUL3sYxSvNj1NwsVYPsWdMUfomsdkYm3Tj0nbV0N1wRKwFe1MgKACDIBdMAhPE%2FwicwNWxll8Ag40w%2BFfhibJkGHmutjYeQ8gVlaN%2BjO51nDysa9TwNUFMqaGbKdRJZFfOJSp6mkRKsv0rRIpEVWjAvyFkxNOEpwvcAVPfEe%2Bl8ojeNTx3nXLBcWRrYGxSRjDEk0VlpxYrbe1ZmaQ5xuT0u3r%2B2qe5j0J5uytiZPGsRL2Jm32AldpxPUNJ3jmmsN4x62z1cXrbedXBQf2yvIFCeZrtyicZZG2U2nrrBJzYorI2EXLrvTfCSB43s41PKEvbZDEfQby6L4JTj%2FfIwam%2B4%2BwucBu%2BDgNK05Nle1rSt9HvR%2FKPC4U6LTfvUIaip1mjIa8fPzykii23h2eanT57zQ7fsyYH5QjywwlooAUcAdOh5QumgTHx6aAO7%2FL52eaQNEShrxfhL6albEDmfhGflrsT4tps8gTHNOJbeDeBlt0WJWDHSgxs6cW6lQqyg1FpD5ZVDfhn1HYFF1y4Eiaqa18pQf3zzYMBhcanlBjYfgWNayAf%2FASOgklu8bmgD7hADrk4cRlOL7NSOewEcbqSmaivT33QuFdHXj5sdvjlN5yMDrAECmdgDWG2L8P%2BAKLs9ZLZ7dJda%2BB4Xl84t7QvnKfvpXJv9obz2KgK8dXyqISyV0sXGZ0U47hOA%2FAiigbEMECJxC9aoKp86re5O5prxOlHkcksutSQJzxZRlPZmrOKhsQBF5zEZKybUC0vVjG8PqOnhOq46qyDTDnj5gZBriWCk4DvXrudQnXQmnXblebhAC2cCB6zIbM4PYgGl0elPSgIf3iFEA21aLdHYLHUQuVkpgi02SxFdrG862Y8ymYGMvXDzUmiX8DS5vKZyZlGmsSgQqfLub5RyLNS4zfDiZc9Edzh%2FtCE%2BX8j9k%2FqWB071rcZyMImne1SLkL4GRw4UPHMV3jjwEYpPG5uW5fAEot0aTSJnsGAwHJi2nvF1Y5OIqWziVCQd5NT7t6Q8guOSpgS%2Fa1dSRn8JGGaCD3BPXDyQRG4Bqhu8XrgAp0yy8DMSvvyVXDgJcJTcr1wQ2BvFKf65jqhvmxXUuDpGBlRvV36XvGjQzLi8KAKT2lYOnmxQPGorURSV0NhyTIuIyqOmKTMhQ%2BieEsgOgpc4KBbfDM4B3SIgFljvfHF6cef7qpyLBXAiQcXvg5l3Iunp%2FWv4dH6qFziO%2BL9PbrimQ9RY6MQphEfGUpOmma7KkGzuS8sPUFnCtIYcKCaI9EXo4HlQLgGrBjbiK5EqMj2AKWt9QWcIFMtnVvQVDQV9lXJJqdPVtUQpbh6gCI2Ov1nvZts7yYdsnvRgxiWFOtNJcOMVLn1vgptVi6qrNiFOfEjHCDB3J%2BHDLqUB77YgQGwX%2Fb1eYna3hGKdlqJKIyiE4nSbV8VFgxmxR4b5mVkkeUhMgs5YTi4ja2XZ009xJRHdkfwMi%2BfocaancuO7h%2FMlcLOa0V%2FSw6Dq47CumRQAKhgbOP8t%2BMTjuxjJGhXCY6XpmDDFqWlVYbQ1aDJ5Cptdw4oLbf3Ck%2BdWkVP0LpH7s9XLPXI%2FQX8ws%2Bj2In63IcRvOOo%2BTTjiN%2BlssfRsanW%2B3REVKoavBOAPTXABW4AL7e4NygHdpAKBscmlDh9Jysp4wxbnUNna3L3xBvyE1jyrGIkUHaqQMuxhHElV6oj1picvgL1QEuS5PyZTEaivqh5vUCKJqOuIgPFGESns8kyFk7%2FDxyima3cYxi%2FYOQCj%2F%2B9Ms2Ll%2Bhn4FmKnl7JkGXQGDKDAz9rUGL1TIlBpuJr9Be2JjK6qPzyDg495UxXYF7JY1qKimw9jWjF0iV6DRIqE%2B%2FeWG0J2ofmZTk0mLYVd4GLiFCOoKR0Cg727tWq981InYynvCuKW43aXgEjofVbxIqrm0VL76zlH3gQzWP3R3Bv9oXxclrlO7VVtgBRpSP4hMFWJ8BrUSBCJXC07l40X4jWuvtc42ofNCxtlX2JH6bdeojXgTh5TxOBKEyY5wvBE%2BACh8BtOPNPkApjoxi5h%2B%2FFMQQNpWvZaMH7MKFu5Ax8HoCQdmGkJrtnOiLHwD3uS5y8%2F2xTSDrE%2F4PT1yqtt6vGe8ldMBVMEPd6KwqiYECHDlfbvzphcWP%2BJiZuL5swoWQYlS%2Br7Yu5mNUiGD2retxBi9fl6RDGn4Ti9B1oyYy%2BMP5G87D%2FCpRlvdnuy0PY6RC8BzTA40NXqckQ9TaOUDywkYsudxJzPgyDoAWn%2BB6nEFbaVxxC6UXjJiuDkW9TWq7uRBOJocky9iMfUhGpv%2FdQuVVIuGjYqACbXf8aa%2BPeYNIHZsM7l4s5gAQuUAzRUoT51hnH3EWofXf2vkD5HJJ33vwE%2FaEWp36GHr6GpMaH4AAPuqM5eabH%2FhfG9zcCz4nN6cPinuAw6IHwtvyB%2FdO1toZciBaPh25U0ducR2PI3Zl7mokyLWKkSnEDOg1x5fCsJE9EKhH7HwFNhWMGMS7%2BqxyYsbHHRUDUH4I%2FAheQY7wujJNnFUH4KdCju83riuQeHU9WEqNzjsJFuF%2FdTDAZ%2FK7%2F1WaAU%2BAWymT59pVMT4g2AxcwNa0XEBDdBDpAPvgDIH73R25teeuAF5ime2Ul0OUIiG4GpSAEJeYW9wDTf43wfwHgHLKJoPznkwAAAABJRU5ErkJggg%3D%3D)](https://doi.org/10.6084/m9.figshare.21965324)
+[![](https://img.shields.io/badge/doi-10.6084/m9.figshare.21965324-blue.svg?style=flat&labelColor=whitesmoke&logo=data%3Aimage%2Fpng%3Bbase64%2CiVBORw0KGgoAAAANSUhEUgAAAB8AAAAfCAYAAAAfrhY5AAAJsklEQVR42qWXd1DTaRrHf%2BiB2Hdt5zhrAUKz4IKEYu9IGiGFFJJQ0gkJCAKiWFDWBRdFhCQUF3UVdeVcRQEBxUI3yY9iEnQHb3bdW1fPubnyz%2F11M7lvEHfOQee2ZOYzPyDv%2B3yf9%2Fk95YX4fx%2BltfUt08GcFEuPR4U9hDDZ%2FVngIlhb%2FSiI6InkTgLzgDcgfvtnovhH4BzoVlrbwr55QnhCtBW4QHXnFrZbPBaQoBh4%2FSYH2EnpBEtqcDMVzB93wA%2F8AFwa23XFGcc8CkT3mxz%2BfXWtq9T9IQlLIXYEuHojudb%2BCM7Hgdq8ydi%2FAHiBXyY%2BLjwFlAEnS6Jnar%2FvnQVhvdzasad0eKvWZKe8hvDB2ofLZ%2FZEcWsh%2BhyIuyO5Bxs2iZIE4nRv7NWAb0EO8AC%2FWPxjYAWuOEX2MSXZVgPxzmRL3xKz3ScGpx6p6QnOx4mDIFqO0w6Q4fEhO5IzwxlSwyD2FYHzwAW%2BAZ4fEsf74gCumykwNHskLM7taQxLYjjIyy8MUtraGhTWdkfhkFJqtvuVl%2F9l2ZquDfEyrH8B0W06nnpH3JtIyRGpH1iJ6SfxDIHjRXHJmdQjLpfHeN54gnfFx4W9QRnovx%2FN20aXZeTD2J84hn3%2BqoF2Tqr14VqTPUCIcP%2B5%2Fly4qC%2BUL3sYxSvNj1NwsVYPsWdMUfomsdkYm3Tj0nbV0N1wRKwFe1MgKACDIBdMAhPE%2FwicwNWxll8Ag40w%2BFfhibJkGHmutjYeQ8gVlaN%2BjO51nDysa9TwNUFMqaGbKdRJZFfOJSp6mkRKsv0rRIpEVWjAvyFkxNOEpwvcAVPfEe%2Bl8ojeNTx3nXLBcWRrYGxSRjDEk0VlpxYrbe1ZmaQ5xuT0u3r%2B2qe5j0J5uytiZPGsRL2Jm32AldpxPUNJ3jmmsN4x62z1cXrbedXBQf2yvIFCeZrtyicZZG2U2nrrBJzYorI2EXLrvTfCSB43s41PKEvbZDEfQby6L4JTj%2FfIwam%2B4%2BwucBu%2BDgNK05Nle1rSt9HvR%2FKPC4U6LTfvUIaip1mjIa8fPzykii23h2eanT57zQ7fsyYH5QjywwlooAUcAdOh5QumgTHx6aAO7%2FL52eaQNEShrxfhL6albEDmfhGflrsT4tps8gTHNOJbeDeBlt0WJWDHSgxs6cW6lQqyg1FpD5ZVDfhn1HYFF1y4Eiaqa18pQf3zzYMBhcanlBjYfgWNayAf%2FASOgklu8bmgD7hADrk4cRlOL7NSOewEcbqSmaivT33QuFdHXj5sdvjlN5yMDrAECmdgDWG2L8P%2BAKLs9ZLZ7dJda%2BB4Xl84t7QvnKfvpXJv9obz2KgK8dXyqISyV0sXGZ0U47hOA%2FAiigbEMECJxC9aoKp86re5O5prxOlHkcksutSQJzxZRlPZmrOKhsQBF5zEZKybUC0vVjG8PqOnhOq46qyDTDnj5gZBriWCk4DvXrudQnXQmnXblebhAC2cCB6zIbM4PYgGl0elPSgIf3iFEA21aLdHYLHUQuVkpgi02SxFdrG862Y8ymYGMvXDzUmiX8DS5vKZyZlGmsSgQqfLub5RyLNS4zfDiZc9Edzh%2FtCE%2BX8j9k%2FqWB071rcZyMImne1SLkL4GRw4UPHMV3jjwEYpPG5uW5fAEot0aTSJnsGAwHJi2nvF1Y5OIqWziVCQd5NT7t6Q8guOSpgS%2Fa1dSRn8JGGaCD3BPXDyQRG4Bqhu8XrgAp0yy8DMSvvyVXDgJcJTcr1wQ2BvFKf65jqhvmxXUuDpGBlRvV36XvGjQzLi8KAKT2lYOnmxQPGorURSV0NhyTIuIyqOmKTMhQ%2BieEsgOgpc4KBbfDM4B3SIgFljvfHF6cef7qpyLBXAiQcXvg5l3Iunp%2FWv4dH6qFziO%2BL9PbrimQ9RY6MQphEfGUpOmma7KkGzuS8sPUFnCtIYcKCaI9EXo4HlQLgGrBjbiK5EqMj2AKWt9QWcIFMtnVvQVDQV9lXJJqdPVtUQpbh6gCI2Ov1nvZts7yYdsnvRgxiWFOtNJcOMVLn1vgptVi6qrNiFOfEjHCDB3J%2BHDLqUB77YgQGwX%2Fb1eYna3hGKdlqJKIyiE4nSbV8VFgxmxR4b5mVkkeUhMgs5YTi4ja2XZ009xJRHdkfwMi%2BfocaancuO7h%2FMlcLOa0V%2FSw6Dq47CumRQAKhgbOP8t%2BMTjuxjJGhXCY6XpmDDFqWlVYbQ1aDJ5Cptdw4oLbf3Ck%2BdWkVP0LpH7s9XLPXI%2FQX8ws%2Bj2In63IcRvOOo%2BTTjiN%2BlssfRsanW%2B3REVKoavBOAPTXABW4AL7e4NygHdpAKBscmlDh9Jysp4wxbnUNna3L3xBvyE1jyrGIkUHaqQMuxhHElV6oj1picvgL1QEuS5PyZTEaivqh5vUCKJqOuIgPFGESns8kyFk7%2FDxyima3cYxi%2FYOQCj%2F%2B9Ms2Ll%2Bhn4FmKnl7JkGXQGDKDAz9rUGL1TIlBpuJr9Be2JjK6qPzyDg495UxXYF7JY1qKimw9jWjF0iV6DRIqE%2B%2FeWG0J2ofmZTk0mLYVd4GLiFCOoKR0Cg727tWq981InYynvCuKW43aXgEjofVbxIqrm0VL76zlH3gQzWP3R3Bv9oXxclrlO7VVtgBRpSP4hMFWJ8BrUSBCJXC07l40X4jWuvtc42ofNCxtlX2JH6bdeojXgTh5TxOBKEyY5wvBE%2BACh8BtOPNPkApjoxi5h%2B%2FFMQQNpWvZaMH7MKFu5Ax8HoCQdmGkJrtnOiLHwD3uS5y8%2F2xTSDrE%2F4PT1yqtt6vGe8ldMBVMEPd6KwqiYECHDlfbvzphcWP%2BJiZuL5swoWQYlS%2Br7Yu5mNUiGD2retxBi9fl6RDGn4Ti9B1oyYy%2BMP5G87D%2FCpRlvdnuy0PY6RC8BzTA40NXqckQ9TaOUDywkYsudxJzPgyDoAWn%2BB6nEFbaVxxC6UXjJiuDkW9TWq7uRBOJocky9iMfUhGpv%2FdQuVVIuGjYqACbXf8aa%2BPeYNIHZsM7l4s5gAQuUAzRUoT51hnH3EWofXf2vkD5HJJ33vwE%2FaEWp36GHr6GpMaH4AAPuqM5eabH%2FhfG9zcCz4nN6cPinuAw6IHwtvyB%2FdO1toZciBaPh25U0ducR2PI3Zl7mokyLWKkSnEDOg1x5fCsJE9EKhH7HwFNhWMGMS7%2BqxyYsbHHRUDUH4I%2FAheQY7wujJNnFUH4KdCju83riuQeHU9WEqNzjsJFuF%2FdTDAZ%2FK7%2F1WaAU%2BAWymT59pVMT4g2AxcwNa0XEBDdBDpAPvgDIH73R25teeuAF5ime2Ul0OUIiG4GpSAEJeYW9wDTf43wfwHgHLKJoPznkwAAAABJRU5ErkJggg%3D%3D)](https://doi.org/10.6084/m9.figshare.21965324)
+[![](https://img.shields.io/badge/License-CC%20BY%204.0-yellow.svg)](https://creativecommons.org/licenses/by/4.0/)
+
+# Version control
+
+Refer to [NEWS.md](https://github.com/JauntyJJS/lancer_output/blob/main/NEWS.md) for more information.
 
@@
 
+# Output Examples
+
 ## Excel Output Example
 
-[`curve_summary.xlsx`](https://raw.githubusercontent.com/JauntyJJS/lancer_output/main/curve_summary.xlsx) is the output in Excel.
+[`curve_summary.xlsx`](https://raw.githubusercontent.com/JauntyJJS/lancer_output/main/curve_summary.xlsx) is an example of `lancer`'s output in Excel.
 
@@
 
-[`curve_plot.pdf`](https://raw.githubusercontent.com/JauntyJJS/lancer_output/main/curve_plot.pdf) is the output in pdf.
+[`curve_plot.pdf`](https://raw.githubusercontent.com/JauntyJJS/lancer_output/main/curve_plot.pdf) is an example of `lancer`'s output in pdf.
 
@@
 
-https://lancer-interactive-example.netlify.app is the output as an interactive trellis plot from the `Curve_Plot_Folder` when the `index.html` file is clicked.
+https://lancer-interactive-example.netlify.app is an example of `lancer`'s output as an interactive trellis plot from the folder `Quarto_Example/Curve_Plot_Folder` when the `index.html` file inside the folder is clicked.
 
@@
 
-https://lancer-quarto-example.netlify.app is the output of a html file generated using [Quarto](https://quarto.org/)
+https://lancer-quarto-example.netlify.app comes from left clicking the `index.html` file from the `Quarto_Example` folder.
+The `index.html` file is generated by running [Quarto](https://quarto.org/) on the `index.qmd` script file.
 
@@
 https://lancer-simulation.netlify.app is the report of a simulation experiment done in the paper.
+The link comes from left clicking the `index.html` file from the `Quarto_Simulation` folder.
+The `index.html` file is generated by running [Quarto](https://quarto.org/) on the `index.qmd` script file.
+
+# Setting up
+
+In order to use this project locally, install
+
+-    [R](https://cran.rstudio.com/)
+-    [RStudio](https://posit.co/download/rstudio-desktop/)
+-    [git](https://git-scm.com/)
+-    [GNU software development tools](https://support.posit.co/hc/en-us/articles/200486498-Package-Development-Prerequisites) like 
+    - [RTools](https://cran.rstudio.com/bin/windows/Rtools/) for Windows
+    - [Xcode](http://itunes.apple.com/us/app/xcode/id497799835?mt=12) for Mac
+    - `r-base-dev` for Linux
+
+in order to use this project locally.
+
+[Clone the repository](https://happygitwithr.com/existing-github-first.html#new-rstudio-project-via-git-clone), then run the following code chunks to initialise the project.
+
+First, install the R package [`renv`](https://rstudio.github.io/renv/index.html)
+
+```{r}
+#| eval: false
+#| warning: false
+#| message: false
+
+install.packages("renv", dependencies = TRUE)
+```
+
+Once installation is done, start a local R library.
+
+```{r}
+#| eval: false
+#| warning: false
+#| message: false
+
+renv::init(bare = TRUE)
+```
+
+Some of the R packages may only have the source code available, without any binary files. Install these R packages to ensure installation of such R packages is possible.
+
+```{r}
+#| eval: false
+#| warning: false
+#| message: false
+
+install.packages("rlang", dependencies = TRUE)
+install.packages("devtools", dependencies = TRUE)
+```
+
+Type the following command to install R packages `lancer` version 0.1.0.
+
+```{r}
+#| eval: false
+#| warning: false
+#| message: false
+devtools::install_github("SLINGhub/lancer", ref = "0.1.0")
+```
+
+Next, type the following command to install the other R packages dependencies.
+
+```{r}
+#| eval: false
+#| warning: false
+#| message: false
+renv::restore()
+```
+
+Once you have run these steps, in RStudio you can open the individual Quarto documents and render each file.

### 2023-01-27 Manuscript/manuscript.qmd
Run code with new version of `lancer`.

@@
 
-*lancer* is available on GitHub <https://github.com/SLINGhub/lancer>. The documentation and tutorials can be accessed from <https://slinghub.github.io/lancer/>
+*lancer* is available on GitHub <https://github.com/SLINGhub/lancer> and figshare <https://doi.org/10.6084/m9.figshare.21966896>.
+The documentation and tutorials can be accessed from <https://slinghub.github.io/lancer/>.
+
+The Quarto scripts for the web links underlying this article are available on figshare at <https://doi.org/10.6084/m9.figshare.21965324>.
 
@@
 It also provides an interactive plot for exploratory data analysis.
-*lancer* is available on GitHub <https://github.com/SLINGhub/lancer> while the documentation and tutorials can be accessed from <https://slinghub.github.io/lancer>.
+*lancer* is available on GitHub <https://github.com/SLINGhub/lancer> and figshare <https://doi.org/10.6084/m9.figshare.21966896> while the documentation and tutorials can be accessed from <https://slinghub.github.io/lancer>.
+The Quarto scripts for the web links underlying this article are available on figshare at <https://doi.org/10.6084/m9.figshare.21965324>.
 

### 2023-01-27 README.qmd
Run code with new version of `lancer`.

@@
 
-[![](https://img.shields.io/badge/doi-10.6084/m9.figshare.21965324-blue.svg?style=flat&labelColor=whitesmoke&logo=data%3Aimage%2Fpng%3Bbase64%2CiVBORw0KGgoAAAANSUhEUgAAAB8AAAAfCAYAAAAfrhY5AAAJsklEQVR42qWXd1DTaRrHf%2BiB2Hdt5zhrAUKz4IKEYu9IGiGFFJJQ0gkJCAKiWFDWBRdFhCQUF3UVdeVcRQEBxUI3yY9iEnQHb3bdW1fPubnyz%2F11M7lvEHfOQee2ZOYzPyDv%2B3yf9%2Fk95YX4fx%2BltfUt08GcFEuPR4U9hDDZ%2FVngIlhb%2FSiI6InkTgLzgDcgfvtnovhH4BzoVlrbwr55QnhCtBW4QHXnFrZbPBaQoBh4%2FSYH2EnpBEtqcDMVzB93wA%2F8AFwa23XFGcc8CkT3mxz%2BfXWtq9T9IQlLIXYEuHojudb%2BCM7Hgdq8ydi%2FAHiBXyY%2BLjwFlAEnS6Jnar%2FvnQVhvdzasad0eKvWZKe8hvDB2ofLZ%2FZEcWsh%2BhyIuyO5Bxs2iZIE4nRv7NWAb0EO8AC%2FWPxjYAWuOEX2MSXZVgPxzmRL3xKz3ScGpx6p6QnOx4mDIFqO0w6Q4fEhO5IzwxlSwyD2FYHzwAW%2BAZ4fEsf74gCumykwNHskLM7taQxLYjjIyy8MUtraGhTWdkfhkFJqtvuVl%2F9l2ZquDfEyrH8B0W06nnpH3JtIyRGpH1iJ6SfxDIHjRXHJmdQjLpfHeN54gnfFx4W9QRnovx%2FN20aXZeTD2J84hn3%2BqoF2Tqr14VqTPUCIcP%2B5%2Fly4qC%2BUL3sYxSvNj1NwsVYPsWdMUfomsdkYm3Tj0nbV0N1wRKwFe1MgKACDIBdMAhPE%2FwicwNWxll8Ag40w%2BFfhibJkGHmutjYeQ8gVlaN%2BjO51nDysa9TwNUFMqaGbKdRJZFfOJSp6mkRKsv0rRIpEVWjAvyFkxNOEpwvcAVPfEe%2Bl8ojeNTx3nXLBcWRrYGxSRjDEk0VlpxYrbe1ZmaQ5xuT0u3r%2B2qe5j0J5uytiZPGsRL2Jm32AldpxPUNJ3jmmsN4x62z1cXrbedXBQf2yvIFCeZrtyicZZG2U2nrrBJzYorI2EXLrvTfCSB43s41PKEvbZDEfQby6L4JTj%2FfIwam%2B4%2BwucBu%2BDgNK05Nle1rSt9HvR%2FKPC4U6LTfvUIaip1mjIa8fPzykii23h2eanT57zQ7fsyYH5QjywwlooAUcAdOh5QumgTHx6aAO7%2FL52eaQNEShrxfhL6albEDmfhGflrsT4tps8gTHNOJbeDeBlt0WJWDHSgxs6cW6lQqyg1FpD5ZVDfhn1HYFF1y4Eiaqa18pQf3zzYMBhcanlBjYfgWNayAf%2FASOgklu8bmgD7hADrk4cRlOL7NSOewEcbqSmaivT33QuFdHXj5sdvjlN5yMDrAECmdgDWG2L8P%2BAKLs9ZLZ7dJda%2BB4Xl84t7QvnKfvpXJv9obz2KgK8dXyqISyV0sXGZ0U47hOA%2FAiigbEMECJxC9aoKp86re5O5prxOlHkcksutSQJzxZRlPZmrOKhsQBF5zEZKybUC0vVjG8PqOnhOq46qyDTDnj5gZBriWCk4DvXrudQnXQmnXblebhAC2cCB6zIbM4PYgGl0elPSgIf3iFEA21aLdHYLHUQuVkpgi02SxFdrG862Y8ymYGMvXDzUmiX8DS5vKZyZlGmsSgQqfLub5RyLNS4zfDiZc9Edzh%2FtCE%2BX8j9k%2FqWB071rcZyMImne1SLkL4GRw4UPHMV3jjwEYpPG5uW5fAEot0aTSJnsGAwHJi2nvF1Y5OIqWziVCQd5NT7t6Q8guOSpgS%2Fa1dSRn8JGGaCD3BPXDyQRG4Bqhu8XrgAp0yy8DMSvvyVXDgJcJTcr1wQ2BvFKf65jqhvmxXUuDpGBlRvV36XvGjQzLi8KAKT2lYOnmxQPGorURSV0NhyTIuIyqOmKTMhQ%2BieEsgOgpc4KBbfDM4B3SIgFljvfHF6cef7qpyLBXAiQcXvg5l3Iunp%2FWv4dH6qFziO%2BL9PbrimQ9RY6MQphEfGUpOmma7KkGzuS8sPUFnCtIYcKCaI9EXo4HlQLgGrBjbiK5EqMj2AKWt9QWcIFMtnVvQVDQV9lXJJqdPVtUQpbh6gCI2Ov1nvZts7yYdsnvRgxiWFOtNJcOMVLn1vgptVi6qrNiFOfEjHCDB3J%2BHDLqUB77YgQGwX%2Fb1eYna3hGKdlqJKIyiE4nSbV8VFgxmxR4b5mVkkeUhMgs5YTi4ja2XZ009xJRHdkfwMi%2BfocaancuO7h%2FMlcLOa0V%2FSw6Dq47CumRQAKhgbOP8t%2BMTjuxjJGhXCY6XpmDDFqWlVYbQ1aDJ5Cptdw4oLbf3Ck%2BdWkVP0LpH7s9XLPXI%2FQX8ws%2Bj2In63IcRvOOo%2BTTjiN%2BlssfRsanW%2B3REVKoavBOAPTXABW4AL7e4NygHdpAKBscmlDh9Jysp4wxbnUNna3L3xBvyE1jyrGIkUHaqQMuxhHElV6oj1picvgL1QEuS5PyZTEaivqh5vUCKJqOuIgPFGESns8kyFk7%2FDxyima3cYxi%2FYOQCj%2F%2B9Ms2Ll%2Bhn4FmKnl7JkGXQGDKDAz9rUGL1TIlBpuJr9Be2JjK6qPzyDg495UxXYF7JY1qKimw9jWjF0iV6DRIqE%2B%2FeWG0J2ofmZTk0mLYVd4GLiFCOoKR0Cg727tWq981InYynvCuKW43aXgEjofVbxIqrm0VL76zlH3gQzWP3R3Bv9oXxclrlO7VVtgBRpSP4hMFWJ8BrUSBCJXC07l40X4jWuvtc42ofNCxtlX2JH6bdeojXgTh5TxOBKEyY5wvBE%2BACh8BtOPNPkApjoxi5h%2B%2FFMQQNpWvZaMH7MKFu5Ax8HoCQdmGkJrtnOiLHwD3uS5y8%2F2xTSDrE%2F4PT1yqtt6vGe8ldMBVMEPd6KwqiYECHDlfbvzphcWP%2BJiZuL5swoWQYlS%2Br7Yu5mNUiGD2retxBi9fl6RDGn4Ti9B1oyYy%2BMP5G87D%2FCpRlvdnuy0PY6RC8BzTA40NXqckQ9TaOUDywkYsudxJzPgyDoAWn%2BB6nEFbaVxxC6UXjJiuDkW9TWq7uRBOJocky9iMfUhGpv%2FdQuVVIuGjYqACbXf8aa%2BPeYNIHZsM7l4s5gAQuUAzRUoT51hnH3EWofXf2vkD5HJJ33vwE%2FaEWp36GHr6GpMaH4AAPuqM5eabH%2FhfG9zcCz4nN6cPinuAw6IHwtvyB%2FdO1toZciBaPh25U0ducR2PI3Zl7mokyLWKkSnEDOg1x5fCsJE9EKhH7HwFNhWMGMS7%2BqxyYsbHHRUDUH4I%2FAheQY7wujJNnFUH4KdCju83riuQeHU9WEqNzjsJFuF%2FdTDAZ%2FK7%2F1WaAU%2BAWymT59pVMT4g2AxcwNa0XEBDdBDpAPvgDIH73R25teeuAF5ime2Ul0OUIiG4GpSAEJeYW9wDTf43wfwHgHLKJoPznkwAAAABJRU5ErkJggg%3D%3D)](https://doi.org/10.6084/m9.figshare.21965324)
-[![](https://img.shields.io/badge/License-CC%20BY%204.0-yellow.svg)](https://creativecommons.org/licenses/by/4.0/)
+[![](https://img.shields.io/badge/doi-10.6084/m9.figshare.21965324-blue.svg?style=flat&labelColor=whitesmoke&logo=data%253Aimage%252Fpng%253Bbase64%252CiVBORw0KGgoAAAANSUhEUgAAAB8AAAAfCAYAAAAfrhY5AAAJsklEQVR42qWXd1DTaRrHf%252BiB2Hdt5zhrAUKz4IKEYu9IGiGFFJJQ0gkJCAKiWFDWBRdFhCQUF3UVdeVcRQEBxUI3yY9iEnQHb3bdW1fPubnyz%252F11M7lvEHfOQee2ZOYzPyDv%252B3yf9%252Fk95YX4fx%252BltfUt08GcFEuPR4U9hDDZ%252FVngIlhb%252FSiI6InkTgLzgDcgfvtnovhH4BzoVlrbwr55QnhCtBW4QHXnFrZbPBaQoBh4%252FSYH2EnpBEtqcDMVzB93wA%252F8AFwa23XFGcc8CkT3mxz%252BfXWtq9T9IQlLIXYEuHojudb%252BCM7Hgdq8ydi%252FAHiBXyY%252BLjwFlAEnS6Jnar%252FvnQVhvdzasad0eKvWZKe8hvDB2ofLZ%252FZEcWsh%252BhyIuyO5Bxs2iZIE4nRv7NWAb0EO8AC%252FWPxjYAWuOEX2MSXZVgPxzmRL3xKz3ScGpx6p6QnOx4mDIFqO0w6Q4fEhO5IzwxlSwyD2FYHzwAW%252BAZ4fEsf74gCumykwNHskLM7taQxLYjjIyy8MUtraGhTWdkfhkFJqtvuVl%252F9l2ZquDfEyrH8B0W06nnpH3JtIyRGpH1iJ6SfxDIHjRXHJmdQjLpfHeN54gnfFx4W9QRnovx%252FN20aXZeTD2J84hn3%252BqoF2Tqr14VqTPUCIcP%252B5%252Fly4qC%252BUL3sYxSvNj1NwsVYPsWdMUfomsdkYm3Tj0nbV0N1wRKwFe1MgKACDIBdMAhPE%252FwicwNWxll8Ag40w%252BFfhibJkGHmutjYeQ8gVlaN%252BjO51nDysa9TwNUFMqaGbKdRJZFfOJSp6mkRKsv0rRIpEVWjAvyFkxNOEpwvcAVPfEe%252Bl8ojeNTx3nXLBcWRrYGxSRjDEk0VlpxYrbe1ZmaQ5xuT0u3r%252B2qe5j0J5uytiZPGsRL2Jm32AldpxPUNJ3jmmsN4x62z1cXrbedXBQf2yvIFCeZrtyicZZG2U2nrrBJzYorI2EXLrvTfCSB43s41PKEvbZDEfQby6L4JTj%252FfIwam%252B4%252BwucBu%252BDgNK05Nle1rSt9HvR%252FKPC4U6LTfvUIaip1mjIa8fPzykii23h2eanT57zQ7fsyYH5QjywwlooAUcAdOh5QumgTHx6aAO7%252FL52eaQNEShrxfhL6albEDmfhGflrsT4tps8gTHNOJbeDeBlt0WJWDHSgxs6cW6lQqyg1FpD5ZVDfhn1HYFF1y4Eiaqa18pQf3zzYMBhcanlBjYfgWNayAf%252FASOgklu8bmgD7hADrk4cRlOL7NSOewEcbqSmaivT33QuFdHXj5sdvjlN5yMDrAECmdgDWG2L8P%252BAKLs9ZLZ7dJda%252BB4Xl84t7QvnKfvpXJv9obz2KgK8dXyqISyV0sXGZ0U47hOA%252FAiigbEMECJxC9aoKp86re5O5prxOlHkcksutSQJzxZRlPZmrOKhsQBF5zEZKybUC0vVjG8PqOnhOq46qyDTDnj5gZBriWCk4DvXrudQnXQmnXblebhAC2cCB6zIbM4PYgGl0elPSgIf3iFEA21aLdHYLHUQuVkpgi02SxFdrG862Y8ymYGMvXDzUmiX8DS5vKZyZlGmsSgQqfLub5RyLNS4zfDiZc9Edzh%252FtCE%252BX8j9k%252FqWB071rcZyMImne1SLkL4GRw4UPHMV3jjwEYpPG5uW5fAEot0aTSJnsGAwHJi2nvF1Y5OIqWziVCQd5NT7t6Q8guOSpgS%252Fa1dSRn8JGGaCD3BPXDyQRG4Bqhu8XrgAp0yy8DMSvvyVXDgJcJTcr1wQ2BvFKf65jqhvmxXUuDpGBlRvV36XvGjQzLi8KAKT2lYOnmxQPGorURSV0NhyTIuIyqOmKTMhQ%252BieEsgOgpc4KBbfDM4B3SIgFljvfHF6cef7qpyLBXAiQcXvg5l3Iunp%252FWv4dH6qFziO%252BL9PbrimQ9RY6MQphEfGUpOmma7KkGzuS8sPUFnCtIYcKCaI9EXo4HlQLgGrBjbiK5EqMj2AKWt9QWcIFMtnVvQVDQV9lXJJqdPVtUQpbh6gCI2Ov1nvZts7yYdsnvRgxiWFOtNJcOMVLn1vgptVi6qrNiFOfEjHCDB3J%252BHDLqUB77YgQGwX%252Fb1eYna3hGKdlqJKIyiE4nSbV8VFgxmxR4b5mVkkeUhMgs5YTi4ja2XZ009xJRHdkfwMi%252BfocaancuO7h%252FMlcLOa0V%252FSw6Dq47CumRQAKhgbOP8t%252BMTjuxjJGhXCY6XpmDDFqWlVYbQ1aDJ5Cptdw4oLbf3Ck%252BdWkVP0LpH7s9XLPXI%252FQX8ws%252Bj2In63IcRvOOo%252BTTjiN%252BlssfRsanW%252B3REVKoavBOAPTXABW4AL7e4NygHdpAKBscmlDh9Jysp4wxbnUNna3L3xBvyE1jyrGIkUHaqQMuxhHElV6oj1picvgL1QEuS5PyZTEaivqh5vUCKJqOuIgPFGESns8kyFk7%252FDxyima3cYxi%252FYOQCj%252F%252B9Ms2Ll%252Bhn4FmKnl7JkGXQGDKDAz9rUGL1TIlBpuJr9Be2JjK6qPzyDg495UxXYF7JY1qKimw9jWjF0iV6DRIqE%252B%252FeWG0J2ofmZTk0mLYVd4GLiFCOoKR0Cg727tWq981InYynvCuKW43aXgEjofVbxIqrm0VL76zlH3gQzWP3R3Bv9oXxclrlO7VVtgBRpSP4hMFWJ8BrUSBCJXC07l40X4jWuvtc42ofNCxtlX2JH6bdeojXgTh5TxOBKEyY5wvBE%252BACh8BtOPNPkApjoxi5h%252B%252FFMQQNpWvZaMH7MKFu5Ax8HoCQdmGkJrtnOiLHwD3uS5y8%252F2xTSDrE%252F4PT1yqtt6vGe8ldMBVMEPd6KwqiYECHDlfbvzphcWP%252BJiZuL5swoWQYlS%252Br7Yu5mNUiGD2retxBi9fl6RDGn4Ti9B1oyYy%252BMP5G87D%252FCpRlvdnuy0PY6RC8BzTA40NXqckQ9TaOUDywkYsudxJzPgyDoAWn%252BB6nEFbaVxxC6UXjJiuDkW9TWq7uRBOJocky9iMfUhGpv%252FdQuVVIuGjYqACbXf8aa%252BPeYNIHZsM7l4s5gAQuUAzRUoT51hnH3EWofXf2vkD5HJJ33vwE%252FaEWp36GHr6GpMaH4AAPuqM5eabH%252FhfG9zcCz4nN6cPinuAw6IHwtvyB%252FdO1toZciBaPh25U0ducR2PI3Zl7mokyLWKkSnEDOg1x5fCsJE9EKhH7HwFNhWMGMS7%252BqxyYsbHHRUDUH4I%252FAheQY7wujJNnFUH4KdCju83riuQeHU9WEqNzjsJFuF%252FdTDAZ%252FK7%252F1WaAU%252BAWymT59pVMT4g2AxcwNa0XEBDdBDpAPvgDIH73R25teeuAF5ime2Ul0OUIiG4GpSAEJeYW9wDTf43wfwHgHLKJoPznkwAAAABJRU5ErkJggg%253D%253D)](https://doi.org/10.6084/m9.figshare.21965324) [![](https://img.shields.io/badge/License-CC%20BY%204.0-yellow.svg)](https://creativecommons.org/licenses/by/4.0/)
+
+# Introduction
+
+Here is where I store some output example of the R package [`lancer`](https://github.com/SLINGhub/lancer).
 
@@
 Refer to [NEWS.md](https://github.com/JauntyJJS/lancer_output/blob/main/NEWS.md) for more information.
-
-# Introduction
-
-Here is where I store some output example of the R package [`lancer`](https://github.com/SLINGhub/lancer).
 
@@
     -   [RTools](https://cran.rstudio.com/bin/windows/Rtools/) for Windows
+
     -   [Xcode](http://itunes.apple.com/us/app/xcode/id497799835?mt=12) for Mac
+
     -   `r-base-dev` for Linux
-
-in order to use this project locally.
 
@@
 Once you have run these steps, in RStudio you can open the individual Quarto documents and render each file.
+
+# Quarto documents
+
+## Quarto_Example folder
+
+Rendering `index.qmd` will produce in the folder
+
+-    `curve_summary.xlsx`
+-    `curve_plot.pdf`
+-    `index.html` with dependencies `index_files` and `Curve_Plot_Folder`
+
+## Quarto_Simulation folder
+
+Rendering `index.qmd` will produce in the folder
+
+-    `linear_simulated_database.csv`, `noise_regime_simulated_database.csv` and `saturation_regime_simulated_database.csv`
+-    `linear_simulated_database.rds`, `noise_regime_simulated_database.rds` and `saturation_regime_simulated_database.rds`
+-    `linear_curve_summary.csv`, `noise_regime_curve_summary.csv` and `saturation_regime_curve_summary.csv`
+-    `linear_curve_summary.rds`, `noise_regime_curve_summary.rds` and `saturation_regime_curve_summary.rds`
+-    `curve_plot_linear.pdf`, `curve_plot_noise_regime.pdf` and `curve_plot_saturation_regime.pdf`
+-    `index.html` with dependencies `index_files`, `Curve_Linear_Folder`, `Curve_Noise_Regime_Folder` and `Curve_Saturation_Regime_Folder`
+
+## Manuscript folder
+
+Rendering `manuscript.qmd` will produce `manuscript.docx`, the manuscript document.
+
+Rendering `supplementary.qmd` will produce `supplementary.docx`, the supplementary document.
+
+Do note that both Quarto documents read in the results of the simulated datasets from the files `linear_curve_summary.rds`, `noise_regime_curve_summary.rds` and `saturation_regime_curve_summary.rds` in the `Quarto_Simulation folder`

### 2023-01-27 README.qmd
Try out nre version of lancer.

@@
 
-Type the following command to install R packages `lancer` version 0.1.0.
+Install these R packages to ensure rendering of Quarto documents is possible.
 
@@
 #| message: false
-devtools::install_github("SLINGhub/lancer", ref = "0.1.0")
+
+install.packages("rmarkdown", dependencies = TRUE)
+install.packages("markdown", dependencies = TRUE)
+```
+
+Type the following command to install R packages `lancer` version 0.1.1.
+
+```{r}
+#| eval: false
+#| warning: false
+#| message: false
+devtools::install_github("SLINGhub/lancer", ref = "0.1.1")
 ```

### 2023-01-27 README.qmd
Try again.

--- 2023-01-27 README.qmd
@@
 
+# Introduction
+
+Here is where I store some output example of the R package [`lancer`](https://github.com/SLINGhub/lancer).
+
 # Version control
